---
title: "The effect of evenly spaced photoreceptors on chromatic contrast"
output:
  pdf_document: default
  html_document:
    theme: flatly
    toc: true
    toc_depth: 2
subtitle: Supplementary Information
Date: September 10 2021
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "./docs") })
---
# The aim {.tabset .tabset-fade .tabset-pills}

* Here, we tested the effect of even spacing of sensitivities on colour discrimination in a tetrachromatic visual system. Specifically, we ran visual models with __an evenly spaced visual system__ and __an unevenly spaced visual system__, then compared spectral contrast in all three comparison groups (‘leaf vs. flower’, ‘leaf vs. beetle’, ‘beetle vs. flower’). 

* These two visual systems have the same upper and lower sensitivities with varying distribution of the two middle sensitivities. The evenly spaced visual system has peak sensitivities at 355 nm, 455 nm, 560 nm, and 660 nm, while VS 660 from the [Main models](main_models.html) section is used to represent the unevenly spaced visual system, with peak sensitivities at 355 nm, 445 nm, 530 nm, and 660 nm. 

* The model parameters and the statistical methods remain the same as described in the main text.

</br>
</br>

```{r, warning=FALSE, echo=FALSE, message=FALSE, results='hide'}
library(pavo)
library(dplyr)
library(stringr)
library(tidyr) #for gather() 
library(ggplot2)
library(lme4)
library(car)
library(multcomp)
library(boot) #for mean() 
library(pander) #for creating tidy tables
library(ggpubr) #for ggarrange() 
library(tibble) # for add_column()
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE) # Suppress warnings in the HTML output
knitr::opts_chunk$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
```

```{r Import data, echo=FALSE, message=FALSE, warning=FALSE}
# import sensitivity curves
even.space <- read.csv("data/peak sensitivity_evenly space.csv", header = TRUE) %>%
  as.rspec()

specsensbuprest.model2 <- read.csv("data/peak sensitivity_filter shift_aim2.csv",header = TRUE) %>%
  as.rspec()

# import irradiance
irradiance.d65 <- read.csv("data/d65.csv", header = TRUE) %>% 
  as.rspec(lim = c(300,800)) %>%  #set import range
  procspec(opt = c("min", "max")) #standardize the illumination spectrum
irradiance.twilight <- read.csv("data/civil twilight.csv", header = TRUE) %>% 
  as.rspec(lim = c(300,800)) %>% 
  rename( twilight = Irradiance) %>% 
  irrad2flux() #convert the irradiance (μ Watt.cm^{-2}) to photon flux (μ mol.s^{-1}.m^{-2}) to derive correct quantum catch.

#import background - average leaf
aveleaf <- read.csv("data/aveleaf.csv", header = TRUE) %>% 
  as.rspec()

#import and combine beetle, flower, leaf together
raw.dataset <- read.csv("data/refelectance spectra.csv", header = TRUE) %>% 
  as.rspec()
dataset <- aggspec(raw.dataset, by = 3, FUN = mean) %>%  #average three measurements to a representative one
  procspec(opt = "smooth", span = 0.1, fixneg = "zero") #smooth the spectra and lift <0 to 0
```

## Sensitivity curves
```{r, fig.cap="Figure caption: Sensitivity curves of the evenly spaced visual system (solid lines) and the unevenly spaced visual system (VS 660; dotted lines).",echo = FALSE, message = FALSE, warning = FALSE}
#plot the visual systems
system.list <- c("evenly spaced","unevenly spaced")
system.type <- rep(system.list , c(1*501, 1*501))

visevencurve <- even.space %>%
  rename( UVS = 2, SWS = 3, MWS = 4, LWS = 5)
VS660curve <- specsensbuprest.model2[,c(1,2,3,4,9)] %>%  
  rename( UVS = 2, SWS = 3, MWS = 4, LWS = 5)
combine.curves <- visevencurve %>%  
  rbind(VS660curve) %>% 
  cbind(system.type) %>%
  gather(peak, value, -wl, -system.type) 

ggplot(combine.curves,
       aes(x = wl, y = value, 
           linetype = system.type, color = peak))+
  geom_line()+
  guides(color = guide_legend(title = "peak sensitivity", reverse = TRUE),
         linetype = guide_legend(title = "system type"))+
  scale_color_manual(
    values = c("red4","olivedrab4", "dodgerblue3", "darkorchid4"),
    labels = c("LWS", "MWS", "SWS", "UVS"))+
  xlab("Wavelength (nm)")+ 
  ylab("Relative spectral sensitivity")+
  theme_classic()
```

</br>
</br>

## Normalised sensitivity curves

```{r, fig.cap="Figure caption: Normalised sensitivity curves of the evenly spaced visual system (solid lines) and the unevenly spaced visual system (VS 660; dotted lines).",echo = FALSE, message = FALSE, warning = FALSE}
# Sensitivity data for evenly space
even.list <- list(even.space[, 1:2], even.space[, c(1, 3)], even.space[, c(1, 4)], even.space[, c(1, 5)])

hold.even <- tibble("UVS" = NA, "SWS" = NA, "MWS" = NA, "LWS" = NA, wl = even.space[,1])

for(i in 1:length(even.list)){
  
  temp <- even.list[[i]] %>% procspec(opt = c("min", "max"))
  hold.even[[i]] <- temp[, 2]
}

# Sensitivity data for unevenly space
unevenly.list <- list(specsensbuprest.model2[, 1:2], 
                      specsensbuprest.model2[, c(1, 3)], specsensbuprest.model2[, c(1, 4)], 
                      specsensbuprest.model2[, c(1, 5)], specsensbuprest.model2[, c(1, 6)], 
                      specsensbuprest.model2[, c(1, 7)], specsensbuprest.model2[, c(1, 8)], 
                      specsensbuprest.model2[, c(1, 9)])

hold.unevenly <- tibble("355 nm" = NA, "445 nm" = NA, "530 nm" = NA, "580 nm" = NA,
                        "600 nm" = NA, "620 nm" = NA, "640 nm" = NA, "660 nm" = NA, 
                        wl = specsensbuprest.model2[,1])

for(i in 1:length(unevenly.list)){
  
  temp <- unevenly.list[[i]] %>% procspec(opt = c("min", "max"))
  hold.unevenly[[i]] <- temp[, 2]
}

plotdat.unevenly <- gather(hold.unevenly[,1:8], peak, value) %>% cbind(hold.unevenly[,"wl"])

# Reshape and combine evenly and unevenly spaced data 

pre.plotdat.even <- gather(hold.even[,1:4], peak, value) %>% cbind(hold.even[,"wl"]) %>% 
  add_column(system.type = strrep("evenly spaced", 1)) 
pre.plotdat.uneven <- plotdat.unevenly %>% filter(peak %in% c("355 nm", "445 nm", "530 nm", "660 nm")) %>% 
  add_column(system.type = strrep("unevenly spaced", 1)) %>% 
  mutate(peak = str_replace(peak, "355 nm", "UVS")) %>% 
  mutate(peak = str_replace(peak, "445 nm", "SWS")) %>% 
  mutate(peak = str_replace(peak, "530 nm", "MWS")) %>% 
  mutate(peak = str_replace(peak, "660 nm", "LWS"))

plotdat.even <- pre.plotdat.even %>% rbind(pre.plotdat.uneven)

ggplot(plotdat.even,
       aes(x = wl, y = value, 
           linetype = system.type, color = peak))+
  geom_line()+
  guides(color = guide_legend(title = "peak sensitivity", reverse = TRUE),
         linetype = guide_legend(title = "system type"))+
  scale_color_manual(
    values = c("red4","olivedrab4", "dodgerblue3", "darkorchid4"))+
  xlab("Wavelength (nm)")+ 
  ylab("Relative spectral sensitivity")+
  theme_classic()

```

</br>
</br>

# Data description

* We used the same spectral data collected from beetles and plants as described in the [Main models](main_models.html) section.

</br>
</br>

# Run the visual models
* We ran the visual models with the same parameter settings and steps as in the main models.

```{r Set up functions for quantum catch calculation, message=FALSE}
## D65
get.d65.vismodel <- function(i){
  
  vs.i <- vismodel(dataset[1:501,], 
                   visual = i, #this need to change according to the visual system
                   bkg = aveleaf$aveleaf, 
                   illum = irradiance.d65[1:501,2], 
                   qcatch = 'fi', 
                   relative = FALSE,
                   vonkries = TRUE)
  return(vs.i)
}
```

```{r Calculate quatumn catch, echo=FALSE,message=FALSE, warning=FALSE}

# Quantum catch - D65
## Evenly space
buprest.even.space.d65 <- get.d65.vismodel(even.space)

## VS660
buprest660 <- get.d65.vismodel(specsensbuprest.model2[, c(1,2,3,4,9)])
```


```{r Calculate contrasts}
get.evenspace.coldist <- function(i){
  
  con <- coldist(modeldata = i, # put output of vismodel()
                   noise="neural", 
                   achro=FALSE, 
                   n = c(1.14,1,1.26,1.38),
                   weber = 0.12,
                   weber.ref = 4)
  
  return(con)
}

#Contrast calculation
Cbuprest.even.space.d65  <-  get.evenspace.coldist(buprest.even.space.d65)

#VS660
Cbuprest660 <- get.evenspace.coldist(buprest660)

#combine all contrast value in each comparison group

even.vissys_d65 <- list(Cbuprest.even.space.d65, Cbuprest660)
even.fl.vissys <- list("even.fl", "Vis5.fl") 
even.bl.vissys <- list("even.bl", "Vis5.bl")
even.bf.vissys <- list("even.bf", "Vis5.bf") 

### flower vs leaf
allvis.fl_d65.even <- data_frame()
for (i in 1:length(even.vissys_d65)) {
  
  temp.i <- even.vissys_d65[[i]] %>% 
    filter(str_detect(patch1,"flower")) %>% 
    filter(str_detect(patch2,"leaves"))
  
  temp.i$vissys <- strrep(even.fl.vissys[[i]],1)
  
  allvis.fl_d65.even <- temp.i %>% rbind(allvis.fl_d65.even)  
}

### beetle vs leaf
allvis.bl_d65.even <- data_frame()
for (i in 1:length(even.vissys_d65)) {
  
  temp.i <- even.vissys_d65[[i]] %>% 
    filter(str_detect(patch2,"beetle")) %>% 
    filter(str_detect(patch1,"leaves"))
  
  temp.i$vissys <- strrep(even.bl.vissys[[i]],1)
  
  allvis.bl_d65.even <- temp.i %>% rbind(allvis.bl_d65.even)  
}

### beetle vs flower
allvis.bf_d65.even <- data_frame()
for (i in 1:length(even.vissys_d65)) {
  
  temp.i <- even.vissys_d65[[i]] %>% 
    filter(str_detect(patch1,"flower")) %>% 
    filter(str_detect(patch2,"beetle"))
  
  temp.i$vissys <- strrep(even.bf.vissys[[i]],1)
  
  allvis.bf_d65.even <- temp.i %>% rbind(allvis.bf_d65.even)  
}


```
</br>
</br>

## Contrast tables

```{r Print contrast table, echo=FALSE,message=FALSE, warning=FALSE}
allvis.even_d65.list <- list(allvis.fl_d65.even, allvis.bl_d65.even, allvis.bf_d65.even)

## create a data frame to hold the loop output
contrast.list_d65.even <- data_frame(system = c("evenspace", "VS 660"),
                                     flower.vs.leaf = NA, 
                                     beetle.vs.leaf = NA, 
                                     beetle.vs.flower = NA)
## loop
for (i in 1:length(allvis.even_d65.list)) {
  
   meantable.i <- aggregate(allvis.even_d65.list[[i]][,"dS"], 
                            by = list(allvis.even_d65.list[[i]]$vissys), 
                            mean) 
   mean.i <- meantable.i[, 2] 
   contrast.list_d65.even[,i+1] <- mean.i # here same at column i+1 because the 1st column is the visual system names
}

## print out the table 
contrast.list_d65.even %>% pander() 
```

</br>
</br>


# Compare contrasts {.tabset .tabset-fade .tabset-pills}
* To compare contrasts between visual systems, We conducted Wald chi-square tests on generalised linear mixed models (GLMM) followed by posthoc tests.

* In the models, we assigned
    + Independent variable: __contrast__
    + Dependent variable: 
        + Fixed factor: __visual system__
        + Random factor: __sample ID__ of both targets in the comparison

```{r Set up list and function for GLMM, echo=FALSE,message=FALSE, warning=FALSE} 
# Organize data before GLMM

## D65 - Aim 2
### flower vs leaf
vislist.fl_d65.even <- list("even.flower.vs.leaf",
                            "bup660.flower.vs.leaf")
compare.flower.vs.leaf.even <- data_frame()
for (i in 1:length(even.vissys_d65)) {

temp.i <-  even.vissys_d65[[i]] %>% 
  filter(str_detect(patch1, "flower")) %>% 
  filter(str_detect(patch2, "leaves")) %>% 
  dplyr::select(1:3)

temp.i$vissys <- strrep(vislist.fl_d65.even[[i]],1)

compare.flower.vs.leaf.even <- compare.flower.vs.leaf.even %>% rbind(temp.i)
}

### beetle vs leaf
vislist.bl_d65.even <- list("even.beetle.vs.leaf",
                            "bup660.beetle.vs.leaf")
compare.beetle.vs.leaf.even <- data_frame()
for (i in 1:length(even.vissys_d65)) {

temp.i <-  even.vissys_d65[[i]] %>% 
  filter(str_detect(patch1, "leaves")) %>% 
  filter(str_detect(patch2, "beetle")) %>% 
  dplyr::select(1:3)

temp.i$vissys <- strrep(vislist.bl_d65.even[[i]],1)

compare.beetle.vs.leaf.even <- compare.beetle.vs.leaf.even %>% rbind(temp.i)
}


### beetle vs flower
vislist.bf_d65.even <- list("even.beetle.vs.flower",
                            "bup660.beetle.vs.flower")
compare.beetle.vs.flower.even <- data_frame()
for (i in 1:length(even.vissys_d65)) {

temp.i <-  even.vissys_d65[[i]] %>% 
  filter(str_detect(patch1, "flower")) %>% 
  filter(str_detect(patch2, "beetle")) %>% 
  dplyr::select(1:3)

temp.i$vissys <- strrep(vislist.bf_d65.even[[i]],1)

compare.beetle.vs.flower.even <- compare.beetle.vs.flower.even %>% rbind(temp.i)
}

```

</br>

```{r Set up functions for GLMM}
get.lmer <- function(datlist, compnnumber){
  
  lmer(dS ~ vissys + (1|patch2) + (1|patch1), 
       data = datlist[[compnnumber]], REML = F)
  #REML=F, in order to fit the model using the likelihood ratio test. Otherwise, the lmer default will fit the model using the REML (REstricted Maximum Likelihood) criterion.
}

get.posthocsum <- function(modelx){
  
  summary(glht(modelx, 
               linfct = mcp(vissys = "Tukey")), 
          test = adjusted("bonferroni"))
}
```

```{r Run GLMM models, echo=FALSE,message=FALSE, warning=FALSE}
# set up list
input.list.regres_d65.even <- list(compare.flower.vs.leaf.even,
                                compare.beetle.vs.leaf.even,
                                compare.beetle.vs.flower.even)

# Evenly space
##Flower vs Leaf
m.flower.vs.leaf_d65.even <- get.lmer(input.list.regres_d65.even, 1)
sum.flower.vs.leaf_d65.even <- get.posthocsum(m.flower.vs.leaf_d65.even)

##Beetle vs Leaf
m.beetle.vs.leaf_d65.even <- get.lmer(input.list.regres_d65.even, 2)
sum.beetle.vs.leaf_d65.even <- get.posthocsum(m.beetle.vs.leaf_d65.even)

##Beetle vs Flower
m.beetle.vs.flower_d65.even <- get.lmer(input.list.regres_d65.even, 3)
sum.beetle.vs.flower_d65.even <- get.posthocsum(m.beetle.vs.flower_d65.even)

# Evenly space
##Flower vs Leaf
m.flower.vs.leaf_d65.even <- get.lmer(input.list.regres_d65.even, 1)
sum.flower.vs.leaf_d65.even <- get.posthocsum(m.flower.vs.leaf_d65.even)

##Beetle vs Leaf
m.beetle.vs.leaf_d65.even <- get.lmer(input.list.regres_d65.even, 2)
sum.beetle.vs.leaf_d65.even <- get.posthocsum(m.beetle.vs.leaf_d65.even)

##Beetle vs Flower
m.beetle.vs.flower_d65.even <- get.lmer(input.list.regres_d65.even, 3)
sum.beetle.vs.flower_d65.even <- get.posthocsum(m.beetle.vs.flower_d65.even)
```

## __Flower vs. Leaf__ 

```{r,echo=FALSE,message=FALSE, warning=FALSE}
Anova(m.flower.vs.leaf_d65.even) %>% pander()
```


</br>
</br>


## __Beetle vs. Leaf__
```{r,echo=FALSE,message=FALSE, warning=FALSE}
Anova(m.beetle.vs.leaf_d65.even) %>% pander()
```

</br>
</br>


## __Beetle vs. Flower__ 
```{r,echo=FALSE,message=FALSE, warning=FALSE}
Anova(m.beetle.vs.flower_d65.even) %>% pander()
```

</br>
</br>


# Summary
For all three comparison groups, VS 660 (unevenly spaced visual system) has significantly higher contrast than the evenly spaced visual system. This indicates that our results were not biased by uneven spacing of spectral sensitivities in our hypothetical visual systems.