---
title: "Visual sensitivity in the far-red enhances contrast against vegetation"
author: <br>Lu-Yi Wang^1^, Devi Stuart-Fox^1^, Geoff Walker^1^, Nicholas W. Roberts^2^
  and Amanda Franklin^1^ <br></br> ^1^School of Biosciences, The University of Melbourne,
  Australia <br></br> ^2^School of Biological Sciences, University of Bristol, UK
  <br></br>
output:
  pdf_document: default
  html_document:
    theme: flatly
subtitle: Supplementary Information
Date: March 24 2020
---
  
#Aims
  
* We investigated the potential benefit of long wavelength sensitivity by modelling the visual contrast in representative insect vision.

* Specifically, we varied the presence of a long wavelength sensitive photoreceptor and its wavelength of maximum sensitivity.

* To make our study ecological relevant to far-red sensitivity, we focused on jewel beetles and their host plants. 

* Additionally, we tested the effect of red-shifted light environment on contrast by running the same models under twilight illumination.

</br>
</br>

#Load R libraries 
```{r, warning=FALSE, message=FALSE, results='hide'}
library(pavo)
library(dplyr)
library(stringr)
library(tidyr) #for gather() function
library(ggplot2)
library(lme4)
library(car)
library(multcomp)
library(boot) #for mean() function
library(pander) #for creating tidy tables
library(ggpubr) #for ggarrange() function
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE) # Suppress warnings in the HTML output
knitr::opts_chunk$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
```


</br>
</br>

#Data description

</br>

##Import and process the data
* All the wavelength used in the models ranged from 300-800 nm.

```{r import data,message=FALSE}
#import sensitivity curves
specsensbuprest.model1 <- read.csv("data/peak sensitivity for visual model 1.csv",header=TRUE) %>%
  as.rspec()
specsensbuprest.model2 <- read.csv("data/peak sensitivity for visual model 2.csv",header=TRUE) %>%
  as.rspec()
#import irradiance
irradiance.d65 <- read.csv("data/d65.csv",header=TRUE) %>% 
  as.rspec(lim=c(300,800)) %>%  #set import range
  procspec(opt = c("min", "max")) #standardize the illumination spectrum
irradiance.twilight <- read.csv("data/civil twilight.csv",header=TRUE) %>% 
  as.rspec(lim=c(300,800)) %>% 
  procspec(opt = c("min", "max")) %>% 
  rename( twilight = Irradiance) 

#import backgound - average leaf
aveleaf <- read.csv("data/aveleaf.csv",header=TRUE) %>% as.rspec()

#import and combind beetle, flower, leaf together
raw.dataset<-read.csv("data/pooled_spec_2019.csv",header=TRUE) %>% as.rspec()
dataset<- aggspec(raw.dataset, by = 3, FUN = mean) %>%  #average three measurements to a representative one
  procspec(opt = "smooth", span = 0.1, fixneg = "zero") #smooth the spectra and lift <0 to 0
```

</br>

##Spectral reflectance of the targets
* Jewel beetles and their host plants (leaves and flowers): collected using integrating sphere
  + Leaves: 
    + sample source: mainly from Melton Gardens and Maranoa Gardens (4 from Melbourne roadsides).
    + colour: green
    + totla number: 46 (all are from the host plant genus of Australian jewel beetles)
  
  + Flowers: 
    + sample source: mainly from Melton Gardens and Maranoa Gardens (4 from Melbourne roadsides).
    + colour: white (10), pink (11), red (10), yellow (9), orange (3), and purple (4)
    + total number: 47 (from 46 species, exactly the same species for leaves reflectance)
  
  + Beetles:
    + sample source: Australian jewel beetles from, ANIC (29) and our own collection
    + colour: red, pink, yellow/orange, green, blue, velvet, black
    + totla number: 37

* We averaged of 3 measurements to generate a representative spectrum for each colour
* The spectral data were smoothed with the span = 0.1, and those < 0 were lifted to 0
```{r, fig.cap="Reflectance spectra of the targets"}
#assign categoryies to each spectrum
category.list <- c("flower","leaf","beetle")
category <- rep(category.list , c(47*501,46*501,37*501))
wavelength<-rep(dataset[,1])

#transform the data for ploting purpose
dataset.transpose<-gather(dataset[,2:131], key = "species", value = "reflectance", na.rm = FALSE,
                          convert = FALSE, factor_key = FALSE)
dataset.plot.indivisually<-cbind(dataset.transpose, wavelength,category)

#split data by categories for future use
flower.spec<-dataset.plot.indivisually[1:23547,]
leaf.spec<-dataset.plot.indivisually[23548:46593,]
beetle.spec<-dataset.plot.indivisually[46594:65130,]

#merge the spectra before plot here
dataset.plot.indivisually$category2<-factor(dataset.plot.indivisually$category, levels=c("leaf","flower","beetle"))

#plot the spectra of the targets used in this model
ggplot(dataset.plot.indivisually,aes(x=wavelength,y=reflectance, colour=category2, group=species))+
  geom_point(size=.05)+
  geom_line(size=.05)+
  theme(legend.position = "none")+
  scale_color_manual( values = c( "forestgreen", "palevioletred1","cornflowerblue"))+
  facet_grid(category2 ~ .)+
  xlab("Wavelength (nm)")+ylab("Reflectance (%)")+
  theme_classic()+
  guides(colour=FALSE) # remove the legend
```


</br>
</br>

##Visual sensitivities and visual systems
* We created 9 sensitivity curves peaking at 380, 460, 520, 580, 600, 620, 640, 660, 680 nm and classified them into 4 photoreceptor types based on their peaks:
  + Ultraviolet sensitive (UVS): 380 nm
  + Short-wavelength sensitive (SWS): 460 nm
  + Medium-wavelength sensitive (MWS): 520 nm
  + Long-wavelength sensitive (LWS): 580, 600, 620, 640, 660, 680 nm

* Based on these sensitivities, we created several different visual systems for 2 visual models:
  
***
* In the first model ( __Visual model 1__ ), we tested effect of having an LWS photoreceptor. We compared the contrast between 3 trichromatic visual system with varied photoreceptor combination. We also tested an extra receptor the extent to which enhanced the contrast by comparing with a tetrachromatic visual system.
  + Visual systems in __visual model 1__: 
    1. Visual system USM: 380 nm, 460 nm, 520 nm (UVS,SWS,MWS)
    2. Visual system UML: 380 nm, 520 nm, 580 nm (UVS,MWS,LWS)
    3. Visual system USL: 380 nm, 460 nm, 580 nm (UVS,SWS,LWS)
    4. Visual system USML: 380 nm, 460 nm, 520 nm, 580 nm (UVS,SWS,MWS,LWS)

***
* In the second model ( __Visual model 2__ ), we tested how the contrast changed as peak sensitivity increased by systematically increasing the peak sensitivity of the LWS photoreceptor from 580-680 nm.
  + Visual systems in __visual model 2__:
    1. Visual system 580: 380 nm, 460 nm, 520 nm, 580 nm
    2. Visual system 600: 380 nm, 460 nm, 520 nm, 600 nm
    3. Visual system 620: 380 nm, 460 nm, 520 nm, 620 nm
    4. Visual system 640: 380 nm, 460 nm, 520 nm, 640 nm
    5. Visual system 660: 380 nm, 460 nm, 520 nm, 660 nm
    6. Visual system 680: 380 nm, 460 nm, 520 nm, 680 nm


```{r, fig.cap="Sensitivity curves of the photoreceptors with different peak wavelengths."}
wl<-specsensbuprest.model2[,1]
peaks<-gather(specsensbuprest.model2[,2:10], peak, value) %>% cbind(wl)

peak.order <- c("UVS.380.", "UVS.460.", "LWS.520.", "LWS.580.", "LWS.600.", "LWS.620.", "LWS.640.", "LWS.660.", "LWS.680.") #to order the peaks in the legend
ggplot(peaks,aes(x=wl, y=value, col=peak))+
  geom_line()+
  guides(color=guide_legend(title="peak sensitivity"))+
  scale_color_manual(
    values = c("olivedrab4", "orange1", "orange3","darkorange3", "orangered1", "red2","red4", "darkorchid4", "dodgerblue3"),
    labels=c("320 nm", "460 nm","520 nm", "580 nm", "600 nm", "620 nm", "640 nm", "660 nm", "680 nm" ),
    breaks=peak.order)+
  xlab("Wavelength (nm)")+ 
  ylab("Relative spectral sensitivity")+
  theme_classic()

```

</br>
</br>

##Illuminations
* Two light environments: daylight and twilight (to represent red-shifted illumination).
  
    + Daylight: __D65__ (standard daylight) from Commission internationale de l'eclairage CIE
    + Twilight: measured at the Pinnacles Lookout in Alpine National Park, VIC, Australia at 18:15 on September 14th 2019.

```{r, fig.cap="Relative irradiance of the standard daylight and twilight"}
illum <- merge(irradiance.d65, irradiance.twilight) %>% gather(light, illuminace, -wl) 

ggplot(illum, aes(x=wl, y=illuminace, color=light))+
geom_line()+
xlab("Wavelength (nm)")+
ylab("Relative irradiance")+
theme_classic()
```

</br>
</br>

#Run the visual models

</br>
</br>

##First: Quantum catch calculation
* We calculated quantum catch of each visual system based on Fechner's law (the signal of the receptor channel is proportional to the logarithm of the quantum catch).
* The average leaf was used for the background.
* von Kries chromatic adaptation was applied to correct the colour.
```{r,message=FALSE}
#Quantum catch - D65 - Visual model 1
visUVSWMW..=vismodel(dataset[1:501,], visual = specsensbuprest.model1[, 1:4], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
visUV..MWLW=vismodel(dataset[1:501,], visual = specsensbuprest.model1[, c(1,2,4,5)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
visUVSW..LW=vismodel(dataset[1:501,], visual = specsensbuprest.model1[, c(1,2,3,5)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
visUVSWMWLW=vismodel(dataset[1:501,], visual = specsensbuprest.model1[, 1:5], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)

#Quantum catch - D65 - Visual model 2
buprest580=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, 1:5], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest600=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,6)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest620=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,7)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest640=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,8)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest660=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,9)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest680=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,10)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)

#Quantum catch - twilight - Visual model 1
visUVSWMW.._twilight=vismodel(dataset[1:501,], visual = specsensbuprest.model1[, 1:4], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
visUV..MWLW_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.model1[, c(1,2,4,5)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
visUVSW..LW_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.model1[, c(1,2,3,5)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
visUVSWMWLW_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.model1[, 1:5], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)

#Quantum catch - twilight - Visual model 2
buprest580_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, 1:5], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest600_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,6)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest620_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,7)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest640_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,8)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest660_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,9)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest680_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,10)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
```


</br>
</br>

##Second: Contrast calculation {.tabset .tabset-fade .tabset-pills}
* We used a neural noise-limited model where the noise is proportional to the Weber fraction and is independent of the intensity of the signal received.
* Photoreceptor density is based on the opisn gene epxression of Emerald ash borer, _Agrilus planipennis_: 1.14, 1, 1.26, 1.38
* The Weber fraction was asinged to be 0.1

```{r,message=FALSE}
#Contrast calculation- D65 - Visual model 1
CvisUVSWMW.. = coldist(visUVSWMW.., noise="neural", achro=FALSE, n = c(1.14,1,1.26), weber = 0.1, weber.ref = 3)  ##change "weber.ref" to 3
CvisUV..MWLW = coldist(visUV..MWLW, noise="neural", achro=FALSE, n = c(1.14,1.26,1.38), weber = 0.1, weber.ref = 3)
CvisUVSW..LW = coldist(visUVSW..LW, noise="neural", achro=FALSE, n = c(1.14,1,1.38), weber = 0.1, weber.ref = 3)
CvisUVSWMWLW = coldist(visUVSWMWLW, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)

#Contrast calculation- D65 - Visual model 2
Cbuprest580 = coldist(buprest580, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest600 = coldist(buprest600, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest620 = coldist(buprest620, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest640 = coldist(buprest640, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest660 = coldist(buprest660, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest680 = coldist(buprest680, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)

#Contrast calculation- twilight - Visual model 1
CvisUVSWMW.._twilight = coldist(visUVSWMW.._twilight, noise="neural", achro=FALSE, n = c(1.14,1,1.26), weber = 0.1, weber.ref = 3)  ##change "weber.ref" to 3
CvisUV..MWLW_twilight = coldist(visUV..MWLW_twilight, noise="neural", achro=FALSE, n = c(1.14,1.26,1.38), weber = 0.1, weber.ref = 3)
CvisUVSW..LW_twilight = coldist(visUVSW..LW_twilight, noise="neural", achro=FALSE, n = c(1.14,1,1.38), weber = 0.1, weber.ref = 3)
CvisUVSWMWLW_twilight = coldist(visUVSWMWLW_twilight, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)

#Contrast calculation- twilight - Visual model 2
Cbuprest580_twilight = coldist(buprest580_twilight, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest600_twilight = coldist(buprest600_twilight, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest620_twilight = coldist(buprest620_twilight, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest640_twilight = coldist(buprest640_twilight, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest660_twilight = coldist(buprest660_twilight, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest680_twilight = coldist(buprest680_twilight, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
```
```{r}
#combine all contrast value in each comparison group

#Daylight - model 1

##flower vs leaf
Vis1.lf_d65.model1<- CvisUVSWMW..%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis1.lf_d65.model1$vissys<-strrep("Vis1.lf",1)
Vis2.lf_d65.model1<-CvisUV..MWLW%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis2.lf_d65.model1$vissys<-strrep("Vis2.lf",1)
Vis3.lf_d65.model1<-CvisUVSW..LW%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis3.lf_d65.model1$vissys<-strrep("Vis3.lf",1)
Vis4.lf_d65.model1<-CvisUVSWMWLW%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis4.lf_d65.model1$vissys<-strrep("Vis4.lf",1)
allvis.lf_d65.model1<-Vis1.lf_d65.model1 %>% rbind(Vis2.lf_d65.model1) %>% rbind(Vis3.lf_d65.model1) %>%rbind(Vis4.lf_d65.model1)

##beetle vs leaf
Vis1.lb_d65.model1<- CvisUVSWMW..%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis1.lb_d65.model1$vissys<-strrep("Vis1.lb",1)
Vis2.lb_d65.model1<-CvisUV..MWLW%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis2.lb_d65.model1$vissys<-strrep("Vis2.lb",1)
Vis3.lb_d65.model1<-CvisUVSW..LW%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis3.lb_d65.model1$vissys<-strrep("Vis3.lb",1)
Vis4.lb_d65.model1<-CvisUVSWMWLW%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis4.lb_d65.model1$vissys<-strrep("Vis4.lb",1)
allvis.lb_d65.model1<-Vis1.lb_d65.model1 %>% rbind(Vis2.lb_d65.model1) %>% rbind(Vis3.lb_d65.model1) %>%rbind(Vis4.lb_d65.model1)

##beetle vs flower
Vis1.bf_d65.model1<- CvisUVSWMW..%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis1.bf_d65.model1$vissys<-strrep("Vis1.bf",1)
Vis2.bf_d65.model1<-CvisUV..MWLW%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis2.bf_d65.model1$vissys<-strrep("Vis2.bf",1)
Vis3.bf_d65.model1<-CvisUVSW..LW%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis3.bf_d65.model1$vissys<-strrep("Vis3.bf",1)
Vis4.bf_d65.model1<-CvisUVSWMWLW%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis4.bf_d65.model1$vissys<-strrep("Vis4.bf",1)
allvis.bf_d65.model1<-Vis1.bf_d65.model1 %>% rbind(Vis2.bf_d65.model1) %>% rbind(Vis3.bf_d65.model1)%>%
  rbind(Vis4.bf_d65.model1)

#Twiligth - model 1
##flower vs leaf
Vis1.lf_twilight.model1<- CvisUVSWMW.._twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis1.lf_twilight.model1$vissys<-strrep("Vis1.lf",1)
Vis2.lf_twilight.model1<-CvisUV..MWLW_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis2.lf_twilight.model1$vissys<-strrep("Vis2.lf",1)
Vis3.lf_twilight.model1<-CvisUVSW..LW_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis3.lf_twilight.model1$vissys<-strrep("Vis3.lf",1)
Vis4.lf_twilight.model1<-CvisUVSWMWLW_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis4.lf_twilight.model1$vissys<-strrep("Vis4.lf",1)
allvis.lf_twilight.model1<-Vis1.lf_twilight.model1 %>% rbind(Vis2.lf_twilight.model1) %>% rbind(Vis3.lf_twilight.model1) %>%rbind(Vis4.lf_twilight.model1)

##beetle vs leaf
Vis1.lb_twilight.model1<- CvisUVSWMW.._twilight%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis1.lb_twilight.model1$vissys<-strrep("Vis1.lb",1)
Vis2.lb_twilight.model1<-CvisUV..MWLW_twilight%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis2.lb_twilight.model1$vissys<-strrep("Vis2.lb",1)
Vis3.lb_twilight.model1<-CvisUVSW..LW_twilight%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis3.lb_twilight.model1$vissys<-strrep("Vis3.lb",1)
Vis4.lb_twilight.model1<-CvisUVSWMWLW_twilight%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis4.lb_twilight.model1$vissys<-strrep("Vis4.lb",1)
allvis.lb_twilight.model1<-Vis1.lb_twilight.model1 %>% rbind(Vis2.lb_twilight.model1) %>% rbind(Vis3.lb_twilight.model1) %>%rbind(Vis4.lb_twilight.model1)


##beetle vs flower
Vis1.bf_twilight.model1<- CvisUVSWMW.._twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis1.bf_twilight.model1$vissys<-strrep("Vis1.bf",1)
Vis2.bf_twilight.model1<-CvisUV..MWLW_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis2.bf_twilight.model1$vissys<-strrep("Vis2.bf",1)
Vis3.bf_twilight.model1<-CvisUVSW..LW_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis3.bf_twilight.model1$vissys<-strrep("Vis3.bf",1)
Vis4.bf_twilight.model1<-CvisUVSWMWLW_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis4.bf_twilight.model1$vissys<-strrep("Vis4.bf",1)
allvis.bf_twilight.model1<-Vis1.bf_twilight.model1 %>% rbind(Vis2.bf_twilight.model1) %>% rbind(Vis3.bf_twilight.model1) %>%rbind(Vis4.bf_twilight.model1)



#Daylight - model 2
##flower vs leaf
Vis1.lf_d65.model2<- Cbuprest580%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis1.lf_d65.model2$vissys<-strrep("Vis1.lf",1)
Vis2.lf_d65.model2<-Cbuprest600%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis2.lf_d65.model2$vissys<-strrep("Vis2.lf",1)
Vis3.lf_d65.model2<-Cbuprest620%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis3.lf_d65.model2$vissys<-strrep("Vis3.lf",1)
Vis4.lf_d65.model2<-Cbuprest640%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis4.lf_d65.model2$vissys<-strrep("Vis4.lf",1)
Vis5.lf_d65.model2<-Cbuprest660%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis5.lf_d65.model2$vissys<-strrep("Vis5.lf",1)
Vis6.lf_d65.model2<-Cbuprest680%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis6.lf_d65.model2$vissys<-strrep("Vis6.lf",1)

allvis.lf_d65.model2<-Vis1.lf_d65.model2 %>% rbind(Vis2.lf_d65.model2) %>% rbind(Vis3.lf_d65.model2) %>%
  rbind(Vis4.lf_d65.model2) %>%rbind(Vis5.lf_d65.model2) %>%rbind(Vis6.lf_d65.model2)

##beetle vs leaf
Vis1.lb_d65.model2<- Cbuprest580%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis1.lb_d65.model2$vissys<-strrep("Vis1.lb",1)
Vis2.lb_d65.model2<-Cbuprest600%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis2.lb_d65.model2$vissys<-strrep("Vis2.lb",1)
Vis3.lb_d65.model2<-Cbuprest620%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis3.lb_d65.model2$vissys<-strrep("Vis3.lb",1)
Vis4.lb_d65.model2<-Cbuprest640%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis4.lb_d65.model2$vissys<-strrep("Vis4.lb",1)
Vis5.lb_d65.model2<-Cbuprest660%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis5.lb_d65.model2$vissys<-strrep("Vis5.lb",1)
Vis6.lb_d65.model2<-Cbuprest680%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis6.lb_d65.model2$vissys<-strrep("Vis6.lb",1)

allvis.lb_d65.model2<-Vis1.lb_d65.model2 %>% rbind(Vis2.lb_d65.model2) %>% rbind(Vis3.lb_d65.model2) %>%
  rbind(Vis4.lb_d65.model2) %>%rbind(Vis5.lb_d65.model2) %>%rbind(Vis6.lb_d65.model2)


##beetle vs flower
Vis1.bf_d65.model2<- Cbuprest580%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis1.bf_d65.model2$vissys<-strrep("Vis1.bf",1)
Vis2.bf_d65.model2<-Cbuprest600%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis2.bf_d65.model2$vissys<-strrep("Vis2.bf",1)
Vis3.bf_d65.model2<-Cbuprest620%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis3.bf_d65.model2$vissys<-strrep("Vis3.bf",1)
Vis4.bf_d65.model2<-Cbuprest640%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis4.bf_d65.model2$vissys<-strrep("Vis4.bf",1)
Vis5.bf_d65.model2<-Cbuprest660%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis5.bf_d65.model2$vissys<-strrep("Vis5.bf",1)
Vis6.bf_d65.model2<-Cbuprest680%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis6.bf_d65.model2$vissys<-strrep("Vis6.bf",1)

allvis.bf_d65.model2<-Vis1.bf_d65.model2 %>% rbind(Vis2.bf_d65.model2) %>% rbind(Vis3.bf_d65.model2) %>%
  rbind(Vis4.bf_d65.model2) %>%rbind(Vis5.bf_d65.model2) %>%rbind(Vis6.bf_d65.model2)


##Twiligth - model 2
##flower vs leaf
Vis1.lf_twilight.model2<- Cbuprest580_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis1.lf_twilight.model2$vissys<-strrep("Vis1.lf",1)
Vis2.lf_twilight.model2<-Cbuprest600_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis2.lf_twilight.model2$vissys<-strrep("Vis2.lf",1)
Vis3.lf_twilight.model2<-Cbuprest620_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis3.lf_twilight.model2$vissys<-strrep("Vis3.lf",1)
Vis4.lf_twilight.model2<-Cbuprest640_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis4.lf_twilight.model2$vissys<-strrep("Vis4.lf",1)
Vis5.lf_twilight.model2<-Cbuprest660_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis5.lf_twilight.model2$vissys<-strrep("Vis5.lf",1)
Vis6.lf_twilight.model2<-Cbuprest680_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis6.lf_twilight.model2$vissys<-strrep("Vis6.lf",1)

allvis.lf_twilight.model2<-Vis1.lf_twilight.model2 %>% rbind(Vis2.lf_twilight.model2) %>% rbind(Vis3.lf_twilight.model2) %>%
  rbind(Vis4.lf_twilight.model2) %>%rbind(Vis5.lf_twilight.model2) %>%rbind(Vis6.lf_twilight.model2)

##beetle vs leaf
Vis1.lb_twilight.model2<- Cbuprest580_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis1.lb_twilight.model2$vissys<-strrep("Vis1.lb",1)
Vis2.lb_twilight.model2<-Cbuprest600_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis2.lb_twilight.model2$vissys<-strrep("Vis2.lb",1)
Vis3.lb_twilight.model2<-Cbuprest620_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis3.lb_twilight.model2$vissys<-strrep("Vis3.lb",1)
Vis4.lb_twilight.model2<-Cbuprest640_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis4.lb_twilight.model2$vissys<-strrep("Vis4.lb",1)
Vis5.lb_twilight.model2<-Cbuprest660_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis5.lb_twilight.model2$vissys<-strrep("Vis5.lb",1)
Vis6.lb_twilight.model2<-Cbuprest680_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis6.lb_twilight.model2$vissys<-strrep("Vis6.lb",1)

allvis.lb_twilight.model2<-Vis1.lb_twilight.model2 %>% rbind(Vis2.lb_twilight.model2) %>% rbind(Vis3.lb_twilight.model2) %>%
  rbind(Vis4.lb_twilight.model2) %>%rbind(Vis5.lb_twilight.model2) %>%rbind(Vis6.lb_twilight.model2)

##beetle vs flower
Vis1.bf_twilight.model2<- Cbuprest580_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis1.bf_twilight.model2$vissys<-strrep("Vis1.bf",1)
Vis2.bf_twilight.model2<-Cbuprest600_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis2.bf_twilight.model2$vissys<-strrep("Vis2.bf",1)
Vis3.bf_twilight.model2<-Cbuprest620_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis3.bf_twilight.model2$vissys<-strrep("Vis3.bf",1)
Vis4.bf_twilight.model2<-Cbuprest640_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis4.bf_twilight.model2$vissys<-strrep("Vis4.bf",1)
Vis5.bf_twilight.model2<-Cbuprest660_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis5.bf_twilight.model2$vissys<-strrep("Vis5.bf",1)
Vis6.bf_twilight.model2<-Cbuprest680_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis6.bf_twilight.model2$vissys<-strrep("Vis6.bf",1)

allvis.bf_twilight.model2<-Vis1.bf_twilight.model2 %>% rbind(Vis2.bf_twilight.model2) %>% rbind(Vis3.bf_twilight.model2) %>%
  rbind(Vis4.bf_twilight.model2) %>%rbind(Vis5.bf_twilight.model2) %>%rbind(Vis6.bf_twilight.model2)


```

###Visual model 1 {.tabset .tabset-fade .tabset-pills}
The table shows the median contrast in each comparison group
```{r}
#Visul model 1
system.list.model1<- rbind.data.frame("Vis USM", "Vis UML", "Vis USL",  "Vis USML") %>% rename(system = 1) # make a list of system names
```

####Daylight
```{r}
#Daylight
##list contrast from each comparison group
lf.contrast_d65.model1 <- rbind.data.frame(median(Vis1.lf_d65.model1$dS), median(Vis2.lf_d65.model1$dS),median(Vis3.lf_d65.model1$dS),median(Vis4.lf_d65.model1$dS))
lb.contrast_d65.model1 <-rbind.data.frame(median(Vis1.lb_d65.model1$dS),median(Vis2.lb_d65.model1$dS),median(Vis3.lb_d65.model1$dS),median(Vis4.lb_d65.model1$dS))
bf.contrast_d65.model1 <-rbind.data.frame(median(Vis1.bf_d65.model1$dS), median(Vis2.bf_d65.model1$dS),median(Vis3.bf_d65.model1$dS),median(Vis4.bf_d65.model1$dS))
#combind comparison groups together in a table
contrast.list_d65.model1<- system.list.model1 %>%  cbind(lf.contrast_d65.model1) %>% cbind(lb.contrast_d65.model1) %>% cbind(bf.contrast_d65.model1) %>% dplyr:: rename(leaf.vs.flower = 2, leaf.vs.beetle = 3, beetle.vs.flower = 4) %>% pander() 
contrast.list_d65.model1
```
####Twilight
```{r}
#Twilight
##list contrast from each comparison group
lf.contrast_twilight.model1 <- rbind.data.frame(median(Vis1.lf_twilight.model1$dS), median(Vis2.lf_twilight.model1$dS),median(Vis3.lf_twilight.model1$dS),median(Vis4.lf_twilight.model1$dS))
lb.contrast_twilight.model1 <-rbind.data.frame(median(Vis1.lb_twilight.model1$dS),median(Vis2.lb_twilight.model1$dS),median(Vis3.lb_twilight.model1$dS),median(Vis4.lb_twilight.model1$dS))
bf.contrast_twilight.model1 <-rbind.data.frame(median(Vis1.bf_twilight.model1$dS), median(Vis2.bf_twilight.model1$dS),median(Vis3.bf_twilight.model1$dS),median(Vis4.bf_twilight.model1$dS))
#combind comparison groups together in a table
contrast.list_twilight.model1<- system.list.model1 %>%  cbind(lf.contrast_twilight.model1) %>% cbind(lb.contrast_twilight.model1) %>% cbind(bf.contrast_twilight.model1) %>% dplyr:: rename(leaf.vs.flower = 2, leaf.vs.beetle = 3, beetle.vs.flower = 4) %>% pander()
contrast.list_twilight.model1
```
###Visual model 2 {.tabset .tabset-fade .tabset-pills}
The table shows the median contrast in each comparison group
```{r}
system.list.model2<- rbind.data.frame("Vis 580", "Vis 600", "Vis 620", "Vis 640", "Vis 660", "Vis 680") %>% rename(system = 1) # make a list of system names
```
####Daylight
```{r}
#Daylight
##list contrast from each comparison group
lf.contrast_d65.model2 <- rbind.data.frame(median(Vis1.lf_d65.model2$dS), median(Vis2.lf_d65.model2$dS),median(Vis3.lf_d65.model2$dS),median(Vis4.lf_d65.model2$dS),median(Vis5.lf_d65.model2$dS),median(Vis6.lf_d65.model2$dS))
lb.contrast_d65.model2 <-rbind.data.frame(median(Vis1.lb_d65.model2$dS),median(Vis2.lb_d65.model2$dS),median(Vis3.lb_d65.model2$dS),median(Vis4.lb_d65.model2$dS),median(Vis5.lb_d65.model2$dS),median(Vis6.lb_d65.model2$dS))
bf.contrast_d65.model2 <-rbind.data.frame(median(Vis1.bf_d65.model2$dS), median(Vis2.bf_d65.model2$dS),median(Vis3.bf_d65.model2$dS),median(Vis4.bf_d65.model2$dS),median(Vis5.bf_d65.model2$dS),median(Vis6.bf_d65.model2$dS))
#combind comparison groups together in a table
contrast.list_d65.model2<- system.list.model2 %>%  cbind(lf.contrast_d65.model2) %>% cbind(lb.contrast_d65.model2) %>% cbind(bf.contrast_d65.model2) %>% dplyr:: rename(leaf.vs.flower = 2, leaf.vs.beetle = 3, beetle.vs.flower = 4) %>% pander() 
contrast.list_d65.model2
```
####Twilight
```{r}
#Twilight
##list contrast from each comparison group
lf.contrast_twilight.model2 <- rbind.data.frame(median(Vis1.lf_twilight.model2$dS), median(Vis2.lf_twilight.model2$dS),median(Vis3.lf_twilight.model2$dS),median(Vis4.lf_twilight.model2$dS),median(Vis5.lf_twilight.model2$dS),median(Vis6.lf_twilight.model2$dS))
lb.contrast_twilight.model2 <-rbind.data.frame(median(Vis1.lb_twilight.model2$dS),median(Vis2.lb_twilight.model2$dS),median(Vis3.lb_twilight.model2$dS),median(Vis4.lb_twilight.model2$dS),median(Vis5.lb_twilight.model2$dS),median(Vis6.lb_twilight.model2$dS))
bf.contrast_twilight.model2 <-rbind.data.frame(median(Vis1.bf_twilight.model2$dS), median(Vis2.bf_twilight.model2$dS),median(Vis3.bf_twilight.model2$dS),median(Vis4.bf_twilight.model2$dS),median(Vis5.bf_twilight.model2$dS),median(Vis6.bf_twilight.model2$dS))
#combind comparison groups together in a table
contrast.list_twilight.model2<- system.list.model2 %>%  cbind(lf.contrast_twilight.model2) %>% cbind(lb.contrast_twilight.model2) %>% cbind(bf.contrast_twilight.model2) %>% dplyr:: rename(leaf.vs.flower = 2, leaf.vs.beetle = 3, beetle.vs.flower = 4) %>% pander() 
contrast.list_twilight.model2
```
</br>
</br>

#Compare contrasts
* To compare contrasts between visual systems, We performed Wald chisquare tests on generalised linear mixed models (GLMM) followed by posthoc tests.

* In the models, we assigned
    + Indenpendent variable: __contrast__
    + Dependent variable: 
        + Fixed factor: __visual system__
        + Random factor: __sample ID__ of both targets in the comparison

```{r} 
#creat different comparison groups for furthur GLMM analysis
#Organize data before GLMM

#D65 - visual model 1
##flower vs leaf
CvisUVSWMW...leaf.vs.flower=
  CvisUVSWMW.. %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvisUV..MWLW.leaf.vs.flower=
  CvisUV..MWLW %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvisUVSW..LW.leaf.vs.flower=
  CvisUVSW..LW %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvisUVSWMWLW.leaf.vs.flower=
  CvisUVSWMWLW %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

C.leaf.vs.flower.model1=
  CvisUVSWMW...leaf.vs.flower %>% rbind(CvisUV..MWLW.leaf.vs.flower) %>% 
  rbind(CvisUVSW..LW.leaf.vs.flower)%>% rbind(CvisUVSWMWLW.leaf.vs.flower)

contrast.UVSWMW...leaf.vs.flower<-CvisUVSWMW...leaf.vs.flower[,3]
contrast.UV..MWLW.leaf.vs.flower<-CvisUV..MWLW.leaf.vs.flower[,3]
contrast.UVSW..LW.leaf.vs.flower<-CvisUVSW..LW.leaf.vs.flower[,3]
contrast.UVSWMWLW.leaf.vs.flower<-CvisUVSWMWLW.leaf.vs.flower[,3]

com.contrast.leaf.vs.flower.model1<-cbind(CvisUVSWMW...leaf.vs.flower[,1:2],contrast.UVSWMW...leaf.vs.flower,contrast.UV..MWLW.leaf.vs.flower,contrast.UVSW..LW.leaf.vs.flower,contrast.UVSWMWLW.leaf.vs.flower)
compare.leaf.vs.flower.model1 <- com.contrast.leaf.vs.flower.model1 %>%
  gather(key = "peak_wl.leaf.vs.flower", value = "dS", 3:6)

##beetle vs leaf
CvisUVSWMW...leaf.vs.beetle=
  CvisUVSWMW.. %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvisUV..MWLW.leaf.vs.beetle=
  CvisUV..MWLW %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvisUVSW..LW.leaf.vs.beetle=
  CvisUVSW..LW %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvisUVSWMWLW.leaf.vs.beetle=
  CvisUVSWMWLW %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

C.leaf.vs.beetle.model1=
  CvisUVSWMW...leaf.vs.beetle %>% rbind(CvisUV..MWLW.leaf.vs.beetle) %>% 
  rbind(CvisUVSW..LW.leaf.vs.beetle)%>%  rbind(CvisUVSWMWLW.leaf.vs.beetle)

contrast.UVSWMW...leaf.vs.beetle<-CvisUVSWMW...leaf.vs.beetle[,3]
contrast.UV..MWLW.leaf.vs.beetle<-CvisUV..MWLW.leaf.vs.beetle[,3]
contrast.UVSW..LW.leaf.vs.beetle<-CvisUVSW..LW.leaf.vs.beetle[,3]
contrast.UVSWMWLW.leaf.vs.beetle<-CvisUVSWMWLW.leaf.vs.beetle[,3]

com.contrast.leaf.vs.beetle.model1<-cbind(CvisUVSWMW...leaf.vs.beetle[,1:2],contrast.UVSWMW...leaf.vs.beetle,contrast.UV..MWLW.leaf.vs.beetle,contrast.UVSW..LW.leaf.vs.beetle,contrast.UVSWMWLW.leaf.vs.beetle)
compare.leaf.vs.beetle.model1 <- com.contrast.leaf.vs.beetle.model1 %>%
  gather(key = "peak_wl.leaf.vs.beetle", value = "dS", 3:6)

##beetle vs flower
CvisUVSWMW...flower.vs.beetle=
  CvisUVSWMW.. %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvisUV..MWLW.flower.vs.beetle=
  CvisUV..MWLW %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvisUVSW..LW.flower.vs.beetle=
  CvisUVSW..LW %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvisUVSWMWLW.flower.vs.beetle=
  CvisUVSWMWLW %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

C.flower.vs.beetle.model1=
  CvisUVSWMW...flower.vs.beetle %>% rbind(CvisUV..MWLW.flower.vs.beetle) %>% 
  rbind(CvisUVSW..LW.flower.vs.beetle) %>%  rbind(CvisUVSWMWLW.flower.vs.beetle)

contrast.UVSWMW...flower.vs.beetle<-CvisUVSWMW...flower.vs.beetle[,3]
contrast.UV..MWLW.flower.vs.beetle<-CvisUV..MWLW.flower.vs.beetle[,3]
contrast.UVSW..LW.flower.vs.beetle<-CvisUVSW..LW.flower.vs.beetle[,3]
contrast.UVSWMWLW.flower.vs.beetle<-CvisUVSWMWLW.flower.vs.beetle[,3]

com.contrast.flower.vs.beetle.model1<-cbind(CvisUVSWMW...flower.vs.beetle[,1:2],contrast.UVSWMW...flower.vs.beetle,contrast.UV..MWLW.flower.vs.beetle,contrast.UVSW..LW.flower.vs.beetle,contrast.UVSWMWLW.flower.vs.beetle)
compare.flower.vs.beetle.model1 <- com.contrast.flower.vs.beetle.model1 %>%
  gather(key = "peak_wl.flower.vs.beetle", value = "dS", 3:6)



#D65 - visual model 2
##flower vs leaf
Cbuprest580.leaf.vs.flower=
  Cbuprest580 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest600.leaf.vs.flower=
  Cbuprest600 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest620.leaf.vs.flower=
  Cbuprest620 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest640.leaf.vs.flower=
  Cbuprest640 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest660.leaf.vs.flower=
  Cbuprest660 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest680.leaf.vs.flower=
  Cbuprest680 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

Cbuprest.leaf.vs.flower.model2=
  Cbuprest580.leaf.vs.flower %>% rbind(Cbuprest600.leaf.vs.flower) %>%
  rbind(Cbuprest620.leaf.vs.flower)%>% rbind(Cbuprest640.leaf.vs.flower) %>% rbind(Cbuprest660.leaf.vs.flower) %>%
  rbind(Cbuprest680.leaf.vs.flower)

bup580.leaf.vs.flower<-Cbuprest580.leaf.vs.flower[,3]
bup600.leaf.vs.flower<-Cbuprest600.leaf.vs.flower[,3]
bup620.leaf.vs.flower<-Cbuprest620.leaf.vs.flower[,3]
bup640.leaf.vs.flower<-Cbuprest640.leaf.vs.flower[,3]
bup660.leaf.vs.flower<-Cbuprest660.leaf.vs.flower[,3]
bup680.leaf.vs.flower<-Cbuprest680.leaf.vs.flower[,3]

com.bupcontrast.leaf.vs.flower.model2<-cbind(Cbuprest.leaf.vs.flower.model2[,1:2],bup580.leaf.vs.flower,bup600.leaf.vs.flower,bup620.leaf.vs.flower,bup640.leaf.vs.flower,bup660.leaf.vs.flower,bup680.leaf.vs.flower)
compare.leaf.vs.flower.model2 <- com.bupcontrast.leaf.vs.flower.model2 %>%
  gather(key = "peak_wl.leaf.vs.flower", value = "dS", 3:8)

##beetle vs leaf
Cbuprest580.leaf.vs.beetle=
  Cbuprest580 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest600.leaf.vs.beetle=
  Cbuprest600 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest620.leaf.vs.beetle=
  Cbuprest620 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest640.leaf.vs.beetle=
  Cbuprest640 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest660.leaf.vs.beetle=
  Cbuprest660 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest680.leaf.vs.beetle=
  Cbuprest680 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

Cbuprest.leaf.vs.beetle.model2=
  Cbuprest580.leaf.vs.beetle  %>% rbind(Cbuprest600.leaf.vs.beetle)%>%
  rbind(Cbuprest620.leaf.vs.beetle)%>% rbind(Cbuprest640.leaf.vs.beetle) %>% rbind(Cbuprest660.leaf.vs.beetle) %>% 
  rbind(Cbuprest680.leaf.vs.beetle)

bup580.leaf.vs.beetle<-Cbuprest580.leaf.vs.beetle[,3]
bup600.leaf.vs.beetle<-Cbuprest600.leaf.vs.beetle[,3]
bup620.leaf.vs.beetle<-Cbuprest620.leaf.vs.beetle[,3]
bup640.leaf.vs.beetle<-Cbuprest640.leaf.vs.beetle[,3]
bup660.leaf.vs.beetle<-Cbuprest660.leaf.vs.beetle[,3]
bup680.leaf.vs.beetle<-Cbuprest680.leaf.vs.beetle[,3]

com.bupcontrast.leaf.vs.beetle.model2<-cbind(Cbuprest.leaf.vs.beetle.model2[,1:2],bup580.leaf.vs.beetle,bup600.leaf.vs.beetle,bup620.leaf.vs.beetle,bup640.leaf.vs.beetle,bup660.leaf.vs.beetle,bup680.leaf.vs.beetle)
compare.leaf.vs.beetle.model2 <- com.bupcontrast.leaf.vs.beetle.model2 %>%
  gather(key = "peak_wl.leaf.vs.beetle", value = "dS", 3:8)

##beetle vs flower
Cbuprest580.flower.vs.beetle=
  Cbuprest580 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest600.flower.vs.beetle=
  Cbuprest600 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest620.flower.vs.beetle=
  Cbuprest620 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest640.flower.vs.beetle=
  Cbuprest640 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest660.flower.vs.beetle=
  Cbuprest660 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest680.flower.vs.beetle=
  Cbuprest680 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

Cbuprest.flower.vs.beetle.model2=
  Cbuprest580.flower.vs.beetle %>% rbind(Cbuprest600.flower.vs.beetle) %>% 
  rbind(Cbuprest620.flower.vs.beetle)%>% rbind(Cbuprest640.flower.vs.beetle) %>% 
  rbind(Cbuprest660.flower.vs.beetle)%>% rbind(Cbuprest680.flower.vs.beetle)

bup580.flower.vs.beetle<-Cbuprest580.flower.vs.beetle[,3]
bup600.flower.vs.beetle<-Cbuprest600.flower.vs.beetle[,3]
bup620.flower.vs.beetle<-Cbuprest620.flower.vs.beetle[,3]
bup640.flower.vs.beetle<-Cbuprest640.flower.vs.beetle[,3]
bup660.flower.vs.beetle<-Cbuprest660.flower.vs.beetle[,3]
bup680.flower.vs.beetle<-Cbuprest680.flower.vs.beetle[,3]

com.bupcontrast.flower.vs.beetle.model2<-cbind(Cbuprest.flower.vs.beetle.model2[,1:2],bup580.flower.vs.beetle,bup600.flower.vs.beetle,bup620.flower.vs.beetle,bup640.flower.vs.beetle,bup660.flower.vs.beetle,bup680.flower.vs.beetle)
compare.flower.vs.beetle.model2 <- com.bupcontrast.flower.vs.beetle.model2 %>%
  gather(key = "peak_wl.flower.vs.beetle", value = "dS", 3:8)


#Twilight - visual model 1
##flower vs leaf
CvisUVSWMW...leaf.vs.flower_twilight=
  CvisUVSWMW.._twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvisUV..MWLW.leaf.vs.flower_twilight=
  CvisUV..MWLW_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvisUVSW..LW.leaf.vs.flower_twilight=
  CvisUVSW..LW_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvisUVSWMWLW.leaf.vs.flower_twilight=
  CvisUVSWMWLW_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

C.leaf.vs.flower_twilight.model1=
  CvisUVSWMW...leaf.vs.flower_twilight %>% rbind(CvisUV..MWLW.leaf.vs.flower_twilight) %>% 
  rbind(CvisUVSW..LW.leaf.vs.flower_twilight)%>% rbind(CvisUVSWMWLW.leaf.vs.flower_twilight)

contrast.UVSWMW...leaf.vs.flower_twilight<-CvisUVSWMW...leaf.vs.flower_twilight[,3]
contrast.UV..MWLW.leaf.vs.flower_twilight<-CvisUV..MWLW.leaf.vs.flower_twilight[,3]
contrast.UVSW..LW.leaf.vs.flower_twilight<-CvisUVSW..LW.leaf.vs.flower_twilight[,3]
contrast.UVSWMWLW.leaf.vs.flower_twilight<-CvisUVSWMWLW.leaf.vs.flower_twilight[,3]

com.contrast.leaf.vs.flower_twilight.model1<-cbind(CvisUVSWMW...leaf.vs.flower_twilight[,1:2],contrast.UVSWMW...leaf.vs.flower_twilight,contrast.UV..MWLW.leaf.vs.flower_twilight,contrast.UVSW..LW.leaf.vs.flower_twilight,contrast.UVSWMWLW.leaf.vs.flower_twilight)
compare.leaf.vs.flower_twilight.model1 <- com.contrast.leaf.vs.flower_twilight.model1 %>%
  gather(key = "peak_wl.leaf.vs.flower", value = "dS", 3:6)

##beetle vs leaf
CvisUVSWMW...leaf.vs.beetle_twilight=
  CvisUVSWMW.._twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvisUV..MWLW.leaf.vs.beetle_twilight=
  CvisUV..MWLW_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvisUVSW..LW.leaf.vs.beetle_twilight=
  CvisUVSW..LW_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvisUVSWMWLW.leaf.vs.beetle_twilight=
  CvisUVSWMWLW_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

C.leaf.vs.beetle_twilight.model1=
  CvisUVSWMW...leaf.vs.beetle_twilight %>% rbind(CvisUV..MWLW.leaf.vs.beetle_twilight) %>% 
  rbind(CvisUVSW..LW.leaf.vs.beetle_twilight)%>%  rbind(CvisUVSWMWLW.leaf.vs.beetle_twilight)

contrast.UVSWMW...leaf.vs.beetle_twilight<-CvisUVSWMW...leaf.vs.beetle_twilight[,3]
contrast.UV..MWLW.leaf.vs.beetle_twilight<-CvisUV..MWLW.leaf.vs.beetle_twilight[,3]
contrast.UVSW..LW.leaf.vs.beetle_twilight<-CvisUVSW..LW.leaf.vs.beetle_twilight[,3]
contrast.UVSWMWLW.leaf.vs.beetle_twilight<-CvisUVSWMWLW.leaf.vs.beetle_twilight[,3]

com.contrast.leaf.vs.beetle_twilight.model1<-cbind(CvisUVSWMW...leaf.vs.beetle_twilight[,1:2],contrast.UVSWMW...leaf.vs.beetle_twilight,contrast.UV..MWLW.leaf.vs.beetle_twilight,contrast.UVSW..LW.leaf.vs.beetle_twilight,contrast.UVSWMWLW.leaf.vs.beetle_twilight)
compare.leaf.vs.beetle_twilight.model1 <- com.contrast.leaf.vs.beetle_twilight.model1 %>%
  gather(key = "peak_wl.leaf.vs.beetle", value = "dS", 3:6)

##beetle vs flower
CvisUVSWMW...flower.vs.beetle_twilight=
  CvisUVSWMW.._twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvisUV..MWLW.flower.vs.beetle_twilight=
  CvisUV..MWLW_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvisUVSW..LW.flower.vs.beetle_twilight=
  CvisUVSW..LW_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvisUVSWMWLW.flower.vs.beetle_twilight=
  CvisUVSWMWLW_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

C.flower.vs.beetle_twilight.model1=
  CvisUVSWMW...flower.vs.beetle_twilight %>% rbind(CvisUV..MWLW.flower.vs.beetle_twilight) %>% 
  rbind(CvisUVSW..LW.flower.vs.beetle_twilight) %>%  rbind(CvisUVSWMWLW.flower.vs.beetle_twilight)

contrast.UVSWMW...flower.vs.beetle_twilight<-CvisUVSWMW...flower.vs.beetle_twilight[,3]
contrast.UV..MWLW.flower.vs.beetle_twilight<-CvisUV..MWLW.flower.vs.beetle_twilight[,3]
contrast.UVSW..LW.flower.vs.beetle_twilight<-CvisUVSW..LW.flower.vs.beetle_twilight[,3]
contrast.UVSWMWLW.flower.vs.beetle_twilight<-CvisUVSWMWLW.flower.vs.beetle_twilight[,3]

com.contrast.flower.vs.beetle_twilight.model1<-cbind(CvisUVSWMW...flower.vs.beetle_twilight[,1:2],contrast.UVSWMW...flower.vs.beetle_twilight,contrast.UV..MWLW.flower.vs.beetle_twilight,contrast.UVSW..LW.flower.vs.beetle_twilight,contrast.UVSWMWLW.flower.vs.beetle_twilight)
compare.flower.vs.beetle_twilight.model1 <- com.contrast.flower.vs.beetle_twilight.model1 %>%
  gather(key = "peak_wl.flower.vs.beetle", value = "dS", 3:6)



#Twilight - visual model 2
##flower vs leaf
Cbuprest580.leaf.vs.flower_twilight=
  Cbuprest580_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest600.leaf.vs.flower_twilight=
  Cbuprest600_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest620.leaf.vs.flower_twilight=
  Cbuprest620_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest640.leaf.vs.flower_twilight=
  Cbuprest640_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest660.leaf.vs.flower_twilight=
  Cbuprest660_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest680.leaf.vs.flower_twilight=
  Cbuprest680_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

Cbuprest.leaf.vs.flower_twilight.model2=
  Cbuprest580.leaf.vs.flower_twilight %>% rbind(Cbuprest600.leaf.vs.flower_twilight) %>%
  rbind(Cbuprest620.leaf.vs.flower_twilight)%>% rbind(Cbuprest640.leaf.vs.flower_twilight) %>% rbind(Cbuprest660.leaf.vs.flower_twilight) %>% rbind(Cbuprest680.leaf.vs.flower_twilight)

bup580.leaf.vs.flower_twilight<-Cbuprest580.leaf.vs.flower_twilight[,3]
bup600.leaf.vs.flower_twilight<-Cbuprest600.leaf.vs.flower_twilight[,3]
bup620.leaf.vs.flower_twilight<-Cbuprest620.leaf.vs.flower_twilight[,3]
bup640.leaf.vs.flower_twilight<-Cbuprest640.leaf.vs.flower_twilight[,3]
bup660.leaf.vs.flower_twilight<-Cbuprest660.leaf.vs.flower_twilight[,3]
bup680.leaf.vs.flower_twilight<-Cbuprest680.leaf.vs.flower_twilight[,3]

com.bupcontrast.leaf.vs.flower_twilight.model2<-cbind(Cbuprest.leaf.vs.flower_twilight.model2[,1:2],bup580.leaf.vs.flower_twilight,bup600.leaf.vs.flower_twilight,bup620.leaf.vs.flower_twilight,bup640.leaf.vs.flower_twilight,bup660.leaf.vs.flower_twilight,bup680.leaf.vs.flower_twilight)
compare.leaf.vs.flower_twilight.model2 <- com.bupcontrast.leaf.vs.flower_twilight.model2 %>%
  gather(key = "peak_wl.leaf.vs.flower", value = "dS", 3:8)

##beetle vs leaf
Cbuprest580.leaf.vs.beetle_twilight=
  Cbuprest580_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest600.leaf.vs.beetle_twilight=
  Cbuprest600_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest620.leaf.vs.beetle_twilight=
  Cbuprest620_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest640.leaf.vs.beetle_twilight=
  Cbuprest640_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest660.leaf.vs.beetle_twilight=
  Cbuprest660_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest680.leaf.vs.beetle_twilight=
  Cbuprest680_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

Cbuprest.leaf.vs.beetle_twilight.model2=
  Cbuprest580.leaf.vs.beetle_twilight  %>% rbind(Cbuprest600.leaf.vs.beetle_twilight)%>%
  rbind(Cbuprest620.leaf.vs.beetle_twilight)%>% rbind(Cbuprest640.leaf.vs.beetle_twilight) %>%
  rbind(Cbuprest660.leaf.vs.beetle_twilight) %>% rbind(Cbuprest680.leaf.vs.beetle_twilight)

bup580.leaf.vs.beetle_twilight<-Cbuprest580.leaf.vs.beetle_twilight[,3]
bup600.leaf.vs.beetle_twilight<-Cbuprest600.leaf.vs.beetle_twilight[,3]
bup620.leaf.vs.beetle_twilight<-Cbuprest620.leaf.vs.beetle_twilight[,3]
bup640.leaf.vs.beetle_twilight<-Cbuprest640.leaf.vs.beetle_twilight[,3]
bup660.leaf.vs.beetle_twilight<-Cbuprest660.leaf.vs.beetle_twilight[,3]
bup680.leaf.vs.beetle_twilight<-Cbuprest680.leaf.vs.beetle_twilight[,3]

com.bupcontrast.leaf.vs.beetle_twilight.model2<-cbind(Cbuprest.leaf.vs.beetle_twilight.model2[,1:2],bup580.leaf.vs.beetle_twilight,bup600.leaf.vs.beetle_twilight,bup620.leaf.vs.beetle_twilight,bup640.leaf.vs.beetle_twilight,bup660.leaf.vs.beetle_twilight,bup680.leaf.vs.beetle_twilight)
compare.leaf.vs.beetle_twilight.model2 <- com.bupcontrast.leaf.vs.beetle_twilight.model2 %>%
  gather(key = "peak_wl.leaf.vs.beetle", value = "dS", 3:8)

##beetle vs flower
Cbuprest580.flower.vs.beetle_twilight=
  Cbuprest580_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest600.flower.vs.beetle_twilight=
  Cbuprest600_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest620.flower.vs.beetle_twilight=
  Cbuprest620_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest640.flower.vs.beetle_twilight=
  Cbuprest640_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest660.flower.vs.beetle_twilight=
  Cbuprest660_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest680.flower.vs.beetle_twilight=
  Cbuprest680_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

Cbuprest.flower.vs.beetle_twilight.model2=
  Cbuprest580.flower.vs.beetle_twilight %>%rbind(Cbuprest600.flower.vs.beetle_twilight) %>% 
  rbind(Cbuprest620.flower.vs.beetle_twilight) %>% rbind(Cbuprest640.flower.vs.beetle_twilight) %>% 
  rbind(Cbuprest660.flower.vs.beetle_twilight) %>% rbind(Cbuprest680.flower.vs.beetle_twilight)

bup580.flower.vs.beetle_twilight<-Cbuprest580.flower.vs.beetle_twilight[,3]
bup600.flower.vs.beetle_twilight<-Cbuprest600.flower.vs.beetle_twilight[,3]
bup620.flower.vs.beetle_twilight<-Cbuprest620.flower.vs.beetle_twilight[,3]
bup640.flower.vs.beetle_twilight<-Cbuprest640.flower.vs.beetle_twilight[,3]
bup660.flower.vs.beetle_twilight<-Cbuprest660.flower.vs.beetle_twilight[,3]
bup680.flower.vs.beetle_twilight<-Cbuprest680.flower.vs.beetle_twilight[,3]

com.bupcontrast.flower.vs.beetle_twilight.model2<-cbind(Cbuprest.flower.vs.beetle_twilight.model2[,1:2],bup580.flower.vs.beetle_twilight,bup600.flower.vs.beetle_twilight,bup620.flower.vs.beetle_twilight,bup640.flower.vs.beetle_twilight,bup660.flower.vs.beetle_twilight,bup680.flower.vs.beetle_twilight)
compare.flower.vs.beetle_twilight.model2 <- com.bupcontrast.flower.vs.beetle_twilight.model2 %>%
  gather(key = "peak_wl.flower.vs.beetle", value = "dS", 3:8)

```

##Check assumptions {.tabset .tabset-fade .tabset-pills}

* Before running GLMM, we first check if the data follows the assumption of normality and homogeneity of variance

</br>

Click the tabs to choose the assumptions ( __Normality__ / __Homogeneity__ ) of the visual models ( __Visual model 1__ / __Visual model 2__ ) under different light conditions ( __Daylight__ / __Twilight__)

</br>


```{r}
#checking assumptions
##D65 - visual model 1
res.leaf.vs.flower_d65.model1<-lm(compare.leaf.vs.flower.model1$dS ~ compare.leaf.vs.flower.model1$peak_wl.leaf.vs.flower)
res.leaf.vs.beetle_d65.model1<-lm(compare.leaf.vs.beetle.model1$dS ~ compare.leaf.vs.beetle.model1$peak_wl.leaf.vs.beetle)
res.flower.vs.beetle_d65.model1<-lm(compare.flower.vs.beetle.model1$dS ~ compare.flower.vs.beetle.model1$peak_wl.flower.vs.beetle)

##D65 - visual model 2
res.leaf.vs.flower_d65.model2<-lm(compare.leaf.vs.flower.model2$dS ~ compare.leaf.vs.flower.model2$peak_wl.leaf.vs.flower)
res.leaf.vs.beetle_d65.model2<-lm(compare.leaf.vs.beetle.model2$dS ~ compare.leaf.vs.beetle.model2$peak_wl.leaf.vs.beetle)
res.flower.vs.beetle_d65.model2<-lm(compare.flower.vs.beetle.model2$dS ~ compare.flower.vs.beetle.model2$peak_wl.flower.vs.beetle)

##Twilight - visual model 1
res.leaf.vs.flower_twilight.model1<-lm(compare.leaf.vs.flower.model1$dS ~ compare.leaf.vs.flower.model1$peak_wl.leaf.vs.flower)
res.leaf.vs.beetle_twilight.model1<-lm(compare.leaf.vs.beetle.model1$dS ~ compare.leaf.vs.beetle.model1$peak_wl.leaf.vs.beetle)
res.flower.vs.beetle_twilight.model1<-lm(compare.flower.vs.beetle.model1$dS ~ compare.flower.vs.beetle.model1$peak_wl.flower.vs.beetle)

##Twilight - visual model 2
res.leaf.vs.flower_twilight.model2<-lm(compare.leaf.vs.flower.model2$dS ~ compare.leaf.vs.flower.model2$peak_wl.leaf.vs.flower)
res.leaf.vs.beetle_twilight.model2<-lm(compare.leaf.vs.beetle.model2$dS ~ compare.leaf.vs.beetle.model2$peak_wl.leaf.vs.beetle)
res.flower.vs.beetle_twilight.model2<-lm(compare.flower.vs.beetle.model2$dS ~ compare.flower.vs.beetle.model2$peak_wl.flower.vs.beetle)
```

### Normality {.tabset .tabset-fade .tabset-pills}
#### Visual model 1 {.tabset .tabset-fade .tabset-pills}

##### D65 
```{r}
par (mfrow=c(1,3),pin=c(1.5, 1.5))
qqnorm(res.leaf.vs.flower_d65.model1$residuals, main = "Leaf vs Flower")
qqnorm(res.leaf.vs.beetle_d65.model1$residuals, main = "Leaf vs Beetle")
qqnorm(res.flower.vs.beetle_d65.model1$residuals, main = "Beetle vs Flower")
```

##### Twilight
```{r}
par (mfrow=c(1,3),pin=c(1.5, 1.5))
qqnorm(res.leaf.vs.flower_twilight.model1$residuals, main = "Leaf vs Flower")
qqnorm(res.leaf.vs.beetle_twilight.model1$residuals, main = "Leaf vs Beetle")
qqnorm(res.flower.vs.beetle_twilight.model1$residuals, main = "Beetle vs Flower")
```

#### Visual model 2 {.tabset .tabset-fade .tabset-pills}
##### D65 
```{r}
par (mfrow=c(1,3),pin=c(1.5, 1.5))
qqnorm(res.leaf.vs.flower_d65.model2$residuals, main = "Leaf vs Flower")
qqnorm(res.leaf.vs.beetle_d65.model2$residuals, main = "Leaf vs Beetle")
qqnorm(res.flower.vs.beetle_d65.model2$residuals, main = "Beetle vs Flower")
```

##### Twilight
```{r}
par (mfrow=c(1,3),pin=c(1.5, 1.5))
qqnorm(res.leaf.vs.flower_twilight.model2$residuals, main = "Leaf vs Flower")
qqnorm(res.leaf.vs.beetle_twilight.model2$residuals, main = "Leaf vs Beetle")
qqnorm(res.flower.vs.beetle_twilight.model2$residuals, main = "Beetle vs Flower")
```

### Homoscedasticity {.tabset .tabset-fade .tabset-pills}
#### Visual model 1 {.tabset .tabset-fade .tabset-pills}

##### D65
```{r}
par (mfrow=c(1,3),oma=c(2,2,0,0)) #oma=c() to creat space for common lables
boxplot(compare.leaf.vs.flower.model1$dS~compare.leaf.vs.flower.model1$peak_wl.leaf.vs.flower, las=2,
        main = "Leaf vs Flower",
        names=c("Vis UML", "Vis USL", "Vis USM", "Vis USML"))
boxplot(compare.leaf.vs.beetle.model1$dS~compare.leaf.vs.beetle.model1$peak_wl.leaf.vs.beetle, las=2,
        main = "Leaf vs Beetle",
        names=c("Vis UML", "Vis USL", "Vis USM", "Vis USML"))
boxplot(compare.flower.vs.beetle.model1$dS~compare.flower.vs.beetle.model1$peak_wl.flower.vs.beetle, las=2,
        main = "Beetle vs Flower",
        names=c("Vis UML", "Vis USL", "Vis USM", "Vis USML"))
mtext("Visual system",side=1,line=0,outer=TRUE,cex=1.3) #side assigns the position of the text e.g. bottom
mtext("Contrast (JND)",side=2,line=0,outer=TRUE,cex=1.3,las=0) #las assigns the orientation of the text
```

##### Twilight
```{r}
par (mfrow=c(1,3),oma=c(2,2,0,0))
boxplot(compare.leaf.vs.flower_twilight.model1$dS~compare.leaf.vs.flower_twilight.model1$peak_wl.leaf.vs.flower, las=2,
        main = "Leaf vs Flower",
        names=c("Vis UML", "Vis USL", "Vis USM", "Vis USML"))
boxplot(compare.leaf.vs.beetle_twilight.model1$dS~compare.leaf.vs.beetle_twilight.model1$peak_wl.leaf.vs.beetle, las=2,
        main = "Leaf vs Beetle",
        names=c("Vis UML", "Vis USL", "Vis USM", "Vis USML"))
boxplot(compare.flower.vs.beetle_twilight.model1$dS~compare.flower.vs.beetle_twilight.model1$peak_wl.flower.vs.beetle, las=2,
        main = "Beetle vs Flower",
        names=c("Vis UML", "Vis USL", "Vis USM", "Vis USML"))
mtext("Visual system",side=1,line=0,outer=TRUE,cex=1.3)
mtext("Contrast (JND)",side=2,line=0,outer=TRUE,cex=1.3,las=0)
```

#### Visual model 2 {.tabset .tabset-fade .tabset-pills}
##### D65
```{r}
par (mfrow=c(1,3),oma=c(2,2,0,0))
boxplot(compare.leaf.vs.flower.model2$dS~compare.leaf.vs.flower.model2$peak_wl.leaf.vs.flower, las=2,
        main = "Leaf vs Flower",
        names=c("Vis 580", "Vis 600", "Vis 620", "Vis 640", "Vis 660", "Vis 680"))
boxplot(compare.leaf.vs.beetle.model2$dS~compare.leaf.vs.beetle.model2$peak_wl.leaf.vs.beetle, las=2,
        main = "Leaf vs Beetle",
        names=c("Vis 580", "Vis 600", "Vis 620", "Vis 640", "Vis 660", "Vis 680"))
boxplot(compare.flower.vs.beetle.model2$dS~compare.flower.vs.beetle.model2$peak_wl.flower.vs.beetle, las=2,
        main = "Beetle vs Flower",
        names=c("Vis 580", "Vis 600", "Vis 620", "Vis 640", "Vis 660", "Vis 680"))
mtext("Visual system",side=1,line=0,outer=TRUE,cex=1.3)
mtext("Contrast (JND)",side=2,line=0,outer=TRUE,cex=1.3,las=0)
```

##### Twilight 
```{r}
par (mfrow=c(1,3),oma=c(2,2,0,0))
boxplot(compare.leaf.vs.flower_twilight.model2$dS~compare.leaf.vs.flower_twilight.model2$peak_wl.leaf.vs.flower, las=2,
        main = "Leaf vs Flower",
        names=c("Vis 580", "Vis 600", "Vis 620", "Vis 640", "Vis 660", "Vis 680"))
boxplot(compare.leaf.vs.beetle_twilight.model2$dS~compare.leaf.vs.beetle_twilight.model2$peak_wl.leaf.vs.beetle, las=2,
        main = "Leaf vs Beetle",
        names=c("Vis 580", "Vis 600", "Vis 620", "Vis 640", "Vis 660", "Vis 680"))
boxplot(compare.flower.vs.beetle_twilight.model2$dS~compare.flower.vs.beetle_twilight.model2$peak_wl.flower.vs.beetle, las=2,
        main = "Beetle vs Flower",
        names=c("Vis 580", "Vis 600", "Vis 620", "Vis 640", "Vis 660", "Vis 680"))
mtext("Visual system",side=1,line=0,outer=TRUE,cex=1.3)
mtext("Contrast (JND)",side=2,line=0,outer=TRUE,cex=1.3,las=0)
```


</br>
</br>

##GLMM results

</br>

```{r}
#GLMM - D65 - visual model 1
##Leaf vs Flower
m.leaf.vs.flower_d65.model1 <- lmer(dS~peak_wl.leaf.vs.flower + (1|patch2) + (1|patch1), data = compare.leaf.vs.flower.model1,REML=F)
sum.leaf.vs.flower_d65.model1<-summary(glht(m.leaf.vs.flower_d65.model1, linfct = mcp(peak_wl.leaf.vs.flower = "Tukey")), test = adjusted("bonferroni"))
#REML=F, in order to fit the model using the likelihood ratio test. Otherwise, the lmer default will fit the model using the REML (REstricted Maximum Likelihood) criterion.

##Leaf vs Beetle
m.leaf.vs.beetle_d65.model1 <- lmer(dS~peak_wl.leaf.vs.beetle + (1|patch2) + (1|patch1), data = compare.leaf.vs.beetle.model1,REML=F)
sum.leaf.vs.beetle_d65.model1 <- summary(glht(m.leaf.vs.beetle_d65.model1, linfct = mcp(peak_wl.leaf.vs.beetle = "Tukey")), test = adjusted("bonferroni"))

##Beetle vs Flower
m.flower.vs.beetle_d65.model1 <- lmer(dS~peak_wl.flower.vs.beetle + (1|patch2) + (1|patch1), data = compare.flower.vs.beetle.model1,REML=F)
sum.flower.vs.beetle_d65.model1 <-summary(glht(m.flower.vs.beetle_d65.model1, linfct = mcp(peak_wl.flower.vs.beetle = "Tukey")), test = adjusted("bonferroni"))

###reshape data for heatmap
p1_d65.model1<-sum.leaf.vs.flower_d65.model1[["test"]][["pvalues"]]
p2_d65.model1<-sum.leaf.vs.beetle_d65.model1[["test"]][["pvalues"]]
p3_d65.model1<-sum.flower.vs.beetle_d65.model1[["test"]][["pvalues"]]

VislistA_d65.model1<-c("Vis USL", "Vis USM","Vis USML","Vis USM","Vis USML","Vis USML")
VislistB_d65.model1<-c("Vis UML", "Vis UML","Vis UML","Vis USL","Vis USL","Vis USW")

heat_d65.model1<-data.frame(names(p1_d65.model1),as.numeric(str_extract(p1_d65.model1,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2_d65.model1,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3_d65.model1,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, leaf.vs.flower = 2, leaf.vs.beetle = 3, flower.vs.beetle = 4) %>% 
  cbind(VislistA_d65.model1) %>% 
  cbind(VislistB_d65.model1) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat_d65.model1$sig.leaf.vs.flower[heat_d65.model1$leaf.vs.flower > 0.05] <- ""
heat_d65.model1$sig.leaf.vs.flower[heat_d65.model1$leaf.vs.flower < 0.05] <- "*"
heat_d65.model1$sig.leaf.vs.flower[heat_d65.model1$leaf.vs.flower < 0.01] <- "**"
heat_d65.model1$sig.leaf.vs.flower[heat_d65.model1$leaf.vs.flower < 0.0001] <- "***"
heat_d65.model1$sig.leaf.vs.beetle[heat_d65.model1$leaf.vs.beetle > 0.05] <- ""
heat_d65.model1$sig.leaf.vs.beetle[heat_d65.model1$leaf.vs.beetle < 0.05] <- "*"
heat_d65.model1$sig.leaf.vs.beetle[heat_d65.model1$leaf.vs.beetle < 0.01] <- "**"
heat_d65.model1$sig.leaf.vs.beetle[heat_d65.model1$leaf.vs.beetle < 0.0001] <- "***"
heat_d65.model1$sig.flower.vs.beetle[heat_d65.model1$flower.vs.beetle > 0.05] <- ""
heat_d65.model1$sig.flower.vs.beetle[heat_d65.model1$flower.vs.beetle < 0.05] <- "*"
heat_d65.model1$sig.flower.vs.beetle[heat_d65.model1$flower.vs.beetle < 0.01] <- "**"
heat_d65.model1$sig.flower.vs.beetle[heat_d65.model1$flower.vs.beetle < 0.0001] <- "***"


#GLMM - D65 - visual model 2
##Leaf vs Flower
m.leaf.vs.flower_d65.model2 <- lmer(dS~peak_wl.leaf.vs.flower + (1|patch2) + (1|patch1), data = compare.leaf.vs.flower.model2,REML=F)
sum.leaf.vs.flower_d65.model2 <- summary(glht(m.leaf.vs.flower_d65.model2, linfct = mcp(peak_wl.leaf.vs.flower = "Tukey")), test = adjusted("bonferroni"))
##Leaf vs Beetle
m.leaf.vs.beetle_d65.model2 <- lmer(dS~peak_wl.leaf.vs.beetle + (1|patch2) + (1|patch1), data = compare.leaf.vs.beetle.model2,REML=F)
sum.leaf.vs.beetle_d65.model2 <- summary(glht(m.leaf.vs.beetle_d65.model2, linfct = mcp(peak_wl.leaf.vs.beetle = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Flower
m.flower.vs.beetle_d65.model2 <- lmer(dS~peak_wl.flower.vs.beetle + (1|patch2) + (1|patch1), data = compare.flower.vs.beetle.model2,REML=F)
sum.flower.vs.beetle_d65.model2 <- summary(glht(m.flower.vs.beetle_d65.model2, linfct = mcp(peak_wl.flower.vs.beetle = "Tukey")), test = adjusted("bonferroni"))

###reshape data for heatmap
p1_d65.model2<-sum.leaf.vs.flower_d65.model2[["test"]][["pvalues"]]
p2_d65.model2<-sum.leaf.vs.beetle_d65.model2[["test"]][["pvalues"]]
p3_d65.model2<-sum.flower.vs.beetle_d65.model2[["test"]][["pvalues"]]

VislistA_d65.model2<-c("Vis 600", "Vis 620","Vis 640","Vis 660","Vis 680","Vis 620","Vis 640","Vis 660","Vis 680","Vis 640","Vis 660","Vis 680","Vis 660","Vis 680","Vis 680")
VislistB_d65.model2<-c("Vis 580","Vis 580","Vis 580","Vis 580","Vis 580","Vis 600","Vis 600","Vis 600","Vis 600","Vis 620","Vis 620","Vis 620","Vis 640","Vis 640","Vis 660")

heat_d65.model2<-data.frame(names(p1_d65.model2),as.numeric(str_extract(p1_d65.model2,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2_d65.model2,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3_d65.model2,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, leaf.vs.flower = 2, leaf.vs.beetle = 3, flower.vs.beetle = 4) %>% 
  cbind(VislistA_d65.model2) %>% 
  cbind(VislistB_d65.model2) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat_d65.model2$sig.leaf.vs.flower[heat_d65.model2$leaf.vs.flower > 0.05] <- ""
heat_d65.model2$sig.leaf.vs.flower[heat_d65.model2$leaf.vs.flower < 0.05] <- "*"
heat_d65.model2$sig.leaf.vs.flower[heat_d65.model2$leaf.vs.flower < 0.01] <- "**"
heat_d65.model2$sig.leaf.vs.flower[heat_d65.model2$leaf.vs.flower < 0.0001] <- "***"
heat_d65.model2$sig.leaf.vs.beetle[heat_d65.model2$leaf.vs.beetle > 0.05] <- ""
heat_d65.model2$sig.leaf.vs.beetle[heat_d65.model2$leaf.vs.beetle < 0.05] <- "*"
heat_d65.model2$sig.leaf.vs.beetle[heat_d65.model2$leaf.vs.beetle < 0.01] <- "**"
heat_d65.model2$sig.leaf.vs.beetle[heat_d65.model2$leaf.vs.beetle < 0.0001] <- "***"
heat_d65.model2$sig.flower.vs.beetle[heat_d65.model2$flower.vs.beetle > 0.05] <- ""
heat_d65.model2$sig.flower.vs.beetle[heat_d65.model2$flower.vs.beetle < 0.05] <- "*"
heat_d65.model2$sig.flower.vs.beetle[heat_d65.model2$flower.vs.beetle < 0.01] <- "**"
heat_d65.model2$sig.flower.vs.beetle[heat_d65.model2$flower.vs.beetle < 0.0001] <- "***"




#GLMM - Twilight - visual model 1
##Leaf vs Flower
m.leaf.vs.flower_twilight.model1 <- lmer(dS~peak_wl.leaf.vs.flower + (1|patch2) + (1|patch1), data = compare.leaf.vs.flower_twilight.model1,REML=F)
sum.leaf.vs.flower_twilight.model1 <- summary(glht(m.leaf.vs.flower_twilight.model1, linfct = mcp(peak_wl.leaf.vs.flower = "Tukey")), test = adjusted("bonferroni"))
##Leaf vs Beetle
m.leaf.vs.beetle_twilight.model1 <- lmer(dS~peak_wl.leaf.vs.beetle + (1|patch2) + (1|patch1), data = compare.leaf.vs.beetle_twilight.model1,REML=F)
sum.leaf.vs.beetle_twilight.model1<-summary(glht(m.leaf.vs.beetle_twilight.model1, linfct = mcp(peak_wl.leaf.vs.beetle = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Flower
m.flower.vs.beetle_twilight.model1 <- lmer(dS~peak_wl.flower.vs.beetle + (1|patch2) + (1|patch1), data = compare.flower.vs.beetle_twilight.model1,REML=F)
sum.flower.vs.beetle_twilight.model1<-summary(glht(m.flower.vs.beetle_twilight.model1, linfct = mcp(peak_wl.flower.vs.beetle = "Tukey")), test = adjusted("bonferroni"))
###reshape data for heatmap
p1_twilight.model1<-sum.leaf.vs.flower_twilight.model1[["test"]][["pvalues"]]
p2_twilight.model1<-sum.leaf.vs.beetle_twilight.model1[["test"]][["pvalues"]]
p3_twilight.model1<-sum.flower.vs.beetle_twilight.model1[["test"]][["pvalues"]]

VislistA_twilight.model1<-c("Vis USL", "Vis USM","Vis USML","Vis USM","Vis USML","Vis USML")
VislistB_twilight.model1<-c("Vis UML", "Vis UML","Vis UML","Vis USL","Vis USL","Vis USW")

heat_twilight.model1<-data.frame(names(p1_twilight.model1),as.numeric(str_extract(p1_twilight.model1,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2_twilight.model1,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3_twilight.model1,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, leaf.vs.flower = 2, leaf.vs.beetle = 3, flower.vs.beetle = 4) %>% 
  cbind(VislistA_twilight.model1) %>% 
  cbind(VislistB_twilight.model1) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat_twilight.model1$sig.leaf.vs.flower[heat_twilight.model1$leaf.vs.flower > 0.05] <- ""
heat_twilight.model1$sig.leaf.vs.flower[heat_twilight.model1$leaf.vs.flower < 0.05] <- "*"
heat_twilight.model1$sig.leaf.vs.flower[heat_twilight.model1$leaf.vs.flower < 0.01] <- "**"
heat_twilight.model1$sig.leaf.vs.flower[heat_twilight.model1$leaf.vs.flower < 0.0001] <- "***"
heat_twilight.model1$sig.leaf.vs.beetle[heat_twilight.model1$leaf.vs.beetle > 0.05] <- ""
heat_twilight.model1$sig.leaf.vs.beetle[heat_twilight.model1$leaf.vs.beetle < 0.05] <- "*"
heat_twilight.model1$sig.leaf.vs.beetle[heat_twilight.model1$leaf.vs.beetle < 0.01] <- "**"
heat_twilight.model1$sig.leaf.vs.beetle[heat_twilight.model1$leaf.vs.beetle < 0.0001] <- "***"
heat_twilight.model1$sig.flower.vs.beetle[heat_twilight.model1$flower.vs.beetle > 0.05] <- ""
heat_twilight.model1$sig.flower.vs.beetle[heat_twilight.model1$flower.vs.beetle < 0.05] <- "*"
heat_twilight.model1$sig.flower.vs.beetle[heat_twilight.model1$flower.vs.beetle < 0.01] <- "**"
heat_twilight.model1$sig.flower.vs.beetle[heat_twilight.model1$flower.vs.beetle < 0.0001] <- "***"




#GLMM - Twilight - visual model 2
##Leaf vs Flower
m.leaf.vs.flower_twilight.model2 <- lmer(dS~peak_wl.leaf.vs.flower + (1|patch2) + (1|patch1), data = compare.leaf.vs.flower_twilight.model2,REML=F)
sum.leaf.vs.flower_twilight.model2 <- summary(glht(m.leaf.vs.flower_twilight.model2, linfct = mcp(peak_wl.leaf.vs.flower = "Tukey")), test = adjusted("bonferroni"))
##Leaf vs Beetle
m.leaf.vs.beetle_twilight.model2 <- lmer(dS~peak_wl.leaf.vs.beetle + (1|patch2) + (1|patch1), data = compare.leaf.vs.beetle_twilight.model2,REML=F)
sum.leaf.vs.beetle_twilight.model2 <- summary(glht(m.leaf.vs.beetle_twilight.model2, linfct = mcp(peak_wl.leaf.vs.beetle = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Flower
m.flower.vs.beetle_twilight.model2 <- lmer(dS~peak_wl.flower.vs.beetle + (1|patch2) + (1|patch1), data = compare.flower.vs.beetle_twilight.model2,REML=F)
sum.flower.vs.beetle_twilight.model2 <-summary(glht(m.flower.vs.beetle_twilight.model2, linfct = mcp(peak_wl.flower.vs.beetle = "Tukey")), test = adjusted("bonferroni"))
###reshape data for heatmap
p1_twilight.model2<-sum.leaf.vs.flower_twilight.model2[["test"]][["pvalues"]]
p2_twilight.model2<-sum.leaf.vs.beetle_twilight.model2[["test"]][["pvalues"]]
p3_twilight.model2<-sum.flower.vs.beetle_twilight.model2[["test"]][["pvalues"]]

VislistA_twilight.model2<-c("Vis 600", "Vis 620","Vis 640","Vis 660","Vis 680","Vis 620","Vis 640","Vis 660","Vis 680","Vis 640","Vis 660","Vis 680","Vis 660","Vis 680","Vis 680")
VislistB_twilight.model2<-c("Vis 580","Vis 580","Vis 580","Vis 580","Vis 580","Vis 600","Vis 600","Vis 600","Vis 600","Vis 620","Vis 620","Vis 620","Vis 640","Vis 640","Vis 660")

heat_twilight.model2<-data.frame(names(p1_twilight.model2),as.numeric(str_extract(p1_twilight.model2,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2_twilight.model2,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3_twilight.model2,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, leaf.vs.flower = 2, leaf.vs.beetle = 3, flower.vs.beetle = 4) %>% 
  cbind(VislistA_twilight.model2) %>% 
  cbind(VislistB_twilight.model2) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat_twilight.model2$sig.leaf.vs.flower[heat_twilight.model2$leaf.vs.flower > 0.05] <- ""
heat_twilight.model2$sig.leaf.vs.flower[heat_twilight.model2$leaf.vs.flower < 0.05] <- "*"
heat_twilight.model2$sig.leaf.vs.flower[heat_twilight.model2$leaf.vs.flower < 0.01] <- "**"
heat_twilight.model2$sig.leaf.vs.flower[heat_twilight.model2$leaf.vs.flower < 0.0001] <- "***"
heat_twilight.model2$sig.leaf.vs.beetle[heat_twilight.model2$leaf.vs.beetle > 0.05] <- ""
heat_twilight.model2$sig.leaf.vs.beetle[heat_twilight.model2$leaf.vs.beetle < 0.05] <- "*"
heat_twilight.model2$sig.leaf.vs.beetle[heat_twilight.model2$leaf.vs.beetle < 0.01] <- "**"
heat_twilight.model2$sig.leaf.vs.beetle[heat_twilight.model2$leaf.vs.beetle < 0.0001] <- "***"
heat_twilight.model2$sig.flower.vs.beetle[heat_twilight.model2$flower.vs.beetle > 0.05] <- ""
heat_twilight.model2$sig.flower.vs.beetle[heat_twilight.model2$flower.vs.beetle < 0.05] <- "*"
heat_twilight.model2$sig.flower.vs.beetle[heat_twilight.model2$flower.vs.beetle < 0.01] <- "**"
heat_twilight.model2$sig.flower.vs.beetle[heat_twilight.model2$flower.vs.beetle < 0.0001] <- "***"
```

### Result of visual model 1: comparing visual systems with different photoreceptor combination {.tabset .tabset-fade .tabset-pills}

</br>

Click the tabs to see the results in each comparison groups ( __Leaf vs. Flower__ / __Leaf vs. Beetle__ / __Beetle vs. Flower__) and under different light conditions ( __Daylight__ / __Twilight__)

</br>

#### __Leaf vs Flower__ {.tabset .tabset-fade .tabset-pills}
#####Daylight{.tabset .tabset-fade .tabset-pills}

```{r}
Anova(m.leaf.vs.flower_d65.model1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.model1, aes(x=VislistA_d65.model1, y=VislistB_d65.model1, fill=leaf.vs.flower)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.model1, VislistB_d65.model1, label = paste(format(round(leaf.vs.flower, 2), nsmall = 2), sig.leaf.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.leaf.vs.flower_d65.model1
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.flower_twilight.model1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.model1, aes(x=VislistA_twilight.model1, y=VislistB_twilight.model1, fill=leaf.vs.flower)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.model1, VislistB_twilight.model1, label = paste(format(round(leaf.vs.flower, 2), nsmall = 2), sig.leaf.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.leaf.vs.flower_twilight.model1
```

#### __Leaf vs Beetle__ {.tabset .tabset-fade .tabset-pills}
#####Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.beetle_d65.model1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.model1, aes(x=VislistA_d65.model1, y=VislistB_d65.model1, fill=leaf.vs.beetle)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.model1, VislistB_d65.model1, label = paste(format(round(leaf.vs.beetle, 2), nsmall = 2), sig.leaf.vs.beetle))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.leaf.vs.beetle_d65.model1
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.beetle_twilight.model1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.model1, aes(x=VislistA_twilight.model1, y=VislistB_twilight.model1, fill=leaf.vs.beetle)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.model1, VislistB_twilight.model1, label = paste(format(round(leaf.vs.beetle, 2), nsmall = 2), sig.leaf.vs.beetle))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.leaf.vs.beetle_twilight.model1
```

#### __Beetle vs Flower__ {.tabset .tabset-fade .tabset-pills}
#####Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.beetle_d65.model1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.model1, aes(x=VislistA_d65.model1, y=VislistB_d65.model1, fill=flower.vs.beetle)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.model1, VislistB_d65.model1, label = paste(format(round(flower.vs.beetle, 2), nsmall = 2), sig.flower.vs.beetle)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour 
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.flower.vs.beetle_d65.model1
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.beetle_twilight.model1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.model1, aes(x=VislistA_twilight.model1, y=VislistB_twilight.model1, fill=flower.vs.beetle)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.model1, VislistB_twilight.model1, label = paste(format(round(flower.vs.beetle, 2), nsmall = 2), sig.flower.vs.beetle)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.leaf.vs.flower_twilight.model1
```


</br>
</br>


### Result of visual model 2: comparing visual systems with different peak of LWS photoreceptor {.tabset .tabset-fade .tabset-pills}

</br>

Click the tabs to see the results in each comparison groups ( __Leaf vs. Flower__ / __Leaf vs. Beetle__ / __Beetle vs. Flower__) and under different light conditions ( __Daylight__ / __Twilight__)

</br>

#### __Leaf vs Flower__ {.tabset .tabset-fade .tabset-pills}

#####Daylight{.tabset .tabset-fade .tabset-pills}

```{r}
Anova(m.leaf.vs.flower_d65.model2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.model2, aes(x=VislistA_d65.model2, y=VislistB_d65.model2, fill=leaf.vs.flower)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.model2, VislistB_d65.model2, label = paste(format(round(leaf.vs.flower, 2), nsmall = 2), sig.leaf.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.leaf.vs.flower_d65.model2
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.flower_twilight.model2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.model2, aes(x=VislistA_twilight.model2, y=VislistB_twilight.model2, fill=leaf.vs.flower)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.model2, VislistB_twilight.model2, label = paste(format(round(leaf.vs.flower, 2), nsmall = 2), sig.leaf.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.leaf.vs.flower_twilight.model2
```

#### __Leaf vs Beetle__ {.tabset .tabset-fade .tabset-pills}
#####Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.beetle_d65.model2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.model2, aes(x=VislistA_d65.model2, y=VislistB_d65.model2, fill=leaf.vs.beetle)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.model2, VislistB_d65.model2, label = paste(format(round(leaf.vs.beetle, 2), nsmall = 2), sig.leaf.vs.beetle))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.leaf.vs.beetle_d65.model2
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.beetle_twilight.model2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.model2, aes(x=VislistA_twilight.model2, y=VislistB_twilight.model2, fill=leaf.vs.beetle)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.model2, VislistB_twilight.model2, label = paste(format(round(leaf.vs.beetle, 2), nsmall = 2), sig.leaf.vs.beetle))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.leaf.vs.beetle_twilight.model2
```

#### __Beetle vs Flower__ {.tabset .tabset-fade .tabset-pills}
#####Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.beetle_d65.model2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.model2, aes(x=VislistA_d65.model2, y=VislistB_d65.model2, fill=flower.vs.beetle)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.model2, VislistB_d65.model2, label = paste(format(round(flower.vs.beetle, 2), nsmall = 2), sig.flower.vs.beetle)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour 
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.flower.vs.beetle_d65.model2
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.beetle_twilight.model2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.model2, aes(x=VislistA_twilight.model2, y=VislistB_twilight.model2, fill=leaf.vs.flower)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.model2, VislistB_twilight.model2,  label = paste(format(round(leaf.vs.flower, 2), nsmall = 2), sig.leaf.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.leaf.vs.flower_twilight.model2
```


</br>
</br>

#Plot the contasts {.tabset .tabset-fade .tabset-pills}
* Colours are in accordence with the actual sample colouration in visible range.
* Lines of the same colors connect the same samples

</br>

##Visual model 1 {.tabset .tabset-fade .tabset-pills}
###Daylight
```{r,fig.cap="Contrast comparison between visual systems with different photoreceptor combinations. A dot in each visual system shows a representative contrast of a flower pattern (beetle pattern in the middle panel), which is the average of its contrast to all leaves (all beetle patterns on the right panel). Colours of the dots reflcet the visible colour of the flower (beetle patterns in the middle panel) with the lines of the same colour connecting the results between different visual systems. Black dots show the median of the representative contrast in a visual system. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1. Two contrasts > 10 JND are from flowers that have very low UV reflectance."}
#import the flower color code 
color.code<-read.csv("data/color code list.csv",header=TRUE) 

#creat a list of species name used in the spec data and 
name.list<-unique(dataset.transpose$species) %>% 
  sort() %>% #order it alphebatically as well
  data.frame() %>% dplyr::rename(species = ".")#make it a data frame and name the column "species"

#creat flower name list for visual model 1
flower.colour.model1 <- name.list %>% filter(str_detect(species, "flower")) %>% #select flower names
  cbind(color.code %>% filter(str_detect(type, "flower")) %>% arrange(name)) %>% #select flower color codes and order it alphebatically
  dplyr::select(-type) %>% #remove the redundant column
  mutate(count = 4) %>% uncount(count) #repeat each row for 4 times for 4 visual systems

#creat beetle name list for visual model 1
beetle.colour.model1 <- name.list %>% filter(str_detect(species, "beetle")) %>% #select flower names
  cbind(color.code %>% filter(str_detect(type, "beetle")) %>% arrange(name)) %>% #select flower color codes and order it alphebatically
  dplyr::select(-type) %>% #remove the redundant column
  mutate(count = 4) %>% uncount(count) #repeat each row for 4 times for 4 visual systems



#make flower vs leaf plot
##add the mean
mean.lf_d65.model1<-allvis.lf_d65.model1 %>% mutate(patch3 = paste(allvis.lf_d65.model1$vissys,allvis.lf_d65.model1$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.lf=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lf_d65.model1)[names(mean.lf_d65.model1) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lf_d65.model1<-mean.lf_d65.model1[order(mean.lf_d65.model1$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lf_d65.model1$match.name<-flower.colour.model1$species # this column is just for checking if match correctly
mean.lf_d65.model1$colour<-flower.colour.model1$colour


lf_d65.model1<-ggplot(mean.lf_d65.model1, aes(x=vissys, y=mean.dS.lf,group=flowerID))+
  geom_point(col=mean.lf_d65.model1$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lf_d65.model1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf"),
                   labels=c("Vis USM", "Vis UML", "Vis USL","Vis USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lf_d65.model1, aes(x= "Vis1.lf", y= median(Vis1.lf_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_d65.model1, aes(x= "Vis2.lf", y= median(Vis2.lf_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_d65.model1, aes(x= "Vis3.lf", y= median(Vis3.lf_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_d65.model1, aes(x= "Vis4.lf", y= median(Vis4.lf_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Flower")+
  annotate("text", x = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf"), y = 15, label =c("a","b","a","c")) #add stitistical info



#make beetle vs leaf plot
##add the mean
mean.lb_d65.model1<-allvis.lb_d65.model1 %>% mutate(patch3 = paste(allvis.lb_d65.model1$vissys,allvis.lb_d65.model1$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.lb=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lb_d65.model1)[names(mean.lb_d65.model1) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lb_d65.model1<-mean.lb_d65.model1[order(mean.lb_d65.model1$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lb_d65.model1$match.name<-beetle.colour.model1$species # this column is just for checking if match correctly
mean.lb_d65.model1$colour<-beetle.colour.model1$colour


lb_d65.model1<-ggplot(mean.lb_d65.model1, aes(x=vissys, y=mean.dS.lb,group=beetleID))+
  geom_point(col=mean.lb_d65.model1$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.lb_d65.model1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.background = element_blank(), 
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb"),
                   labels=c("Vis USM", "Vis UML", "Vis USL","Vis USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lb_d65.model1, aes(x= "Vis1.lb", y= median(Vis1.lb_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_d65.model1, aes(x= "Vis2.lb", y= median(Vis2.lb_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_d65.model1, aes(x= "Vis3.lb", y= median(Vis3.lb_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_d65.model1, aes(x= "Vis4.lb", y= median(Vis4.lb_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Beetle")+annotate("text", x = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb"), y = 15, label =c("a","b","b","c")) #add stitistical info


#make beetle vs flower plot
##add the mean
mean.bf_d65.model1<-allvis.bf_d65.model1 %>% mutate(patch3 = paste(allvis.bf_d65.model1$vissys,allvis.bf_d65.model1$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.bf_d65.model1)[names(mean.bf_d65.model1) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf_d65.model1<-mean.bf_d65.model1[order(mean.bf_d65.model1$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf_d65.model1$match.name<-flower.colour.model1$species # this column is just for checking if match correctly
mean.bf_d65.model1$colour<-flower.colour.model1$colour

bf_d65.model1<-ggplot(mean.bf_d65.model1, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf_d65.model1$colour, size=3, alpha=0.7) + 
  geom_line(col=mean.bf_d65.model1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA),#make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf"),
                   labels=c("Vis USM", "Vis UML", "Vis USL","Vis USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf_d65.model1, aes(x= "Vis1.bf", y= median(Vis1.bf_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_d65.model1, aes(x= "Vis2.bf", y= median(Vis2.bf_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_d65.model1, aes(x= "Vis3.bf", y= median(Vis3.bf_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_d65.model1, aes(x= "Vis4.bf", y= median(Vis4.bf_d65.model1$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf"), y = 15, label =c("a","b","a","c")) #add stitistical info

#plot the contrasts from the 3 comparison groups together
figure_d65.model1 <- ggarrange(lf_d65.model1,lb_d65.model1,bf_d65.model1, ncol = 3, nrow = 1)
figure_d65.model1
```

###Twilight
```{r,fig.cap="Contrast comparison between visual systems with different photoreceptor combinations. A dot in each visual system shows a representative contrast of a flower pattern (beetle pattern in the middle panel), which is the average of its contrast to all leaves (all beetle patterns on the right panel). Colours of the dots reflcet the visible colour of the flower (beetle patterns in the middle panel) with the lines of the same colour connecting the results between different visual systems. Black dots show the median of the representative contrast in a visual system. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1. Two contrasts > 10 JND are from flowers that have very low UV reflectance."}
#make flower vs leaf plot
##add the mean
mean.lf_twilight.model1<-allvis.lf_twilight.model1 %>% mutate(patch3 = paste(allvis.lf_twilight.model1$vissys,allvis.lf_twilight.model1$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.lf=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lf_twilight.model1)[names(mean.lf_twilight.model1) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lf_twilight.model1<-mean.lf_twilight.model1[order(mean.lf_twilight.model1$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lf_twilight.model1$match.name<-flower.colour.model1$species # this column is just for checking if match correctly
mean.lf_twilight.model1$colour<-flower.colour.model1$colour


lf_twilight.model1<-ggplot(mean.lf_twilight.model1, aes(x=vissys, y=mean.dS.lf,group=flowerID))+
  geom_point(col=mean.lf_twilight.model1$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lf_twilight.model1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf"),
                   labels=c("Vis USM", "Vis UML", "Vis USL","Vis USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lf_twilight.model1, aes(x= "Vis1.lf", y= median(Vis1.lf_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_twilight.model1, aes(x= "Vis2.lf", y= median(Vis2.lf_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_twilight.model1, aes(x= "Vis3.lf", y= median(Vis3.lf_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_twilight.model1, aes(x= "Vis4.lf", y= median(Vis4.lf_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Flower")+
  annotate("text", x = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf"), y = 15, label =c("a","b","a","c")) #add stitistical info


#make beetle vs leaf plot
##add the mean
mean.lb_twilight.model1<-allvis.lb_twilight.model1 %>% mutate(patch3 = paste(allvis.lb_twilight.model1$vissys,allvis.lb_twilight.model1$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.lb=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lb_twilight.model1)[names(mean.lb_twilight.model1) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lb_twilight.model1<-mean.lb_twilight.model1[order(mean.lb_twilight.model1$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lb_twilight.model1$match.name<-beetle.colour.model1$species # this column is just for checking if match correctly
mean.lb_twilight.model1$colour<-beetle.colour.model1$colour


lb_twilight.model1<-ggplot(mean.lb_twilight.model1, aes(x=vissys, y=mean.dS.lb,group=beetleID))+
  geom_point(col=mean.lb_twilight.model1$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.lb_twilight.model1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.background = element_blank(), 
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb"),
                   labels=c("Vis USM", "Vis UML", "Vis USL","Vis USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lb_twilight.model1, aes(x= "Vis1.lb", y= median(Vis1.lb_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_twilight.model1, aes(x= "Vis2.lb", y= median(Vis2.lb_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_twilight.model1, aes(x= "Vis3.lb", y= median(Vis3.lb_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_twilight.model1, aes(x= "Vis4.lb", y= median(Vis4.lb_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Beetle")+
  annotate("text", x = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb"), y = 15, label =c("a","b","c","d")) #add stitistical info



#make beetle vs flower plot
##add the mean
mean.bf_twilight.model1<-allvis.bf_twilight.model1 %>% mutate(patch3 = paste(allvis.bf_twilight.model1$vissys,allvis.bf_twilight.model1$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.bf_twilight.model1)[names(mean.bf_twilight.model1) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf_twilight.model1<-mean.bf_twilight.model1[order(mean.bf_twilight.model1$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf_twilight.model1$match.name<-flower.colour.model1$species # this column is just for checking if match correctly
mean.bf_twilight.model1$colour<-flower.colour.model1$colour

bf_twilight.model1<-ggplot(mean.bf_twilight.model1, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf_twilight.model1$colour, size=3, alpha=0.7) + 
  geom_line(col=mean.bf_twilight.model1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA),#make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf"),
                   labels=c("Vis USM", "Vis UML", "Vis USL","Vis USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf_twilight.model1, aes(x= "Vis1.bf", y= median(Vis1.bf_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_twilight.model1, aes(x= "Vis2.bf", y= median(Vis2.bf_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_twilight.model1, aes(x= "Vis3.bf", y= median(Vis3.bf_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_twilight.model1, aes(x= "Vis4.bf", y= median(Vis4.bf_twilight.model1$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf"), y = 15, label =c("a","b","a","c")) #add stitistical info



#plot the contrasts from the 3 comparison groups together
figure_twilight.model1 <- ggarrange(lf_twilight.model1,lb_twilight.model1,bf_twilight.model1, ncol = 3, nrow = 1)
figure_twilight.model1
```


##Visual model 2 {.tabset .tabset-fade .tabset-pills}
###Daylight
```{r,fig.cap="Contrast comparison between visual systems with the LWS photoreceptor peaking at different wavelengths. A dot in each visual system shows a representative contrast of a flower pattern (beetle pattern in the middle panel), which is the average of its contrast to all leaves (all beetle patterns on the right panel). Colours of the dots reflect the visible colour of the flower (beetle patterns in the middle panel) with the lines of the same colour connecting the results between different visual systems. Black dots show the median of the representative contrast in a visual system. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1. Two contrasts > 10 JND are from flowers that have very low UV reflectance."}
#creat flower name list for visual model 2
flower.colour.model2 <- name.list %>% filter(str_detect(species, "flower")) %>% #select flower names
  cbind(color.code %>% filter(str_detect(type, "flower")) %>% arrange(name)) %>% #select flower color codes and order it alphebatically
  dplyr::select(-type) %>% #remove the redundant column
  mutate(count = 6) %>% uncount(count) #repeat each row for 4 times for 6 visual systems

#creat beetle name list for visual model 2
beetle.colour.model2 <- name.list %>% filter(str_detect(species, "beetle")) %>% #select flower names
  cbind(color.code %>% filter(str_detect(type, "beetle")) %>% arrange(name)) %>% #select flower color codes and order it alphebatically
  dplyr::select(-type) %>% #remove the redundant column
  mutate(count = 6) %>% uncount(count) #repeat each row for 4 times for 6 visual systems


#make flower vs leaf plot
##add the mean
mean.lf_d65.model2<-allvis.lf_d65.model2 %>% mutate(patch3 = paste(allvis.lf_d65.model2$vissys,allvis.lf_d65.model2$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.lf=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lf_d65.model2)[names(mean.lf_d65.model2) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lf_d65.model2<-mean.lf_d65.model2[order(mean.lf_d65.model2$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lf_d65.model2$match.name<-flower.colour.model2$species # this column is just for checking if match correctly
mean.lf_d65.model2$colour<-flower.colour.model2$colour

lf_d65.model2<-ggplot(mean.lf_d65.model2, aes(x=vissys, y=mean.dS.lf,group=flowerID))+
  geom_point(col=mean.lf_d65.model2$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lf_d65.model2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf","Vis5.lf","Vis6.lf"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660","Vis 680"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lf_d65.model2, aes(x= "Vis1.lf", y= median(Vis1.lf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_d65.model2, aes(x= "Vis2.lf", y= median(Vis2.lf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_d65.model2, aes(x= "Vis3.lf", y= median(Vis3.lf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_d65.model2, aes(x= "Vis4.lf", y= median(Vis4.lf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_d65.model2, aes(x= "Vis5.lf", y= median(Vis5.lf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_d65.model2, aes(x= "Vis6.lf", y= median(Vis6.lf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Flower")+
  annotate("text", x = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf","Vis5.lf","Vis6.lf"), y = 15, label =c("a","b","c","d","e","b")) #add stitistical info


#make beetle vs leaf plot
##add the mean
mean.lb_d65.model2<-allvis.lb_d65.model2 %>% mutate(patch3 = paste(allvis.lb_d65.model2$vissys,allvis.lb_d65.model2$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.lb=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lb_d65.model2)[names(mean.lb_d65.model2) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lb_d65.model2<-mean.lb_d65.model2[order(mean.lb_d65.model2$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lb_d65.model2$match.name<-beetle.colour.model2$species # this column is just for checking if match correctly
mean.lb_d65.model2$colour<-beetle.colour.model2$colour


lb_d65.model2<-ggplot(mean.lb_d65.model2, aes(x=vissys, y=mean.dS.lb,group=beetleID))+
  geom_point(col=mean.lb_d65.model2$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lb_d65.model2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.background = element_blank(),
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb","Vis5.lb","Vis6.lb"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660","Vis 680"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lb_d65.model2, aes(x= "Vis1.lb", y= median(Vis1.lb_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_d65.model2, aes(x= "Vis2.lb", y= median(Vis2.lb_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_d65.model2, aes(x= "Vis3.lb", y= median(Vis3.lb_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_d65.model2, aes(x= "Vis4.lb", y= median(Vis4.lb_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_d65.model2, aes(x= "Vis5.lb", y= median(Vis5.lb_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_d65.model2, aes(x= "Vis6.lb", y= median(Vis6.lb_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Beetle")+
  annotate("text", x = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb","Vis5.lb","Vis6.lb"), y = 15, label =c("a","b","c","d","e","f")) #add stitistical info


#make beetle vs flower plot
##add the mean
mean.bf_d65.model2<-allvis.bf_d65.model2 %>% mutate(patch3 = paste(allvis.bf_d65.model2$vissys,allvis.bf_d65.model2$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore


##plot the mean dS
names(mean.bf_d65.model2)[names(mean.bf_d65.model2) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf_d65.model2<-mean.bf_d65.model2[order(mean.bf_d65.model2$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf_d65.model2$match.name<-flower.colour.model2$species # this column is just for checking if match correctly
mean.bf_d65.model2$colour<-flower.colour.model2$colour

bf_d65.model2<-ggplot(mean.bf_d65.model2, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf_d65.model2$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.bf_d65.model2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf","Vis5.bf","Vis6.bf"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660","Vis 680"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf_d65.model2, aes(x= "Vis1.bf", y= median(Vis1.bf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_d65.model2, aes(x= "Vis2.bf", y= median(Vis2.bf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_d65.model2, aes(x= "Vis3.bf", y= median(Vis3.bf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_d65.model2, aes(x= "Vis4.bf", y= median(Vis4.bf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_d65.model2, aes(x= "Vis5.bf", y= median(Vis5.bf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_d65.model2, aes(x= "Vis6.bf", y= median(Vis6.bf_d65.model2$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf","Vis5.bf","Vis6.bf"), y = 15, label =c("a","b","c","d","e","f")) #add stitistical info


figure_d65.model2 <- ggarrange(lf_d65.model2,lb_d65.model2,bf_d65.model2, ncol = 3, nrow = 1)
figure_d65.model2
```

###Twilight
```{r,fig.cap="Contrast comparison between visual systems with the LWS photoreceptor peaking at different wavelengths. A dot in each visual system shows a representative contrast of a flower pattern (beetle pattern in the middle panel), which is the average of its contrast to all leaves (all beetle patterns on the right panel). Colours of the dots reflect the visible colour of the flower (beetle patterns in the middle panel) with the lines of the same colour connecting the results between different visual systems. Black dots show the median of the representative contrast in a visual system. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1. Two contrasts > 10 JND are from flowers that have very low UV reflectance."}
#make flower vs leaf plot
##add the mean
mean.lf_twilight.model2<-allvis.lf_twilight.model2 %>% mutate(patch3 = paste(allvis.lf_twilight.model2$vissys,allvis.lf_twilight.model2$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.lf=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lf_twilight.model2)[names(mean.lf_twilight.model2) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lf_twilight.model2<-mean.lf_twilight.model2[order(mean.lf_twilight.model2$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lf_twilight.model2$match.name<-flower.colour.model2$species # this column is just for checking if match correctly
mean.lf_twilight.model2$colour<-flower.colour.model2$colour

lf_twilight.model2<-ggplot(mean.lf_twilight.model2, aes(x=vissys, y=mean.dS.lf,group=flowerID))+
  geom_point(col=mean.lf_twilight.model2$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lf_twilight.model2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf","Vis5.lf","Vis6.lf"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660","Vis 680"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lf_twilight.model2, aes(x= "Vis1.lf", y= median(Vis1.lf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_twilight.model2, aes(x= "Vis2.lf", y= median(Vis2.lf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_twilight.model2, aes(x= "Vis3.lf", y= median(Vis3.lf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_twilight.model2, aes(x= "Vis4.lf", y= median(Vis4.lf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_twilight.model2, aes(x= "Vis5.lf", y= median(Vis5.lf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lf_twilight.model2, aes(x= "Vis6.lf", y= median(Vis6.lf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Flower")+
  annotate("text", x = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf","Vis5.lf","Vis6.lf"), y = 15, label =c("a","b","c","c","d","b")) #add stitistical info


#make beetle vs leaf plot
##add the mean
mean.lb_twilight.model2<-allvis.lb_twilight.model2 %>% mutate(patch3 = paste(allvis.lb_twilight.model2$vissys,allvis.lb_twilight.model2$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.lb=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lb_twilight.model2)[names(mean.lb_twilight.model2) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lb_twilight.model2<-mean.lb_twilight.model2[order(mean.lb_twilight.model2$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lb_twilight.model2$match.name<-beetle.colour.model2$species # this column is just for checking if match correctly
mean.lb_twilight.model2$colour<-beetle.colour.model2$colour


lb_twilight.model2<-ggplot(mean.lb_twilight.model2, aes(x=vissys, y=mean.dS.lb,group=beetleID))+
  geom_point(col=mean.lb_twilight.model2$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lb_twilight.model2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.background = element_blank(),
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb","Vis5.lb","Vis6.lb"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660","Vis 680"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lb_twilight.model2, aes(x= "Vis1.lb", y= median(Vis1.lb_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_twilight.model2, aes(x= "Vis2.lb", y= median(Vis2.lb_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_twilight.model2, aes(x= "Vis3.lb", y= median(Vis3.lb_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_twilight.model2, aes(x= "Vis4.lb", y= median(Vis4.lb_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_twilight.model2, aes(x= "Vis5.lb", y= median(Vis5.lb_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.lb_twilight.model2, aes(x= "Vis6.lb", y= median(Vis6.lb_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Beetle")+
  annotate("text", x = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb","Vis5.lb","Vis6.lb"), y = 15, label =c("a","b","c","d","e","f")) #add stitistical info


#make beetle vs flower plot
##add the mean
mean.bf_twilight.model2<-allvis.bf_twilight.model2 %>% mutate(patch3 = paste(allvis.bf_twilight.model2$vissys,allvis.bf_twilight.model2$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore


##plot the mean dS
names(mean.bf_twilight.model2)[names(mean.bf_twilight.model2) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf_twilight.model2<-mean.bf_twilight.model2[order(mean.bf_twilight.model2$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf_twilight.model2$match.name<-flower.colour.model2$species # this column is just for checking if match correctly
mean.bf_twilight.model2$colour<-flower.colour.model2$colour

bf_twilight.model2<-ggplot(mean.bf_twilight.model2, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf_twilight.model2$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.bf_twilight.model2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf","Vis5.bf","Vis6.bf"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660","Vis 680"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf_twilight.model2, aes(x= "Vis1.bf", y= median(Vis1.bf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_twilight.model2, aes(x= "Vis2.bf", y= median(Vis2.bf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_twilight.model2, aes(x= "Vis3.bf", y= median(Vis3.bf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_twilight.model2, aes(x= "Vis4.bf", y= median(Vis4.bf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_twilight.model2, aes(x= "Vis5.bf", y= median(Vis5.bf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  geom_point(data = mean.bf_twilight.model2, aes(x= "Vis6.bf", y= median(Vis6.bf_twilight.model2$dS)), 
             col="black", size=5)+ #add the median point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf","Vis5.bf","Vis6.bf"), y = 15, label =c("a","b","c","c","d","b")) #add stitistical info


figure_twilight.model2 <- ggarrange(lf_twilight.model2,lb_twilight.model2,bf_twilight.model2, ncol = 3, nrow = 1)
figure_twilight.model2
```

#Summary

* Visual models using hypothetical insect visual systems indicate that long wavelength sensitivity enhances the contrast of beetle colours against leaf backgrounds; whereas short wavelength sensitivity enhances the contrast of flowers with both leaves and beetles. 
</br>
</br>
* Tetrachromacy consistently increases contrast compared to trichromacy, with the largest increase of 1.4-fold observed in the comparison between beetles and leaves. 
</br>
</br>
* The optimal peak sensitivity of the LWS photoreceptor depends on what is being viewed. When comparing beetle colours with both leaves and flowers, contrast increases with increasing LWS max, whereas when comparing flowers with leaves, contrast is maximized with a LWS photoreceptor peak sensitivity of 640 nm.
</br>
</br>
* The contrasts in the corresponding comparisons were qualitatively similar in twilight models.