---
title: "Main models: Visual sensitivity in the far-red enhances contrast against vegetation"
author: <br>Lu-Yi Wang^1^, Devi Stuart-Fox^1^, Geoff Walker^1^, Nicholas W. Roberts^2^
  and Amanda M. Franklin^1^ <br></br> ^1^School of Biosciences, The University of Melbourne,
  Australia <br></br> ^2^School of Biological Sciences, University of Bristol, UK
  <br></br>
output:
  pdf_document: default
  html_document:
    theme: flatly
    toc: true
    toc_depth: 2
subtitle: Supplementary Information
Date: August 31 2020
---

#The aims
  
* We used visual modelling to investigate the potential benefit of long wavelength sensitivity for insects.

* Specifically, we varied the presence of a long wavelength sensitive photoreceptor and its peak sensitivity.

* Our study focused on jewel beetles and their host plants because jewel beetles have sensitivity in the far red. 

* Additionally, we tested the effect of red-shifted light environment on contrast by running the same models under twilight illumination.

</br>
</br>

#Load R libraries 
```{r, warning=FALSE, message=FALSE, results='hide'}
library(pavo)
library(dplyr)
library(stringr)
library(tidyr) #for gather() function
library(ggplot2)
library(lme4)
library(car)
library(multcomp)
library(boot) #for mean() function
library(pander) #for creating tidy tables
library(ggpubr) #for ggarrange() function
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE) # Suppress warnings in the HTML output
knitr::opts_chunk$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
```


</br>
</br>

#Data description

</br>

##Import and process the data
* The wavelength range for all data used in the models was 300-800 nm.

```{r import data,message=FALSE}
#import sensitivity curves
specsensbuprest.aim1 <- read.csv("data/peak sensitivity_filter shift_aim1.csv",header=TRUE) %>%
  as.rspec()
specsensbuprest.aim2 <- read.csv("data/peak sensitivity_filter shift_aim2.csv",header=TRUE) %>%
  as.rspec()
#import irradiance
irradiance.d65 <- read.csv("data/d65.csv",header=TRUE) %>% 
  as.rspec(lim=c(300,800)) %>%  #set import range
  procspec(opt = c("min", "max")) #standardize the illumination spectrum
irradiance.twilight <- read.csv("data/civil twilight.csv",header=TRUE) %>% 
  as.rspec(lim=c(300,800)) %>% 
  procspec(opt = c("min", "max")) %>% 
  rename( twilight = Irradiance) 

#import backgound - average leaf
aveleaf <- read.csv("data/aveleaf.csv",header=TRUE) %>% as.rspec()

#import and combind beetle, flower, leaf together
raw.dataset<-read.csv("data/refelectance spectra.csv",header=TRUE) %>% as.rspec()
dataset<- aggspec(raw.dataset, by = 3, FUN = mean) %>%  #average three measurements to a representative one
  procspec(opt = "smooth", span = 0.1, fixneg = "zero") #smooth the spectra and lift <0 to 0
```

</br>

##Spectral reflectance of the targets
* Jewel beetles and their host plants (leaves and flowers)
    + Leaves: 
        + sample source: mainly from Melton Gardens and Maranoa Gardens (4 from Meblourne roadsides).
        + colour (to human vision): green
        + total number: 46 (all are from the host plant genus of Australian jewel beetles)
  
    + Flowers: 
        + sample source: mainly from Melton Gardens and Maranoa Gardens (4 from Meblourne roadsides).
        + colour (to human vision): white (10), pink (11), red (10), yellow (9), orange (3), and purple (4)
        + total number: 47 (from 46 species, the same species for leaf reflectance)
  
    + Beetles:
        + sample source: Australian jewel beetles from, ANIC (29) and our own collection
        + colour (to human vision): red, pink, yellow/orange, green, blue, velvet, black
        + total number: 37

* We averaged of 3 measurements to generate a representative spectrum for each colour
* The spectral data were smoothed with the span = 0.1, and those < 0 were lifted to 0
```{r, fig.cap="Figure caption: Reflectance spectra of the targets"}
#assign categoryies to each spectrum
category.list <- c("flower","leaf","beetle")
category <- rep(category.list , c(47*501,46*501,37*501))
wavelength<-rep(dataset[,1])

#transform the data for ploting purpose
dataset.transpose<-gather(dataset[,2:131], key = "species", value = "reflectance", na.rm = FALSE,
                          convert = FALSE, factor_key = FALSE)
dataset.plot.indivisually<-cbind(dataset.transpose, wavelength,category)

#split data by categories for future use
flower.spec<-dataset.plot.indivisually[1:23547,]
leaf.spec<-dataset.plot.indivisually[23548:46593,]
beetle.spec<-dataset.plot.indivisually[46594:65130,]

#merge the spectra before plot here
dataset.plot.indivisually$category2<-factor(dataset.plot.indivisually$category, levels=c("leaf","flower","beetle"))

#plot the spectra of the targets used in this model
ggplot(dataset.plot.indivisually,aes(x=wavelength,y=reflectance, colour=category2, group=species))+
  geom_point(size=.05)+
  geom_line(size=.05)+
  theme(legend.position = "none")+
  scale_color_manual( values = c( "forestgreen", "palevioletred1","cornflowerblue"))+
  facet_grid(category2 ~ .)+
  xlab("Wavelength (nm)")+ylab("Reflectance (%)")+
  theme_classic()+
  guides(colour=FALSE) # remove the legend
```


</br>
</br>

##Visual sensitivities and visual systems
* We created nine sensitivity curves peaking at 380, 460, 520, 580, 600, 620, 640, 660 nm and classified them into 4 photoreceptor types based on their peaks: 
    + Ultraviolet sensitive (UVS): 380 nm
    + Short-wavelength sensitive (SWS): 460 nm
    + Medium-wavelength sensitive (MWS): 520 nm
    + Long-wavelength sensitive (LWS): 580, 600, 620, 640, 660 nm

* For the LWS, we applied a cut-off filter on the A1opsin sensitivity template peaking at 570 nm to shift the peak sensitivty to longer wavelengths.

* Based on these sensitivities, we created several different visual systems to test two different questions: 
    + What is the benefit of possessing a long wavelength photoreceptor?
    + Is there an benefit to shifting the peak sensitivity of the long wavelength photoreceptor?
  
***
* For the first question we compared the contrast between 3 trichromatic visual system with varied photoreceptor combination. We also tested whether an extra receptor enhanced chromatic contrast by comparing the trichromatic visual systems with a tetrachromatic visual system.
    + Visual systems used: 
        1. Visual system USM (USM): 380 nm, 460 nm, 520 nm (UVS,SWS,MWS)
        2. Visual system UML (UML): 380 nm, 520 nm, 580 nm (UVS,MWS,LWS)
        3. Visual system USL (USL): 380 nm, 460 nm, 580 nm (UVS,SWS,LWS)
        4. Visual system USML (USML): 380 nm, 460 nm, 520 nm, 580 nm (UVS,SWS,MWS,LWS)

***
* For the second question, we tested how the contrast changed as peak sensitivity increased by systematically increasing the peak sensitivity of the LWS photoreceptor from 580-660 nm.
    + Visual systems used:
        1. Visual system 580 (VS 580): 380 nm, 460 nm, 520 nm, 580 nm
        2. Visual system 600 (VS 600): 380 nm, 460 nm, 520 nm, 600 nm
        3. Visual system 620 (VS 620): 380 nm, 460 nm, 520 nm, 620 nm
        4. Visual system 640 (VS 640): 380 nm, 460 nm, 520 nm, 640 nm
        5. Visual system 660 (VS 660): 380 nm, 460 nm, 520 nm, 660 nm


```{r, fig.cap="Figure caption: Sensitivity curves of the photoreceptors with different peak wavelengths."}
wl<-specsensbuprest.aim2[,1]
peaks<-gather(specsensbuprest.aim2[,2:9], peak, value) %>% cbind(wl)

peak.order <- c("UVS.380.A1.", "SWS.460.A1.", "MWS.520.A1.", "LWS.570.A1..filter580.", "LWS.570.A1..filter600.", "LWS.570.A1..filter620.", "LWS.570.A1..filter640.", "LWS.570.A1..filter660.") #to order the peaks in the legend
ggplot(peaks,aes(x=wl, y=value, col=peak))+
  geom_line()+
  guides(color=guide_legend(title="peak sensitivity"))+
  scale_color_manual(
    values = c("darkorchid4", "dodgerblue3", "olivedrab4", "orange1", "orange3","darkorange3", "orangered1", "red2"),
    labels=c("380 nm", "460 nm","520 nm", "580 nm", "600 nm", "620 nm", "640 nm", "660 nm" ),
    breaks=peak.order)+
  xlab("Wavelength (nm)")+ 
  ylab("Relative spectral sensitivity")+
  theme_classic()

```

</br>
</br>

##Illuminations
* Two light environments: daylight and twilight (to represent red-shifted illumination).
  
    + Daylight: __D65__ (standard daylight) from Commission internationale de l'eclairage CIE
    + Twilight: measured at the Pinnacles Lookout in Alpine National Park, VIC, Australia at 18:15 on September 14th 2019.

```{r, fig.cap="Figure caption: Relative irradiance of standard daylight and twilight"}
illum <- merge(irradiance.d65, irradiance.twilight) %>% gather(light, illuminace, -wl) 

ggplot(illum, aes(x=wl, y=illuminace, color=light))+
geom_line()+
xlab("Wavelength (nm)")+
ylab("Relative irradiance")+
theme_classic()
```

</br>
</br>

#Run the visual models

</br>
</br>

##First: Quantum catch calculation
* We used the `vismodel` function in the package pavo to calculate quantum catch.
* For each visual system, quantum catch was calculated based on Fechner's law (the signal of the receptor channel is proportional to the logarithm of the quantum catch).
* The average of all leaf spectra was used as the background adapting light.
* The von Kries chromatic adaptation was applied.
```{r,message=FALSE}
#Quantum catch - D65 - aim 1
vsUSM=vismodel(dataset[1:501,], visual = specsensbuprest.aim1[, 1:4], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
vsUML=vismodel(dataset[1:501,], visual = specsensbuprest.aim1[, c(1,2,4,5)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
vsUSL=vismodel(dataset[1:501,], visual = specsensbuprest.aim1[, c(1,2,3,5)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
vsUSML=vismodel(dataset[1:501,], visual = specsensbuprest.aim1[, 1:5], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)

#Quantum catch - D65 - Aim 2
buprest580=vismodel(dataset[1:501,], visual = specsensbuprest.aim2[, 1:5], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest600=vismodel(dataset[1:501,], visual = specsensbuprest.aim2[, c(1,2,3,4,6)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest620=vismodel(dataset[1:501,], visual = specsensbuprest.aim2[, c(1,2,3,4,7)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest640=vismodel(dataset[1:501,], visual = specsensbuprest.aim2[, c(1,2,3,4,8)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest660=vismodel(dataset[1:501,], visual = specsensbuprest.aim2[, c(1,2,3,4,9)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)


#Quantum catch - twilight - aim 1
vsUSM_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.aim1[, 1:4], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
vsUML_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.aim1[, c(1,2,4,5)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
vsUSL_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.aim1[, c(1,2,3,5)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
vsUSML_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.aim1[, 1:5], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)

#Quantum catch - twilight - Aim 2
buprest580_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.aim2[, 1:5], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest600_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.aim2[, c(1,2,3,4,6)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest620_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.aim2[, c(1,2,3,4,7)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest640_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.aim2[, c(1,2,3,4,8)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest660_twilight=vismodel(dataset[1:501,], visual = specsensbuprest.aim2[, c(1,2,3,4,9)], bkg=aveleaf$aveleaf, illum = irradiance.twilight[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)

```


</br>
</br>

##Second: Contrast calculation {.tabset .tabset-fade .tabset-pills}
* To calculate chromatic contrast we used the `coldist` function in pavo.
* We used a neural noise-limited model where the noise is proportional to the Weber fraction and is independent of the intensity of the signal received.
* Photoreceptor density of the tetrachromat was based on the opsin gene expression of Emerald ash borer, _Agrilus planipennis_: 1.14, 1, 1.26, 1.38. For the trichromates, we redistributed the lost cone number proportionally to the remaining three cones. (USM: 1.6027, 1.4059, 1.771; UML: 1.4416, 1.5933, 1.7451; USL:1.5481, 1.3580, 1.8740)


* The Weber fraction for the longest cone in the tetrachromat was 0.1, which was used to calculated the unknown signa;-to-noise ratio. To keep the signa;-to-noise ratio the same bwtween the tetrachromat and the trichromates, we adjusted the weber fractions for the longest cone in trichromats to be 0.0883, 0.0889, 0.0858 for USM, UML, USL. 

* In the models using twilight illuminance, we took the photo shot noise into account.

```{r,message=FALSE}
#Contrast calculation- D65 - aim 1
CvsUSM = coldist(vsUSM, noise="neural", achro=FALSE, n = c(1.6027, 1.4059, 1.7714), weber = 0.0883, weber.ref = 3) 
CvsUML = coldist(vsUML, noise="neural", achro=FALSE, n = c(1.4416, 1.5933, 1.7451), weber = 0.0889, weber.ref = 3)
CvsUSL = coldist(vsUSL, noise="neural", achro=FALSE, n = c(1.5481, 1.3580, 1.8740), weber = 0.0858, weber.ref = 3)
CvsUSML = coldist(vsUSML, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)

#Contrast calculation- D65 - Aim 2
Cbuprest580 = coldist(buprest580, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest600 = coldist(buprest600, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest620 = coldist(buprest620, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest640 = coldist(buprest640, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest660 = coldist(buprest660, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)

#Contrast calculation- twilight - aim 1
CvsUSM_twilight = coldist(vsUSM_twilight, noise="quantum", achro=FALSE, n = c(1.6027, 1.4059, 1.7714), weber = 0.0883, weber.ref = 3)  
CvsUML_twilight = coldist(vsUML_twilight, noise="quantum", achro=FALSE, n = c(1.4416, 1.5933, 1.7451), weber = 0.0889, weber.ref = 3)
CvsUSL_twilight = coldist(vsUSL_twilight, noise="quantum", achro=FALSE, n = c(1.5481, 1.3580, 1.8740), weber = 0.0858, weber.ref = 3)
CvsUSML_twilight = coldist(vsUSML_twilight, noise="quantum", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1,  weber.ref = 4)

#Contrast calculation- twilight - Aim 2
Cbuprest580_twilight = coldist(buprest580_twilight, noise="quantum", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest600_twilight = coldist(buprest600_twilight, noise="quantum", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest620_twilight = coldist(buprest620_twilight, noise="quantum", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest640_twilight = coldist(buprest640_twilight, noise="quantum", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest660_twilight = coldist(buprest660_twilight, noise="quantum", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
```

```{r}
#combine all contrast value in each comparison group

#Daylight - aim 1

##flower vs leaf
VS1.fl_d65.aim1<- CvsUSM%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS1.fl_d65.aim1$vissys<-strrep("VS1.fl",1)
VS2.fl_d65.aim1<-CvsUML%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS2.fl_d65.aim1$vissys<-strrep("VS2.fl",1)
VS3.fl_d65.aim1<-CvsUSL%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS3.fl_d65.aim1$vissys<-strrep("VS3.fl",1)
VS4.fl_d65.aim1<-CvsUSML%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS4.fl_d65.aim1$vissys<-strrep("VS4.fl",1)
allvis.fl_d65.aim1<-VS1.fl_d65.aim1 %>% rbind(VS2.fl_d65.aim1) %>% rbind(VS3.fl_d65.aim1) %>%rbind(VS4.fl_d65.aim1)

##beetle vs leaf
VS1.bl_d65.aim1<- CvsUSM%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS1.bl_d65.aim1$vissys<-strrep("VS1.bl",1)
VS2.bl_d65.aim1<-CvsUML%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS2.bl_d65.aim1$vissys<-strrep("VS2.bl",1)
VS3.bl_d65.aim1<-CvsUSL%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS3.bl_d65.aim1$vissys<-strrep("VS3.bl",1)
VS4.bl_d65.aim1<-CvsUSML%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS4.bl_d65.aim1$vissys<-strrep("VS4.bl",1)
allvis.bl_d65.aim1<-VS1.bl_d65.aim1 %>% rbind(VS2.bl_d65.aim1) %>% rbind(VS3.bl_d65.aim1) %>%rbind(VS4.bl_d65.aim1)

##beetle vs flower
VS1.bf_d65.aim1<- CvsUSM%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS1.bf_d65.aim1$vissys<-strrep("VS1.bf",1)
VS2.bf_d65.aim1<-CvsUML%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS2.bf_d65.aim1$vissys<-strrep("VS2.bf",1)
VS3.bf_d65.aim1<-CvsUSL%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS3.bf_d65.aim1$vissys<-strrep("VS3.bf",1)
VS4.bf_d65.aim1<-CvsUSML%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS4.bf_d65.aim1$vissys<-strrep("VS4.bf",1)
allvis.bf_d65.aim1<-VS1.bf_d65.aim1 %>% rbind(VS2.bf_d65.aim1) %>% rbind(VS3.bf_d65.aim1)%>%
  rbind(VS4.bf_d65.aim1)

#Twiligth - aim 1
##flower vs leaf
VS1.fl_twilight.aim1<- CvsUSM_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS1.fl_twilight.aim1$vissys<-strrep("VS1.fl",1)
VS2.fl_twilight.aim1<-CvsUML_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS2.fl_twilight.aim1$vissys<-strrep("VS2.fl",1)
VS3.fl_twilight.aim1<-CvsUSL_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS3.fl_twilight.aim1$vissys<-strrep("VS3.fl",1)
VS4.fl_twilight.aim1<-CvsUSML_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS4.fl_twilight.aim1$vissys<-strrep("VS4.fl",1)
allvis.fl_twilight.aim1<-VS1.fl_twilight.aim1 %>% rbind(VS2.fl_twilight.aim1) %>% rbind(VS3.fl_twilight.aim1) %>%rbind(VS4.fl_twilight.aim1)

##beetle vs leaf
VS1.bl_twilight.aim1<- CvsUSM_twilight%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS1.bl_twilight.aim1$vissys<-strrep("VS1.bl",1)
VS2.bl_twilight.aim1<-CvsUML_twilight%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS2.bl_twilight.aim1$vissys<-strrep("VS2.bl",1)
VS3.bl_twilight.aim1<-CvsUSL_twilight%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS3.bl_twilight.aim1$vissys<-strrep("VS3.bl",1)
VS4.bl_twilight.aim1<-CvsUSML_twilight%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS4.bl_twilight.aim1$vissys<-strrep("VS4.bl",1)
allvis.bl_twilight.aim1<-VS1.bl_twilight.aim1 %>% rbind(VS2.bl_twilight.aim1) %>% rbind(VS3.bl_twilight.aim1) %>%rbind(VS4.bl_twilight.aim1)


##beetle vs flower
VS1.bf_twilight.aim1<- CvsUSM_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS1.bf_twilight.aim1$vissys<-strrep("VS1.bf",1)
VS2.bf_twilight.aim1<-CvsUML_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS2.bf_twilight.aim1$vissys<-strrep("VS2.bf",1)
VS3.bf_twilight.aim1<-CvsUSL_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS3.bf_twilight.aim1$vissys<-strrep("VS3.bf",1)
VS4.bf_twilight.aim1<-CvsUSML_twilight%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS4.bf_twilight.aim1$vissys<-strrep("VS4.bf",1)
allvis.bf_twilight.aim1<-VS1.bf_twilight.aim1 %>% rbind(VS2.bf_twilight.aim1) %>% rbind(VS3.bf_twilight.aim1) %>%rbind(VS4.bf_twilight.aim1)



#Daylight - aim 2
##flower vs leaf
VS1.fl_d65.aim2<- Cbuprest580%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS1.fl_d65.aim2$vissys<-strrep("VS1.fl",1)
VS2.fl_d65.aim2<-Cbuprest600%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS2.fl_d65.aim2$vissys<-strrep("VS2.fl",1)
VS3.fl_d65.aim2<-Cbuprest620%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS3.fl_d65.aim2$vissys<-strrep("VS3.fl",1)
VS4.fl_d65.aim2<-Cbuprest640%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS4.fl_d65.aim2$vissys<-strrep("VS4.fl",1)
VS5.fl_d65.aim2<-Cbuprest660%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS5.fl_d65.aim2$vissys<-strrep("VS5.fl",1)

allvis.fl_d65.aim2<-VS1.fl_d65.aim2 %>% rbind(VS2.fl_d65.aim2) %>% rbind(VS3.fl_d65.aim2) %>%
  rbind(VS4.fl_d65.aim2) %>%rbind(VS5.fl_d65.aim2)

##beetle vs leaf
VS1.bl_d65.aim2<- Cbuprest580%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS1.bl_d65.aim2$vissys<-strrep("VS1.bl",1)
VS2.bl_d65.aim2<-Cbuprest600%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS2.bl_d65.aim2$vissys<-strrep("VS2.bl",1)
VS3.bl_d65.aim2<-Cbuprest620%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS3.bl_d65.aim2$vissys<-strrep("VS3.bl",1)
VS4.bl_d65.aim2<-Cbuprest640%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS4.bl_d65.aim2$vissys<-strrep("VS4.bl",1)
VS5.bl_d65.aim2<-Cbuprest660%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS5.bl_d65.aim2$vissys<-strrep("VS5.bl",1)

allvis.bl_d65.aim2<-VS1.bl_d65.aim2 %>% rbind(VS2.bl_d65.aim2) %>% rbind(VS3.bl_d65.aim2) %>%
  rbind(VS4.bl_d65.aim2) %>%rbind(VS5.bl_d65.aim2) 


##beetle vs flower
VS1.bf_d65.aim2<- Cbuprest580%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS1.bf_d65.aim2$vissys<-strrep("VS1.bf",1)
VS2.bf_d65.aim2<-Cbuprest600%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS2.bf_d65.aim2$vissys<-strrep("VS2.bf",1)
VS3.bf_d65.aim2<-Cbuprest620%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS3.bf_d65.aim2$vissys<-strrep("VS3.bf",1)
VS4.bf_d65.aim2<-Cbuprest640%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS4.bf_d65.aim2$vissys<-strrep("VS4.bf",1)
VS5.bf_d65.aim2<-Cbuprest660%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS5.bf_d65.aim2$vissys<-strrep("VS5.bf",1)

allvis.bf_d65.aim2<-VS1.bf_d65.aim2 %>% rbind(VS2.bf_d65.aim2) %>% rbind(VS3.bf_d65.aim2) %>%
  rbind(VS4.bf_d65.aim2) %>%rbind(VS5.bf_d65.aim2) 

##Twiligth - aim 2
##flower vs leaf
VS1.fl_twilight.aim2<- Cbuprest580_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS1.fl_twilight.aim2$vissys<-strrep("VS1.fl",1)
VS2.fl_twilight.aim2<-Cbuprest600_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS2.fl_twilight.aim2$vissys<-strrep("VS2.fl",1)
VS3.fl_twilight.aim2<-Cbuprest620_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS3.fl_twilight.aim2$vissys<-strrep("VS3.fl",1)
VS4.fl_twilight.aim2<-Cbuprest640_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS4.fl_twilight.aim2$vissys<-strrep("VS4.fl",1)
VS5.fl_twilight.aim2<-Cbuprest660_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
VS5.fl_twilight.aim2$vissys<-strrep("VS5.fl",1)

allvis.fl_twilight.aim2<-VS1.fl_twilight.aim2 %>% rbind(VS2.fl_twilight.aim2) %>% rbind(VS3.fl_twilight.aim2) %>%
  rbind(VS4.fl_twilight.aim2) %>%rbind(VS5.fl_twilight.aim2)

##beetle vs leaf
VS1.bl_twilight.aim2<- Cbuprest580_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS1.bl_twilight.aim2$vissys<-strrep("VS1.bl",1)
VS2.bl_twilight.aim2<-Cbuprest600_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS2.bl_twilight.aim2$vissys<-strrep("VS2.bl",1)
VS3.bl_twilight.aim2<-Cbuprest620_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS3.bl_twilight.aim2$vissys<-strrep("VS3.bl",1)
VS4.bl_twilight.aim2<-Cbuprest640_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS4.bl_twilight.aim2$vissys<-strrep("VS4.bl",1)
VS5.bl_twilight.aim2<-Cbuprest660_twilight %>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
VS5.bl_twilight.aim2$vissys<-strrep("VS5.bl",1)

allvis.bl_twilight.aim2<-VS1.bl_twilight.aim2 %>% rbind(VS2.bl_twilight.aim2) %>% rbind(VS3.bl_twilight.aim2) %>% rbind(VS4.bl_twilight.aim2) %>%rbind(VS5.bl_twilight.aim2)

##beetle vs flower
VS1.bf_twilight.aim2<- Cbuprest580_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS1.bf_twilight.aim2$vissys<-strrep("VS1.bf",1)
VS2.bf_twilight.aim2<-Cbuprest600_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS2.bf_twilight.aim2$vissys<-strrep("VS2.bf",1)
VS3.bf_twilight.aim2<-Cbuprest620_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS3.bf_twilight.aim2$vissys<-strrep("VS3.bf",1)
VS4.bf_twilight.aim2<-Cbuprest640_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS4.bf_twilight.aim2$vissys<-strrep("VS4.bf",1)
VS5.bf_twilight.aim2<-Cbuprest660_twilight %>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
VS5.bf_twilight.aim2$vissys<-strrep("VS5.bf",1)

allvis.bf_twilight.aim2<-VS1.bf_twilight.aim2 %>% rbind(VS2.bf_twilight.aim2) %>% rbind(VS3.bf_twilight.aim2) %>% rbind(VS4.bf_twilight.aim2) %>%rbind(VS5.bf_twilight.aim2)
```

###Aim 1 {.tabset .tabset-fade .tabset-pills}
The table shows the median contrast in each comparison group
```{r}
#Aim 1
system.list.aim1<- rbind.data.frame("USM", "UML", "USL",  "USML") %>% rename(system = 1) # make a list of system names
```

####Daylight
```{r}
#Daylight
##list contrast from each comparison group
fl.contrast_d65.aim1 <- rbind.data.frame(median(VS1.fl_d65.aim1$dS), median(VS2.fl_d65.aim1$dS),median(VS3.fl_d65.aim1$dS),median(VS4.fl_d65.aim1$dS))
bl.contrast_d65.aim1 <-rbind.data.frame(median(VS1.bl_d65.aim1$dS),median(VS2.bl_d65.aim1$dS),median(VS3.bl_d65.aim1$dS),median(VS4.bl_d65.aim1$dS))
bf.contrast_d65.aim1 <-rbind.data.frame(median(VS1.bf_d65.aim1$dS), median(VS2.bf_d65.aim1$dS),median(VS3.bf_d65.aim1$dS),median(VS4.bf_d65.aim1$dS))
#combind comparison groups together in a table
contrast.list_d65.aim1<- system.list.aim1 %>%  cbind(fl.contrast_d65.aim1) %>% cbind(bl.contrast_d65.aim1) %>% cbind(bf.contrast_d65.aim1) %>% dplyr:: rename(flower.vs.leaf = 2, beetle.vs.leaf = 3, beetle.vs.flower = 4) %>% pander() 
contrast.list_d65.aim1
```
####Twilight
```{r}
#Twilight
##list contrast from each comparison group
fl.contrast_twilight.aim1 <- rbind.data.frame(median(VS1.fl_twilight.aim1$dS), median(VS2.fl_twilight.aim1$dS),median(VS3.fl_twilight.aim1$dS),median(VS4.fl_twilight.aim1$dS))
bl.contrast_twilight.aim1 <-rbind.data.frame(median(VS1.bl_twilight.aim1$dS),median(VS2.bl_twilight.aim1$dS),median(VS3.bl_twilight.aim1$dS),median(VS4.bl_twilight.aim1$dS))
bf.contrast_twilight.aim1 <-rbind.data.frame(median(VS1.bf_twilight.aim1$dS), median(VS2.bf_twilight.aim1$dS),median(VS3.bf_twilight.aim1$dS),median(VS4.bf_twilight.aim1$dS))
#combind comparison groups together in a table
contrast.list_twilight.aim1<- system.list.aim1 %>%  cbind(fl.contrast_twilight.aim1) %>% cbind(bl.contrast_twilight.aim1) %>% cbind(bf.contrast_twilight.aim1) %>% dplyr:: rename(flower.vs.leaf = 2, beetle.vs.leaf = 3, beetle.vs.flower = 4) %>% pander()
contrast.list_twilight.aim1
```
###Aim 2 {.tabset .tabset-fade .tabset-pills}
The table shows the median contrast in each comparison group
```{r}
system.list.aim2<- rbind.data.frame("VS 580", "VS 600", "VS 620", "VS 640", "Vis 660") %>% rename(system = 1) # make a list of system names
```
####Daylight
```{r}
#Daylight
##list contrast from each comparison group
fl.contrast_d65.aim2 <- rbind.data.frame(median(VS1.fl_d65.aim2$dS), median(VS2.fl_d65.aim2$dS),median(VS3.fl_d65.aim2$dS),median(VS4.fl_d65.aim2$dS),median(VS5.fl_d65.aim2$dS))
bl.contrast_d65.aim2 <-rbind.data.frame(median(VS1.bl_d65.aim2$dS),median(VS2.bl_d65.aim2$dS),median(VS3.bl_d65.aim2$dS),median(VS4.bl_d65.aim2$dS),median(VS5.bl_d65.aim2$dS))
bf.contrast_d65.aim2 <-rbind.data.frame(median(VS1.bf_d65.aim2$dS), median(VS2.bf_d65.aim2$dS),median(VS3.bf_d65.aim2$dS),median(VS4.bf_d65.aim2$dS),median(VS5.bf_d65.aim2$dS))
#combind comparison groups together in a table
contrast.list_d65.aim2<- system.list.aim2 %>%  cbind(fl.contrast_d65.aim2) %>% cbind(bl.contrast_d65.aim2) %>% cbind(bf.contrast_d65.aim2) %>% dplyr:: rename(flower.vs.leaf = 2, beetle.vs.leaf = 3, beetle.vs.flower = 4) %>% pander() 
contrast.list_d65.aim2
```
####Twilight
```{r}
#Twilight
##list contrast from each comparison group
fl.contrast_twilight.aim2 <- rbind.data.frame(median(VS1.fl_twilight.aim2$dS), median(VS2.fl_twilight.aim2$dS),median(VS3.fl_twilight.aim2$dS),median(VS4.fl_twilight.aim2$dS),median(VS5.fl_twilight.aim2$dS))
bl.contrast_twilight.aim2 <-rbind.data.frame(median(VS1.bl_twilight.aim2$dS),median(VS2.bl_twilight.aim2$dS),median(VS3.bl_twilight.aim2$dS),median(VS4.bl_twilight.aim2$dS),median(VS5.bl_twilight.aim2$dS))
bf.contrast_twilight.aim2 <-rbind.data.frame(median(VS1.bf_twilight.aim2$dS), median(VS2.bf_twilight.aim2$dS),median(VS3.bf_twilight.aim2$dS),median(VS4.bf_twilight.aim2$dS),median(VS5.bf_twilight.aim2$dS))
#combind comparison groups together in a table
contrast.list_twilight.aim2<- system.list.aim2 %>%  cbind(fl.contrast_twilight.aim2) %>% cbind(bl.contrast_twilight.aim2) %>% cbind(bf.contrast_twilight.aim2) %>% dplyr:: rename(flower.vs.leaf = 2, beetle.vs.leaf = 3, beetle.vs.flower = 4) %>% pander() 
contrast.list_twilight.aim2
```
</br>
</br>

#Compare contrasts
* To compare contrasts between visual systems, We conducted Wald chi-square tests on generalised linear mixed models (GLMM) followed by posthoc tests.

* In the models, we assigned
    + Independent variable: __contrast__
    + Dependent variable: 
        + Fixed factor: __visual system__
        + Random factor: __sample ID__ of both targets in the comparison

```{r} 
#creat different comparison groups for furthur GLMM analysis
#Organize data before GLMM

#D65 - aim 1
##flower vs leaf
CvsUSM.flower.vs.leaf=
  CvsUSM %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvsUML.flower.vs.leaf=
  CvsUML %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvsUSL.flower.vs.leaf=
  CvsUSL %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvsUSML.flower.vs.leaf=
  CvsUSML %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

C.flower.vs.leaf.aim1=
  CvsUSM.flower.vs.leaf %>% rbind(CvsUML.flower.vs.leaf) %>% 
  rbind(CvsUSL.flower.vs.leaf)%>% rbind(CvsUSML.flower.vs.leaf)

contrast.UVSWMW...flower.vs.leaf<-CvsUSM.flower.vs.leaf[,3]
contrast.UV..MWLW.flower.vs.leaf<-CvsUML.flower.vs.leaf[,3]
contrast.UVSW..LW.flower.vs.leaf<-CvsUSL.flower.vs.leaf[,3]
contrast.UVSWMWLW.flower.vs.leaf<-CvsUSML.flower.vs.leaf[,3]

com.contrast.flower.vs.leaf.aim1<-cbind(CvsUSM.flower.vs.leaf[,1:2],contrast.UVSWMW...flower.vs.leaf,contrast.UV..MWLW.flower.vs.leaf,contrast.UVSW..LW.flower.vs.leaf,contrast.UVSWMWLW.flower.vs.leaf)
compare.flower.vs.leaf.aim1 <- com.contrast.flower.vs.leaf.aim1 %>%
  gather(key = "peak_wl.flower.vs.leaf", value = "dS", 3:6)

##beetle vs leaf
CvsUSM.beetle.vs.leaf=
  CvsUSM %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvsUML.beetle.vs.leaf=
  CvsUML %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvsUSL.beetle.vs.leaf=
  CvsUSL %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvsUSML.beetle.vs.leaf=
  CvsUSML %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

C.beetle.vs.leaf.aim1=
  CvsUSM.beetle.vs.leaf %>% rbind(CvsUML.beetle.vs.leaf) %>% 
  rbind(CvsUSL.beetle.vs.leaf)%>%  rbind(CvsUSML.beetle.vs.leaf)

contrast.UVSWMW...beetle.vs.leaf<-CvsUSM.beetle.vs.leaf[,3]
contrast.UV..MWLW.beetle.vs.leaf<-CvsUML.beetle.vs.leaf[,3]
contrast.UVSW..LW.beetle.vs.leaf<-CvsUSL.beetle.vs.leaf[,3]
contrast.UVSWMWLW.beetle.vs.leaf<-CvsUSML.beetle.vs.leaf[,3]

com.contrast.beetle.vs.leaf.aim1<-cbind(CvsUSM.beetle.vs.leaf[,1:2],contrast.UVSWMW...beetle.vs.leaf,contrast.UV..MWLW.beetle.vs.leaf,contrast.UVSW..LW.beetle.vs.leaf,contrast.UVSWMWLW.beetle.vs.leaf)
compare.beetle.vs.leaf.aim1 <- com.contrast.beetle.vs.leaf.aim1 %>%
  gather(key = "peak_wl.beetle.vs.leaf", value = "dS", 3:6)

##beetle vs flower
CvsUSM.beetle.vs.flower=
  CvsUSM %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvsUML.beetle.vs.flower=
  CvsUML %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvsUSL.beetle.vs.flower=
  CvsUSL %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvsUSML.beetle.vs.flower=
  CvsUSML %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

C.beetle.vs.flower.aim1=
  CvsUSM.beetle.vs.flower %>% rbind(CvsUML.beetle.vs.flower) %>% 
  rbind(CvsUSL.beetle.vs.flower) %>%  rbind(CvsUSML.beetle.vs.flower)

contrast.UVSWMW...beetle.vs.flower<-CvsUSM.beetle.vs.flower[,3]
contrast.UV..MWLW.beetle.vs.flower<-CvsUML.beetle.vs.flower[,3]
contrast.UVSW..LW.beetle.vs.flower<-CvsUSL.beetle.vs.flower[,3]
contrast.UVSWMWLW.beetle.vs.flower<-CvsUSML.beetle.vs.flower[,3]

com.contrast.beetle.vs.flower.aim1<-cbind(CvsUSM.beetle.vs.flower[,1:2],contrast.UVSWMW...beetle.vs.flower,contrast.UV..MWLW.beetle.vs.flower,contrast.UVSW..LW.beetle.vs.flower,contrast.UVSWMWLW.beetle.vs.flower)
compare.beetle.vs.flower.aim1 <- com.contrast.beetle.vs.flower.aim1 %>%
  gather(key = "peak_wl.beetle.vs.flower", value = "dS", 3:6)



#D65 - Aim 2
##flower vs leaf
Cbuprest580.flower.vs.leaf=
  Cbuprest580 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest600.flower.vs.leaf=
  Cbuprest600 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest620.flower.vs.leaf=
  Cbuprest620 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest640.flower.vs.leaf=
  Cbuprest640 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest660.flower.vs.leaf=
  Cbuprest660 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

Cbuprest.flower.vs.leaf.aim2=
  Cbuprest580.flower.vs.leaf %>% rbind(Cbuprest600.flower.vs.leaf) %>%
  rbind(Cbuprest620.flower.vs.leaf)%>% rbind(Cbuprest640.flower.vs.leaf) %>% rbind(Cbuprest660.flower.vs.leaf) 

bup580.flower.vs.leaf<-Cbuprest580.flower.vs.leaf[,3]
bup600.flower.vs.leaf<-Cbuprest600.flower.vs.leaf[,3]
bup620.flower.vs.leaf<-Cbuprest620.flower.vs.leaf[,3]
bup640.flower.vs.leaf<-Cbuprest640.flower.vs.leaf[,3]
bup660.flower.vs.leaf<-Cbuprest660.flower.vs.leaf[,3]

com.bupcontrast.flower.vs.leaf.aim2<-cbind(Cbuprest.flower.vs.leaf.aim2[,1:2],bup580.flower.vs.leaf,bup600.flower.vs.leaf,bup620.flower.vs.leaf,bup640.flower.vs.leaf,bup660.flower.vs.leaf)
compare.flower.vs.leaf.aim2 <- com.bupcontrast.flower.vs.leaf.aim2 %>%
  gather(key = "peak_wl.flower.vs.leaf", value = "dS", 3:7)

##beetle vs leaf
Cbuprest580.beetle.vs.leaf=
  Cbuprest580 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest600.beetle.vs.leaf=
  Cbuprest600 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest620.beetle.vs.leaf=
  Cbuprest620 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest640.beetle.vs.leaf=
  Cbuprest640 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest660.beetle.vs.leaf=
  Cbuprest660 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

Cbuprest.beetle.vs.leaf.aim2=
  Cbuprest580.beetle.vs.leaf  %>% rbind(Cbuprest600.beetle.vs.leaf)%>%
  rbind(Cbuprest620.beetle.vs.leaf)%>% rbind(Cbuprest640.beetle.vs.leaf) %>% rbind(Cbuprest660.beetle.vs.leaf)

bup580.beetle.vs.leaf<-Cbuprest580.beetle.vs.leaf[,3]
bup600.beetle.vs.leaf<-Cbuprest600.beetle.vs.leaf[,3]
bup620.beetle.vs.leaf<-Cbuprest620.beetle.vs.leaf[,3]
bup640.beetle.vs.leaf<-Cbuprest640.beetle.vs.leaf[,3]
bup660.beetle.vs.leaf<-Cbuprest660.beetle.vs.leaf[,3]

com.bupcontrast.beetle.vs.leaf.aim2<-cbind(Cbuprest.beetle.vs.leaf.aim2[,1:2],bup580.beetle.vs.leaf,bup600.beetle.vs.leaf,bup620.beetle.vs.leaf,bup640.beetle.vs.leaf,bup660.beetle.vs.leaf)
compare.beetle.vs.leaf.aim2 <- com.bupcontrast.beetle.vs.leaf.aim2 %>%
  gather(key = "peak_wl.beetle.vs.leaf", value = "dS", 3:7)

##beetle vs flower
Cbuprest580.beetle.vs.flower=
  Cbuprest580 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest600.beetle.vs.flower=
  Cbuprest600 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest620.beetle.vs.flower=
  Cbuprest620 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest640.beetle.vs.flower=
  Cbuprest640 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest660.beetle.vs.flower=
  Cbuprest660 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

Cbuprest.beetle.vs.flower.aim2=
  Cbuprest580.beetle.vs.flower %>% rbind(Cbuprest600.beetle.vs.flower) %>% 
  rbind(Cbuprest620.beetle.vs.flower)%>% rbind(Cbuprest640.beetle.vs.flower) %>% 
  rbind(Cbuprest660.beetle.vs.flower)

bup580.beetle.vs.flower<-Cbuprest580.beetle.vs.flower[,3]
bup600.beetle.vs.flower<-Cbuprest600.beetle.vs.flower[,3]
bup620.beetle.vs.flower<-Cbuprest620.beetle.vs.flower[,3]
bup640.beetle.vs.flower<-Cbuprest640.beetle.vs.flower[,3]
bup660.beetle.vs.flower<-Cbuprest660.beetle.vs.flower[,3]

com.bupcontrast.beetle.vs.flower.aim2<-cbind(Cbuprest.beetle.vs.flower.aim2[,1:2],bup580.beetle.vs.flower,bup600.beetle.vs.flower,bup620.beetle.vs.flower,bup640.beetle.vs.flower,bup660.beetle.vs.flower)
compare.beetle.vs.flower.aim2 <- com.bupcontrast.beetle.vs.flower.aim2 %>%
  gather(key = "peak_wl.beetle.vs.flower", value = "dS", 3:7)


#Twilight - aim 1
##flower vs leaf
CvsUSM.flower.vs.leaf_twilight=
  CvsUSM_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvsUML.flower.vs.leaf_twilight=
  CvsUML_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvsUSL.flower.vs.leaf_twilight=
  CvsUSL_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
CvsUSML.flower.vs.leaf_twilight=
  CvsUSML_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

C.flower.vs.leaf_twilight.aim1=
  CvsUSM.flower.vs.leaf_twilight %>% rbind(CvsUML.flower.vs.leaf_twilight) %>% 
  rbind(CvsUSL.flower.vs.leaf_twilight)%>% rbind(CvsUSML.flower.vs.leaf_twilight)

contrast.UVSWMW...flower.vs.leaf_twilight<-CvsUSM.flower.vs.leaf_twilight[,3]
contrast.UV..MWLW.flower.vs.leaf_twilight<-CvsUML.flower.vs.leaf_twilight[,3]
contrast.UVSW..LW.flower.vs.leaf_twilight<-CvsUSL.flower.vs.leaf_twilight[,3]
contrast.UVSWMWLW.flower.vs.leaf_twilight<-CvsUSML.flower.vs.leaf_twilight[,3]

com.contrast.flower.vs.leaf_twilight.aim1<-cbind(CvsUSM.flower.vs.leaf_twilight[,1:2],contrast.UVSWMW...flower.vs.leaf_twilight,contrast.UV..MWLW.flower.vs.leaf_twilight,contrast.UVSW..LW.flower.vs.leaf_twilight,contrast.UVSWMWLW.flower.vs.leaf_twilight)
compare.flower.vs.leaf_twilight.aim1 <- com.contrast.flower.vs.leaf_twilight.aim1 %>%
  gather(key = "peak_wl.flower.vs.leaf", value = "dS", 3:6)

##beetle vs leaf
CvsUSM.beetle.vs.leaf_twilight=
  CvsUSM_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvsUML.beetle.vs.leaf_twilight=
  CvsUML_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvsUSL.beetle.vs.leaf_twilight=
  CvsUSL_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
CvsUSML.beetle.vs.leaf_twilight=
  CvsUSML_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

C.beetle.vs.leaf_twilight.aim1=
  CvsUSM.beetle.vs.leaf_twilight %>% rbind(CvsUML.beetle.vs.leaf_twilight) %>% 
  rbind(CvsUSL.beetle.vs.leaf_twilight)%>%  rbind(CvsUSML.beetle.vs.leaf_twilight)

contrast.UVSWMW...beetle.vs.leaf_twilight<-CvsUSM.beetle.vs.leaf_twilight[,3]
contrast.UV..MWLW.beetle.vs.leaf_twilight<-CvsUML.beetle.vs.leaf_twilight[,3]
contrast.UVSW..LW.beetle.vs.leaf_twilight<-CvsUSL.beetle.vs.leaf_twilight[,3]
contrast.UVSWMWLW.beetle.vs.leaf_twilight<-CvsUSML.beetle.vs.leaf_twilight[,3]

com.contrast.beetle.vs.leaf_twilight.aim1<-cbind(CvsUSM.beetle.vs.leaf_twilight[,1:2],contrast.UVSWMW...beetle.vs.leaf_twilight,contrast.UV..MWLW.beetle.vs.leaf_twilight,contrast.UVSW..LW.beetle.vs.leaf_twilight,contrast.UVSWMWLW.beetle.vs.leaf_twilight)
compare.beetle.vs.leaf_twilight.aim1 <- com.contrast.beetle.vs.leaf_twilight.aim1 %>%
  gather(key = "peak_wl.beetle.vs.leaf", value = "dS", 3:6)

##beetle vs flower
CvsUSM.beetle.vs.flower_twilight=
  CvsUSM_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvsUML.beetle.vs.flower_twilight=
  CvsUML_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvsUSL.beetle.vs.flower_twilight=
  CvsUSL_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
CvsUSML.beetle.vs.flower_twilight=
  CvsUSML_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

C.beetle.vs.flower_twilight.aim1=
  CvsUSM.beetle.vs.flower_twilight %>% rbind(CvsUML.beetle.vs.flower_twilight) %>% 
  rbind(CvsUSL.beetle.vs.flower_twilight) %>%  rbind(CvsUSML.beetle.vs.flower_twilight)

contrast.UVSWMW...beetle.vs.flower_twilight<-CvsUSM.beetle.vs.flower_twilight[,3]
contrast.UV..MWLW.beetle.vs.flower_twilight<-CvsUML.beetle.vs.flower_twilight[,3]
contrast.UVSW..LW.beetle.vs.flower_twilight<-CvsUSL.beetle.vs.flower_twilight[,3]
contrast.UVSWMWLW.beetle.vs.flower_twilight<-CvsUSML.beetle.vs.flower_twilight[,3]

com.contrast.beetle.vs.flower_twilight.aim1<-cbind(CvsUSM.beetle.vs.flower_twilight[,1:2],contrast.UVSWMW...beetle.vs.flower_twilight,contrast.UV..MWLW.beetle.vs.flower_twilight,contrast.UVSW..LW.beetle.vs.flower_twilight,contrast.UVSWMWLW.beetle.vs.flower_twilight)
compare.beetle.vs.flower_twilight.aim1 <- com.contrast.beetle.vs.flower_twilight.aim1 %>%
  gather(key = "peak_wl.beetle.vs.flower", value = "dS", 3:6)



#Twilight - Aim 2
##flower vs leaf
Cbuprest580.flower.vs.leaf_twilight=
  Cbuprest580_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest600.flower.vs.leaf_twilight=
  Cbuprest600_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest620.flower.vs.leaf_twilight=
  Cbuprest620_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest640.flower.vs.leaf_twilight=
  Cbuprest640_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest660.flower.vs.leaf_twilight=
  Cbuprest660_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

Cbuprest.flower.vs.leaf_twilight.aim2=
  Cbuprest580.flower.vs.leaf_twilight %>% rbind(Cbuprest600.flower.vs.leaf_twilight) %>%
  rbind(Cbuprest620.flower.vs.leaf_twilight)%>% rbind(Cbuprest640.flower.vs.leaf_twilight) %>% rbind(Cbuprest660.flower.vs.leaf_twilight)

bup580.flower.vs.leaf_twilight<-Cbuprest580.flower.vs.leaf_twilight[,3]
bup600.flower.vs.leaf_twilight<-Cbuprest600.flower.vs.leaf_twilight[,3]
bup620.flower.vs.leaf_twilight<-Cbuprest620.flower.vs.leaf_twilight[,3]
bup640.flower.vs.leaf_twilight<-Cbuprest640.flower.vs.leaf_twilight[,3]
bup660.flower.vs.leaf_twilight<-Cbuprest660.flower.vs.leaf_twilight[,3]

com.bupcontrast.flower.vs.leaf_twilight.aim2<-cbind(Cbuprest.flower.vs.leaf_twilight.aim2[,1:2],bup580.flower.vs.leaf_twilight,bup600.flower.vs.leaf_twilight,bup620.flower.vs.leaf_twilight,bup640.flower.vs.leaf_twilight,bup660.flower.vs.leaf_twilight)
compare.flower.vs.leaf_twilight.aim2 <- com.bupcontrast.flower.vs.leaf_twilight.aim2 %>%
  gather(key = "peak_wl.flower.vs.leaf", value = "dS", 3:7)

##beetle vs leaf
Cbuprest580.beetle.vs.leaf_twilight=
  Cbuprest580_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest600.beetle.vs.leaf_twilight=
  Cbuprest600_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest620.beetle.vs.leaf_twilight=
  Cbuprest620_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest640.beetle.vs.leaf_twilight=
  Cbuprest640_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest660.beetle.vs.leaf_twilight=
  Cbuprest660_twilight %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

Cbuprest.beetle.vs.leaf_twilight.aim2=
  Cbuprest580.beetle.vs.leaf_twilight  %>% rbind(Cbuprest600.beetle.vs.leaf_twilight)%>%
  rbind(Cbuprest620.beetle.vs.leaf_twilight)%>% rbind(Cbuprest640.beetle.vs.leaf_twilight) %>%
  rbind(Cbuprest660.beetle.vs.leaf_twilight)

bup580.beetle.vs.leaf_twilight<-Cbuprest580.beetle.vs.leaf_twilight[,3]
bup600.beetle.vs.leaf_twilight<-Cbuprest600.beetle.vs.leaf_twilight[,3]
bup620.beetle.vs.leaf_twilight<-Cbuprest620.beetle.vs.leaf_twilight[,3]
bup640.beetle.vs.leaf_twilight<-Cbuprest640.beetle.vs.leaf_twilight[,3]
bup660.beetle.vs.leaf_twilight<-Cbuprest660.beetle.vs.leaf_twilight[,3]

com.bupcontrast.beetle.vs.leaf_twilight.aim2<-cbind(Cbuprest.beetle.vs.leaf_twilight.aim2[,1:2],bup580.beetle.vs.leaf_twilight,bup600.beetle.vs.leaf_twilight,bup620.beetle.vs.leaf_twilight,bup640.beetle.vs.leaf_twilight,bup660.beetle.vs.leaf_twilight)
compare.beetle.vs.leaf_twilight.aim2 <- com.bupcontrast.beetle.vs.leaf_twilight.aim2 %>%
  gather(key = "peak_wl.beetle.vs.leaf", value = "dS", 3:7)

##beetle vs flower
Cbuprest580.beetle.vs.flower_twilight=
  Cbuprest580_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest600.beetle.vs.flower_twilight=
  Cbuprest600_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest620.beetle.vs.flower_twilight=
  Cbuprest620_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest640.beetle.vs.flower_twilight=
  Cbuprest640_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest660.beetle.vs.flower_twilight=
  Cbuprest660_twilight %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

Cbuprest.beetle.vs.flower_twilight.aim2=
  Cbuprest580.beetle.vs.flower_twilight %>%rbind(Cbuprest600.beetle.vs.flower_twilight) %>% 
  rbind(Cbuprest620.beetle.vs.flower_twilight) %>% rbind(Cbuprest640.beetle.vs.flower_twilight) %>% 
  rbind(Cbuprest660.beetle.vs.flower_twilight)

bup580.beetle.vs.flower_twilight<-Cbuprest580.beetle.vs.flower_twilight[,3]
bup600.beetle.vs.flower_twilight<-Cbuprest600.beetle.vs.flower_twilight[,3]
bup620.beetle.vs.flower_twilight<-Cbuprest620.beetle.vs.flower_twilight[,3]
bup640.beetle.vs.flower_twilight<-Cbuprest640.beetle.vs.flower_twilight[,3]
bup660.beetle.vs.flower_twilight<-Cbuprest660.beetle.vs.flower_twilight[,3]

com.bupcontrast.beetle.vs.flower_twilight.aim2<-cbind(Cbuprest.beetle.vs.flower_twilight.aim2[,1:2],bup580.beetle.vs.flower_twilight,bup600.beetle.vs.flower_twilight,bup620.beetle.vs.flower_twilight,bup640.beetle.vs.flower_twilight,bup660.beetle.vs.flower_twilight)
compare.beetle.vs.flower_twilight.aim2 <- com.bupcontrast.beetle.vs.flower_twilight.aim2 %>%
  gather(key = "peak_wl.beetle.vs.flower", value = "dS", 3:7)

```

##Check assumptions {.tabset .tabset-fade .tabset-pills}

* Before running the GLMMs, we first check if the data follows the assumption of normality and homogeneity of variance

</br>

Click the tabs to choose the assumptions ( __Normality__ / __Homogeneity__ ) of the visual models ( __Aim 1__ / __Aim 2__ ) under different light conditions ( __Daylight__ / __Twilight__)

</br>


```{r}
#checking assumptions
##D65 - aim 1
res.flower.vs.leaf_d65.aim1<-lm(compare.flower.vs.leaf.aim1$dS ~ compare.flower.vs.leaf.aim1$peak_wl.flower.vs.leaf)
res.beetle.vs.leaf_d65.aim1<-lm(compare.beetle.vs.leaf.aim1$dS ~ compare.beetle.vs.leaf.aim1$peak_wl.beetle.vs.leaf)
res.beetle.vs.flower_d65.aim1<-lm(compare.beetle.vs.flower.aim1$dS ~ compare.beetle.vs.flower.aim1$peak_wl.beetle.vs.flower)

##D65 - Aim 2
res.flower.vs.leaf_d65.aim2<-lm(compare.flower.vs.leaf.aim2$dS ~ compare.flower.vs.leaf.aim2$peak_wl.flower.vs.leaf)
res.beetle.vs.leaf_d65.aim2<-lm(compare.beetle.vs.leaf.aim2$dS ~ compare.beetle.vs.leaf.aim2$peak_wl.beetle.vs.leaf)
res.beetle.vs.flower_d65.aim2<-lm(compare.beetle.vs.flower.aim2$dS ~ compare.beetle.vs.flower.aim2$peak_wl.beetle.vs.flower)

##Twilight - aim 1
res.flower.vs.leaf_twilight.aim1<-lm(compare.flower.vs.leaf.aim1$dS ~ compare.flower.vs.leaf.aim1$peak_wl.flower.vs.leaf)
res.beetle.vs.leaf_twilight.aim1<-lm(compare.beetle.vs.leaf.aim1$dS ~ compare.beetle.vs.leaf.aim1$peak_wl.beetle.vs.leaf)
res.beetle.vs.flower_twilight.aim1<-lm(compare.beetle.vs.flower.aim1$dS ~ compare.beetle.vs.flower.aim1$peak_wl.beetle.vs.flower)

##Twilight - Aim 2
res.flower.vs.leaf_twilight.aim2<-lm(compare.flower.vs.leaf.aim2$dS ~ compare.flower.vs.leaf.aim2$peak_wl.flower.vs.leaf)
res.beetle.vs.leaf_twilight.aim2<-lm(compare.beetle.vs.leaf.aim2$dS ~ compare.beetle.vs.leaf.aim2$peak_wl.beetle.vs.leaf)
res.beetle.vs.flower_twilight.aim2<-lm(compare.beetle.vs.flower.aim2$dS ~ compare.beetle.vs.flower.aim2$peak_wl.beetle.vs.flower)
```

### Normality {.tabset .tabset-fade .tabset-pills}
#### Aim 1 {.tabset .tabset-fade .tabset-pills}

##### D65 
```{r}
par (mfrow=c(1,3),pin=c(1.5, 1.5))
qqnorm(res.flower.vs.leaf_d65.aim1$residuals, main = "Flower vs Leaf")
qqnorm(res.beetle.vs.leaf_d65.aim1$residuals, main = "Beetle vs Leaf")
qqnorm(res.beetle.vs.flower_d65.aim1$residuals, main = "Beetle vs Flower")
```

##### Twilight
```{r}
par (mfrow=c(1,3),pin=c(1.5, 1.5))
qqnorm(res.flower.vs.leaf_twilight.aim1$residuals, main = "Flower vs Leaf")
qqnorm(res.beetle.vs.leaf_twilight.aim1$residuals, main = "Beetle vs Leaf")
qqnorm(res.beetle.vs.flower_twilight.aim1$residuals, main = "Beetle vs Flower")
```

#### Aim 2 {.tabset .tabset-fade .tabset-pills}
##### D65 
```{r}
par (mfrow=c(1,3),pin=c(1.5, 1.5))
qqnorm(res.flower.vs.leaf_d65.aim2$residuals, main = "Flower vs Leaf")
qqnorm(res.beetle.vs.leaf_d65.aim2$residuals, main = "Beetle vs Leaf")
qqnorm(res.beetle.vs.flower_d65.aim2$residuals, main = "Beetle vs Flower")
```

##### Twilight
```{r}
par (mfrow=c(1,3),pin=c(1.5, 1.5))
qqnorm(res.flower.vs.leaf_twilight.aim2$residuals, main = "Flower vs Leaf")
qqnorm(res.beetle.vs.leaf_twilight.aim2$residuals, main = "Beetle vs Leaf")
qqnorm(res.beetle.vs.flower_twilight.aim2$residuals, main = "Beetle vs Flower")
```

### Homoscedasticity {.tabset .tabset-fade .tabset-pills}
#### Aim 1 {.tabset .tabset-fade .tabset-pills}

##### D65
```{r}
par (mfrow=c(1,3),oma=c(2,2,0,0)) #oma=c() to creat space for common lables
boxplot(compare.flower.vs.leaf.aim1$dS~compare.flower.vs.leaf.aim1$peak_wl.flower.vs.leaf, las=2,
        main = "Flower vs Leaf",
        names=c("UML", "USL", "USM", "USML"))
boxplot(compare.beetle.vs.leaf.aim1$dS~compare.beetle.vs.leaf.aim1$peak_wl.beetle.vs.leaf, las=2,
        main = "Beetle vs Leaf",
        names=c("UML", "USL", "USM", "USML"))
boxplot(compare.beetle.vs.flower.aim1$dS~compare.beetle.vs.flower.aim1$peak_wl.beetle.vs.flower, las=2,
        main = "Beetle vs Flower",
        names=c("UML", "USL", "USM", "USML"))
mtext("Visual system",side=1,line=0,outer=TRUE,cex=1.3) #side assigns the position of the text e.g. bottom
mtext("Contrast (JND)",side=2,line=0,outer=TRUE,cex=1.3,las=0) #las assigns the orientation of the text
```

##### Twilight
```{r}
par (mfrow=c(1,3),oma=c(2,2,0,0))
boxplot(compare.flower.vs.leaf_twilight.aim1$dS~compare.flower.vs.leaf_twilight.aim1$peak_wl.flower.vs.leaf, las=2,
        main = "Flower vs Leaf",
        names=c("UML", "USL", "USM", "USML"))
boxplot(compare.beetle.vs.leaf_twilight.aim1$dS~compare.beetle.vs.leaf_twilight.aim1$peak_wl.beetle.vs.leaf, las=2,
        main = "Beetle vs Leaf",
        names=c("UML", "USL", "USM", "USML"))
boxplot(compare.beetle.vs.flower_twilight.aim1$dS~compare.beetle.vs.flower_twilight.aim1$peak_wl.beetle.vs.flower, las=2,
        main = "Beetle vs Flower",
        names=c("UML", "USL", "USM", "USML"))
mtext("Visual system",side=1,line=0,outer=TRUE,cex=1.3)
mtext("Contrast (JND)",side=2,line=0,outer=TRUE,cex=1.3,las=0)
```

#### Aim 2 {.tabset .tabset-fade .tabset-pills}
##### D65
```{r}
par (mfrow=c(1,3),oma=c(2,2,0,0))
boxplot(compare.flower.vs.leaf.aim2$dS~compare.flower.vs.leaf.aim2$peak_wl.flower.vs.leaf, las=2,
        main = "Flower vs Leaf",
        names=c("VS 580", "VS 600", "VS 620", "VS 640", "Vis 660"))
boxplot(compare.beetle.vs.leaf.aim2$dS~compare.beetle.vs.leaf.aim2$peak_wl.beetle.vs.leaf, las=2,
        main = "Beetle vs Leaf",
        names=c("VS 580", "VS 600", "VS 620", "VS 640", "Vis 660"))
boxplot(compare.beetle.vs.flower.aim2$dS~compare.beetle.vs.flower.aim2$peak_wl.beetle.vs.flower, las=2,
        main = "Beetle vs Flower",
        names=c("VS 580", "VS 600", "VS 620", "VS 640", "Vis 660"))
mtext("Visual system",side=1,line=0,outer=TRUE,cex=1.3)
mtext("Contrast (JND)",side=2,line=0,outer=TRUE,cex=1.3,las=0)
```

##### Twilight 
```{r}
par (mfrow=c(1,3),oma=c(2,2,0,0))
boxplot(compare.flower.vs.leaf_twilight.aim2$dS~compare.flower.vs.leaf_twilight.aim2$peak_wl.flower.vs.leaf, las=2,
        main = "Flower vs Leaf",
        names=c("VS 580", "VS 600", "VS 620", "VS 640", "Vis 660"))
boxplot(compare.beetle.vs.leaf_twilight.aim2$dS~compare.beetle.vs.leaf_twilight.aim2$peak_wl.beetle.vs.leaf, las=2,
        main = "Beetle vs Leaf",
        names=c("VS 580", "VS 600", "VS 620", "VS 640", "Vis 660"))
boxplot(compare.beetle.vs.flower_twilight.aim2$dS~compare.beetle.vs.flower_twilight.aim2$peak_wl.beetle.vs.flower, las=2,
        main = "Beetle vs Flower",
        names=c("VS 580", "VS 600", "VS 620", "VS 640", "Vis 660"))
mtext("Visual system",side=1,line=0,outer=TRUE,cex=1.3)
mtext("Contrast (JND)",side=2,line=0,outer=TRUE,cex=1.3,las=0)
```


</br>
</br>

##GLMM results

</br>

```{r}
#GLMM - D65 - aim 1
##Flower vs Leaf
m.flower.vs.leaf_d65.aim1 <- lmer(dS~peak_wl.flower.vs.leaf + (1|patch2) + (1|patch1), data = compare.flower.vs.leaf.aim1,REML=F)
sum.flower.vs.leaf_d65.aim1<-summary(glht(m.flower.vs.leaf_d65.aim1, linfct = mcp(peak_wl.flower.vs.leaf = "Tukey")), test = adjusted("bonferroni"))
#REML=F, in order to fit the model using the likelihood ratio test. Otherwise, the lmer default will fit the model using the REML (REstricted Maximum Likelihood) criterion.

##Beetle vs Leaf
m.beetle.vs.leaf_d65.aim1 <- lmer(dS~peak_wl.beetle.vs.leaf + (1|patch2) + (1|patch1), data = compare.beetle.vs.leaf.aim1,REML=F)
sum.beetle.vs.leaf_d65.aim1 <- summary(glht(m.beetle.vs.leaf_d65.aim1, linfct = mcp(peak_wl.beetle.vs.leaf = "Tukey")), test = adjusted("bonferroni"))

##Beetle vs Flower
m.beetle.vs.flower_d65.aim1 <- lmer(dS~peak_wl.beetle.vs.flower + (1|patch2) + (1|patch1), data = compare.beetle.vs.flower.aim1,REML=F)
sum.beetle.vs.flower_d65.aim1 <-summary(glht(m.beetle.vs.flower_d65.aim1, linfct = mcp(peak_wl.beetle.vs.flower = "Tukey")), test = adjusted("bonferroni"))

###reshape data for heatmap
p1_d65.aim1<-sum.flower.vs.leaf_d65.aim1[["test"]][["pvalues"]]
p2_d65.aim1<-sum.beetle.vs.leaf_d65.aim1[["test"]][["pvalues"]]
p3_d65.aim1<-sum.beetle.vs.flower_d65.aim1[["test"]][["pvalues"]]

VislistA_d65.aim1<-c("USL", "USM","USML","USM","USML","USML")
VislistB_d65.aim1<-c("UML", "UML","UML","USL","USL","USM")

heat_d65.aim1<-data.frame(names(p1_d65.aim1),as.numeric(str_extract(p1_d65.aim1,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2_d65.aim1,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3_d65.aim1,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, flower.vs.leaf = 2, beetle.vs.leaf = 3, beetle.vs.flower = 4) %>% 
  cbind(VislistA_d65.aim1) %>% 
  cbind(VislistB_d65.aim1) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat_d65.aim1$sig.flower.vs.leaf[heat_d65.aim1$flower.vs.leaf > 0.05] <- ""
heat_d65.aim1$sig.flower.vs.leaf[heat_d65.aim1$flower.vs.leaf < 0.05] <- "*"
heat_d65.aim1$sig.flower.vs.leaf[heat_d65.aim1$flower.vs.leaf < 0.01] <- "**"
heat_d65.aim1$sig.flower.vs.leaf[heat_d65.aim1$flower.vs.leaf < 0.0001] <- "***"
heat_d65.aim1$sig.beetle.vs.leaf[heat_d65.aim1$beetle.vs.leaf > 0.05] <- ""
heat_d65.aim1$sig.beetle.vs.leaf[heat_d65.aim1$beetle.vs.leaf < 0.05] <- "*"
heat_d65.aim1$sig.beetle.vs.leaf[heat_d65.aim1$beetle.vs.leaf < 0.01] <- "**"
heat_d65.aim1$sig.beetle.vs.leaf[heat_d65.aim1$beetle.vs.leaf < 0.0001] <- "***"
heat_d65.aim1$sig.beetle.vs.flower[heat_d65.aim1$beetle.vs.flower > 0.05] <- ""
heat_d65.aim1$sig.beetle.vs.flower[heat_d65.aim1$beetle.vs.flower < 0.05] <- "*"
heat_d65.aim1$sig.beetle.vs.flower[heat_d65.aim1$beetle.vs.flower < 0.01] <- "**"
heat_d65.aim1$sig.beetle.vs.flower[heat_d65.aim1$beetle.vs.flower < 0.0001] <- "***"


#GLMM - D65 - Aim 2
##Flower vs Leaf
m.flower.vs.leaf_d65.aim2 <- lmer(dS~peak_wl.flower.vs.leaf + (1|patch2) + (1|patch1), data = compare.flower.vs.leaf.aim2,REML=F)
sum.flower.vs.leaf_d65.aim2 <- summary(glht(m.flower.vs.leaf_d65.aim2, linfct = mcp(peak_wl.flower.vs.leaf = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Leaf
m.beetle.vs.leaf_d65.aim2 <- lmer(dS~peak_wl.beetle.vs.leaf + (1|patch2) + (1|patch1), data = compare.beetle.vs.leaf.aim2,REML=F)
sum.beetle.vs.leaf_d65.aim2 <- summary(glht(m.beetle.vs.leaf_d65.aim2, linfct = mcp(peak_wl.beetle.vs.leaf = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Flower
m.beetle.vs.flower_d65.aim2 <- lmer(dS~peak_wl.beetle.vs.flower + (1|patch2) + (1|patch1), data = compare.beetle.vs.flower.aim2,REML=F)
sum.beetle.vs.flower_d65.aim2 <- summary(glht(m.beetle.vs.flower_d65.aim2, linfct = mcp(peak_wl.beetle.vs.flower = "Tukey")), test = adjusted("bonferroni"))

###reshape data for heatmap
p1_d65.aim2<-sum.flower.vs.leaf_d65.aim2[["test"]][["pvalues"]]
p2_d65.aim2<-sum.beetle.vs.leaf_d65.aim2[["test"]][["pvalues"]]
p3_d65.aim2<-sum.beetle.vs.flower_d65.aim2[["test"]][["pvalues"]]

VislistA_d65.aim2<-c("VS 600", "VS 620","VS 640","Vis 660","VS 620","VS 640","Vis 660","VS 640","Vis 660","Vis 660")
VislistB_d65.aim2<-c("VS 580","VS 580","VS 580","VS 580","VS 600","VS 600","VS 600","VS 620","VS 620","VS 640")

heat_d65.aim2<-data.frame(names(p1_d65.aim2),as.numeric(str_extract(p1_d65.aim2,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2_d65.aim2,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3_d65.aim2,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, flower.vs.leaf = 2, beetle.vs.leaf = 3, beetle.vs.flower = 4) %>% 
  cbind(VislistA_d65.aim2) %>% 
  cbind(VislistB_d65.aim2) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat_d65.aim2$sig.flower.vs.leaf[heat_d65.aim2$flower.vs.leaf > 0.05] <- ""
heat_d65.aim2$sig.flower.vs.leaf[heat_d65.aim2$flower.vs.leaf < 0.05] <- "*"
heat_d65.aim2$sig.flower.vs.leaf[heat_d65.aim2$flower.vs.leaf < 0.01] <- "**"
heat_d65.aim2$sig.flower.vs.leaf[heat_d65.aim2$flower.vs.leaf < 0.0001] <- "***"
heat_d65.aim2$sig.beetle.vs.leaf[heat_d65.aim2$beetle.vs.leaf > 0.05] <- ""
heat_d65.aim2$sig.beetle.vs.leaf[heat_d65.aim2$beetle.vs.leaf < 0.05] <- "*"
heat_d65.aim2$sig.beetle.vs.leaf[heat_d65.aim2$beetle.vs.leaf < 0.01] <- "**"
heat_d65.aim2$sig.beetle.vs.leaf[heat_d65.aim2$beetle.vs.leaf < 0.0001] <- "***"
heat_d65.aim2$sig.beetle.vs.flower[heat_d65.aim2$beetle.vs.flower > 0.05] <- ""
heat_d65.aim2$sig.beetle.vs.flower[heat_d65.aim2$beetle.vs.flower < 0.05] <- "*"
heat_d65.aim2$sig.beetle.vs.flower[heat_d65.aim2$beetle.vs.flower < 0.01] <- "**"
heat_d65.aim2$sig.beetle.vs.flower[heat_d65.aim2$beetle.vs.flower < 0.0001] <- "***"




#GLMM - Twilight - aim 1
##Flower vs Leaf
m.flower.vs.leaf_twilight.aim1 <- lmer(dS~peak_wl.flower.vs.leaf + (1|patch2) + (1|patch1), data = compare.flower.vs.leaf_twilight.aim1,REML=F)
sum.flower.vs.leaf_twilight.aim1 <- summary(glht(m.flower.vs.leaf_twilight.aim1, linfct = mcp(peak_wl.flower.vs.leaf = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Leaf
m.beetle.vs.leaf_twilight.aim1 <- lmer(dS~peak_wl.beetle.vs.leaf + (1|patch2) + (1|patch1), data = compare.beetle.vs.leaf_twilight.aim1,REML=F)
sum.beetle.vs.leaf_twilight.aim1<-summary(glht(m.beetle.vs.leaf_twilight.aim1, linfct = mcp(peak_wl.beetle.vs.leaf = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Flower
m.beetle.vs.flower_twilight.aim1 <- lmer(dS~peak_wl.beetle.vs.flower + (1|patch2) + (1|patch1), data = compare.beetle.vs.flower_twilight.aim1,REML=F)
sum.beetle.vs.flower_twilight.aim1<-summary(glht(m.beetle.vs.flower_twilight.aim1, linfct = mcp(peak_wl.beetle.vs.flower = "Tukey")), test = adjusted("bonferroni"))
###reshape data for heatmap
p1_twilight.aim1<-sum.flower.vs.leaf_twilight.aim1[["test"]][["pvalues"]]
p2_twilight.aim1<-sum.beetle.vs.leaf_twilight.aim1[["test"]][["pvalues"]]
p3_twilight.aim1<-sum.beetle.vs.flower_twilight.aim1[["test"]][["pvalues"]]

VislistA_twilight.aim1<-c("USL", "USM","USML","USM","USML","USML")
VislistB_twilight.aim1<-c("UML", "UML","UML","USL","USL","USM")

heat_twilight.aim1<-data.frame(names(p1_twilight.aim1),as.numeric(str_extract(p1_twilight.aim1,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2_twilight.aim1,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3_twilight.aim1,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, flower.vs.leaf = 2, beetle.vs.leaf = 3, beetle.vs.flower = 4) %>% 
  cbind(VislistA_twilight.aim1) %>% 
  cbind(VislistB_twilight.aim1) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat_twilight.aim1$sig.flower.vs.leaf[heat_twilight.aim1$flower.vs.leaf > 0.05] <- ""
heat_twilight.aim1$sig.flower.vs.leaf[heat_twilight.aim1$flower.vs.leaf < 0.05] <- "*"
heat_twilight.aim1$sig.flower.vs.leaf[heat_twilight.aim1$flower.vs.leaf < 0.01] <- "**"
heat_twilight.aim1$sig.flower.vs.leaf[heat_twilight.aim1$flower.vs.leaf < 0.0001] <- "***"
heat_twilight.aim1$sig.beetle.vs.leaf[heat_twilight.aim1$beetle.vs.leaf > 0.05] <- ""
heat_twilight.aim1$sig.beetle.vs.leaf[heat_twilight.aim1$beetle.vs.leaf < 0.05] <- "*"
heat_twilight.aim1$sig.beetle.vs.leaf[heat_twilight.aim1$beetle.vs.leaf < 0.01] <- "**"
heat_twilight.aim1$sig.beetle.vs.leaf[heat_twilight.aim1$beetle.vs.leaf < 0.0001] <- "***"
heat_twilight.aim1$sig.beetle.vs.flower[heat_twilight.aim1$beetle.vs.flower > 0.05] <- ""
heat_twilight.aim1$sig.beetle.vs.flower[heat_twilight.aim1$beetle.vs.flower < 0.05] <- "*"
heat_twilight.aim1$sig.beetle.vs.flower[heat_twilight.aim1$beetle.vs.flower < 0.01] <- "**"
heat_twilight.aim1$sig.beetle.vs.flower[heat_twilight.aim1$beetle.vs.flower < 0.0001] <- "***"




#GLMM - Twilight - Aim 2
##Flower vs Leaf
m.flower.vs.leaf_twilight.aim2 <- lmer(dS~peak_wl.flower.vs.leaf + (1|patch2) + (1|patch1), data = compare.flower.vs.leaf_twilight.aim2,REML=F)
sum.flower.vs.leaf_twilight.aim2 <- summary(glht(m.flower.vs.leaf_twilight.aim2, linfct = mcp(peak_wl.flower.vs.leaf = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Leaf
m.beetle.vs.leaf_twilight.aim2 <- lmer(dS~peak_wl.beetle.vs.leaf + (1|patch2) + (1|patch1), data = compare.beetle.vs.leaf_twilight.aim2,REML=F)
sum.beetle.vs.leaf_twilight.aim2 <- summary(glht(m.beetle.vs.leaf_twilight.aim2, linfct = mcp(peak_wl.beetle.vs.leaf = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Flower
m.beetle.vs.flower_twilight.aim2 <- lmer(dS~peak_wl.beetle.vs.flower + (1|patch2) + (1|patch1), data = compare.beetle.vs.flower_twilight.aim2,REML=F)
sum.beetle.vs.flower_twilight.aim2 <-summary(glht(m.beetle.vs.flower_twilight.aim2, linfct = mcp(peak_wl.beetle.vs.flower = "Tukey")), test = adjusted("bonferroni"))
###reshape data for heatmap
p1_twilight.aim2<-sum.flower.vs.leaf_twilight.aim2[["test"]][["pvalues"]]
p2_twilight.aim2<-sum.beetle.vs.leaf_twilight.aim2[["test"]][["pvalues"]]
p3_twilight.aim2<-sum.beetle.vs.flower_twilight.aim2[["test"]][["pvalues"]]

VislistA_twilight.aim2<-c("VS 600", "VS 620","VS 640","Vis 660","VS 620","VS 640","Vis 660","VS 640","Vis 660","Vis 660")
VislistB_twilight.aim2<-c("VS 580","VS 580","VS 580","VS 580","VS 600","VS 600","VS 600","VS 620","VS 620","VS 640")

heat_twilight.aim2<-data.frame(names(p1_twilight.aim2),as.numeric(str_extract(p1_twilight.aim2,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2_twilight.aim2,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3_twilight.aim2,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, flower.vs.leaf = 2, beetle.vs.leaf = 3, beetle.vs.flower = 4) %>% 
  cbind(VislistA_twilight.aim2) %>% 
  cbind(VislistB_twilight.aim2) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat_twilight.aim2$sig.flower.vs.leaf[heat_twilight.aim2$flower.vs.leaf > 0.05] <- ""
heat_twilight.aim2$sig.flower.vs.leaf[heat_twilight.aim2$flower.vs.leaf < 0.05] <- "*"
heat_twilight.aim2$sig.flower.vs.leaf[heat_twilight.aim2$flower.vs.leaf < 0.01] <- "**"
heat_twilight.aim2$sig.flower.vs.leaf[heat_twilight.aim2$flower.vs.leaf < 0.0001] <- "***"
heat_twilight.aim2$sig.beetle.vs.leaf[heat_twilight.aim2$beetle.vs.leaf > 0.05] <- ""
heat_twilight.aim2$sig.beetle.vs.leaf[heat_twilight.aim2$beetle.vs.leaf < 0.05] <- "*"
heat_twilight.aim2$sig.beetle.vs.leaf[heat_twilight.aim2$beetle.vs.leaf < 0.01] <- "**"
heat_twilight.aim2$sig.beetle.vs.leaf[heat_twilight.aim2$beetle.vs.leaf < 0.0001] <- "***"
heat_twilight.aim2$sig.beetle.vs.flower[heat_twilight.aim2$beetle.vs.flower > 0.05] <- ""
heat_twilight.aim2$sig.beetle.vs.flower[heat_twilight.aim2$beetle.vs.flower < 0.05] <- "*"
heat_twilight.aim2$sig.beetle.vs.flower[heat_twilight.aim2$beetle.vs.flower < 0.01] <- "**"
heat_twilight.aim2$sig.beetle.vs.flower[heat_twilight.aim2$beetle.vs.flower < 0.0001] <- "***"
```

### Results of Aim 1: comparing visual systems with different photoreceptor combinations {.tabset .tabset-fade .tabset-pills}

</br>

Click the tabs to see the results for each comparison group ( __Flower vs. Leaf__ / __Beetle vs. Leaf__ / __Beetle vs. Flower__) and under different light conditions ( __Daylight__ / __Twilight__)

</br>

#### __Flower v.s Leaf__ {.tabset .tabset-fade .tabset-pills}
#####Daylight{.tabset .tabset-fade .tabset-pills}

```{r}
Anova(m.flower.vs.leaf_d65.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.aim1, aes(x=VislistA_d65.aim1, y=VislistB_d65.aim1, fill=flower.vs.leaf)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.aim1, VislistB_d65.aim1, label = paste(format(round(flower.vs.leaf, 2), nsmall = 2), sig.flower.vs.leaf)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.flower.vs.leaf_d65.aim1
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.leaf_twilight.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.aim1, aes(x=VislistA_twilight.aim1, y=VislistB_twilight.aim1, fill=flower.vs.leaf)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.aim1, VislistB_twilight.aim1, label = paste(format(round(flower.vs.leaf, 2), nsmall = 2), sig.flower.vs.leaf)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.flower.vs.leaf_twilight.aim1
```

#### __Beetle vs. Leaf__ {.tabset .tabset-fade .tabset-pills}
#####Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.leaf_d65.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.aim1, aes(x=VislistA_d65.aim1, y=VislistB_d65.aim1, fill=beetle.vs.leaf)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.aim1, VislistB_d65.aim1, label = paste(format(round(beetle.vs.leaf, 2), nsmall = 2), sig.beetle.vs.leaf))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.beetle.vs.leaf_d65.aim1
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.leaf_twilight.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.aim1, aes(x=VislistA_twilight.aim1, y=VislistB_twilight.aim1, fill=beetle.vs.leaf)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.aim1, VislistB_twilight.aim1, label = paste(format(round(beetle.vs.leaf, 2), nsmall = 2), sig.beetle.vs.leaf))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.beetle.vs.leaf_twilight.aim1
```

#### __Beetle vs. Flower__ {.tabset .tabset-fade .tabset-pills}
#####Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.flower_d65.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.aim1, aes(x=VislistA_d65.aim1, y=VislistB_d65.aim1, fill=beetle.vs.flower)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.aim1, VislistB_d65.aim1, label = paste(format(round(beetle.vs.flower, 2), nsmall = 2), sig.beetle.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour 
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.beetle.vs.flower_d65.aim1
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.flower_twilight.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.aim1, aes(x=VislistA_twilight.aim1, y=VislistB_twilight.aim1, fill=beetle.vs.flower)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.aim1, VislistB_twilight.aim1, label = paste(format(round(beetle.vs.flower, 2), nsmall = 2), sig.beetle.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.beetle.vs.flower_twilight.aim1
```


</br>
</br>


### Results of Aim 2: comparing visual systems with different LWS peak sensitivities {.tabset .tabset-fade .tabset-pills}

</br>

Click the tabs to see the results for each comparison group ( __Flower vs. Leaf__ / __Beetle vs. Leaf__ / __Beetle vs. Flower__) and under different light conditions ( __Daylight__ / __Twilight__)

</br>

#### __Flower vs. Leaf__ {.tabset .tabset-fade .tabset-pills}

#####Daylight{.tabset .tabset-fade .tabset-pills}

```{r}
Anova(m.flower.vs.leaf_d65.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.aim2, aes(x=VislistA_d65.aim2, y=VislistB_d65.aim2, fill=flower.vs.leaf)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.aim2, VislistB_d65.aim2, label = paste(format(round(flower.vs.leaf, 2), nsmall = 2), sig.flower.vs.leaf)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.flower.vs.leaf_d65.aim2
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.leaf_twilight.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.aim2, aes(x=VislistA_twilight.aim2, y=VislistB_twilight.aim2, fill=flower.vs.leaf)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.aim2, VislistB_twilight.aim2, label = paste(format(round(flower.vs.leaf, 2), nsmall = 2), sig.flower.vs.leaf)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.flower.vs.leaf_twilight.aim2
```

#### __Beetle vs. Leaf__ {.tabset .tabset-fade .tabset-pills}
#####Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.leaf_d65.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.aim2, aes(x=VislistA_d65.aim2, y=VislistB_d65.aim2, fill=beetle.vs.leaf)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.aim2, VislistB_d65.aim2, label = paste(format(round(beetle.vs.leaf, 2), nsmall = 2), sig.beetle.vs.leaf))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.beetle.vs.leaf_d65.aim2
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.leaf_twilight.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.aim2, aes(x=VislistA_twilight.aim2, y=VislistB_twilight.aim2, fill=beetle.vs.leaf)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.aim2, VislistB_twilight.aim2, label = paste(format(round(beetle.vs.leaf, 2), nsmall = 2), sig.beetle.vs.leaf))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.beetle.vs.leaf_twilight.aim2
```

#### __Beetle vs. Flower__ {.tabset .tabset-fade .tabset-pills}
#####Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.flower_d65.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values 
```{r}
ggplot(data = heat_d65.aim2, aes(x=VislistA_d65.aim2, y=VislistB_d65.aim2, fill=beetle.vs.flower)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_d65.aim2, VislistB_d65.aim2, label = paste(format(round(beetle.vs.flower, 2), nsmall = 2), sig.beetle.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour 
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.beetle.vs.flower_d65.aim2
```

#####Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.flower_twilight.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

######Pair-wise p-values
```{r}
ggplot(data = heat_twilight.aim2, aes(x=VislistA_twilight.aim2, y=VislistB_twilight.aim2, fill=beetle.vs.flower)) + 
  geom_tile(colour="white", size = 4)+
  geom_text(aes(VislistA_twilight.aim2, VislistB_twilight.aim2,  label = paste(format(round(beetle.vs.flower, 2), nsmall = 2), sig.beetle.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid = element_blank(), 
                     panel.border = element_blank(), 
                     axis.ticks = element_blank() )+
   labs(fill = "p vaalue")
```

######Original model output
```{r}
sum.beetle.vs.flower_twilight.aim2
```


</br>
</br>

#Plot the contrasts {.tabset .tabset-fade .tabset-pills}
* Colours approximate human perception of either flower (left and right) or beetle (centre) colouration.
* Lines of the same colors connect the same sample

</br>

##aim 1 {.tabset .tabset-fade .tabset-pills}
###Daylight
```{r,fig.cap="Figure caption: Contrast comparison between visual systems with different photoreceptor combinations. A dot in each visual system shows a representative contrast of a flower pattern (beetle pattern in the middle panel), which is the average of its contrast to all leaves (all beetle patterns on the right panel). Colours of the dots reflect the visible colour of the flower (beetle patterns in the middle panel) with the lines of the same colour connecting the results between different visual systems. Black dots show the median of the representative contrast in a visual system. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1. Two contrasts > 10 JND are from flowers that have very low UV reflectance."}
#import the flower color code 
color.code<-read.csv("data/color code list.csv",header=TRUE) 

#creat a list of species name used in the spec data and 
name.list<-unique(dataset.transpose$species) %>% 
  sort() %>% #order it alphebatically as well
  data.frame() %>% dplyr::rename(species = ".")#make it a data frame and name the column "species"

#creat flower name list for aim 1
flower.colour.aim1 <- name.list %>% filter(str_detect(species, "flower")) %>% #select flower names
  cbind(color.code %>% filter(str_detect(type, "flower")) %>% arrange(name)) %>% #select flower color codes and order it alphebatically
  dplyr::select(-type) %>% #remove the redundant column
  mutate(count = 4) %>% uncount(count) #repeat each row for 4 times for 4 visual systems

#creat beetle name list for aim 1
beetle.colour.aim1 <- name.list %>% filter(str_detect(species, "beetle")) %>% #select flower names
  cbind(color.code %>% filter(str_detect(type, "beetle")) %>% arrange(name)) %>% #select flower color codes and order it alphebatically
  dplyr::select(-type) %>% #remove the redundant column
  mutate(count = 4) %>% uncount(count) #repeat each row for 4 times for 4 visual systems



#make flower vs leaf plot
##add the mean
mean.fl_d65.aim1<-allvis.fl_d65.aim1 %>% mutate(patch3 = paste(allvis.fl_d65.aim1$vissys,allvis.fl_d65.aim1$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.fl=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.fl_d65.aim1)[names(mean.fl_d65.aim1) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.fl_d65.aim1<-mean.fl_d65.aim1[order(mean.fl_d65.aim1$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.fl_d65.aim1$match.name<-flower.colour.aim1$species # this column is just for checking if match correctly
mean.fl_d65.aim1$colour<-flower.colour.aim1$colour


fl_d65.aim1<-ggplot(mean.fl_d65.aim1, aes(x=vissys, y=mean.dS.fl,group=flowerID))+
  geom_point(col=mean.fl_d65.aim1$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.fl_d65.aim1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.fl", "VS2.fl", "VS3.fl","VS4.fl"),
                   labels=c("USM", "UML", "USL","USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.fl_d65.aim1, aes(x= "VS1.fl", y= mean(VS1.fl_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_d65.aim1, aes(x= "VS2.fl", y= mean(VS2.fl_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_d65.aim1, aes(x= "VS3.fl", y= mean(VS3.fl_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_d65.aim1, aes(x= "VS4.fl", y= mean(VS4.fl_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Flower vs. Leaf")+
  annotate("text", x = c("VS1.fl", "VS2.fl", "VS3.fl","VS4.fl"), y = 15, label =c("a","a","b","c")) #add stitistical info



#make beetle vs leaf plot
##add the mean
mean.bl_d65.aim1<-allvis.bl_d65.aim1 %>% mutate(patch3 = paste(allvis.bl_d65.aim1$vissys,allvis.bl_d65.aim1$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.bl=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.bl_d65.aim1)[names(mean.bl_d65.aim1) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bl_d65.aim1<-mean.bl_d65.aim1[order(mean.bl_d65.aim1$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bl_d65.aim1$match.name<-beetle.colour.aim1$species # this column is just for checking if match correctly
mean.bl_d65.aim1$colour<-beetle.colour.aim1$colour


bl_d65.aim1<-ggplot(mean.bl_d65.aim1, aes(x=vissys, y=mean.dS.bl,group=beetleID))+
  geom_point(col=mean.bl_d65.aim1$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.bl_d65.aim1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.background = element_blank(), 
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.bl", "VS2.bl", "VS3.bl","VS4.bl"),
                   labels=c("USM", "UML", "USL","USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bl_d65.aim1, aes(x= "VS1.bl", y= mean(VS1.bl_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_d65.aim1, aes(x= "VS2.bl", y= mean(VS2.bl_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_d65.aim1, aes(x= "VS3.bl", y= mean(VS3.bl_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_d65.aim1, aes(x= "VS4.bl", y= mean(VS4.bl_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Beetle vs. Leaf")+annotate("text", x = c("VS1.bl", "VS2.bl", "VS3.bl","VS4.bl"), y = 15, label =c("a","bc","b","c")) #add stitistical info


#make beetle vs flower plot
##add the mean
mean.bf_d65.aim1<-allvis.bf_d65.aim1 %>% mutate(patch3 = paste(allvis.bf_d65.aim1$vissys,allvis.bf_d65.aim1$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.bf_d65.aim1)[names(mean.bf_d65.aim1) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf_d65.aim1<-mean.bf_d65.aim1[order(mean.bf_d65.aim1$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf_d65.aim1$match.name<-flower.colour.aim1$species # this column is just for checking if match correctly
mean.bf_d65.aim1$colour<-flower.colour.aim1$colour

bf_d65.aim1<-ggplot(mean.bf_d65.aim1, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf_d65.aim1$colour, size=3, alpha=0.7) + 
  geom_line(col=mean.bf_d65.aim1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA),#make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.bf", "VS2.bf", "VS3.bf","VS4.bf"),
                   labels=c("USM", "UML", "USL","USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf_d65.aim1, aes(x= "VS1.bf", y= mean(VS1.bf_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_d65.aim1, aes(x= "VS2.bf", y= mean(VS2.bf_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_d65.aim1, aes(x= "VS3.bf", y= mean(VS3.bf_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_d65.aim1, aes(x= "VS4.bf", y= mean(VS4.bf_d65.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("VS1.bf", "VS2.bf", "VS3.bf","VS4.bf"), y = 15, label =c("a","b","c","d")) #add stitistical info

#plot the contrasts from the 3 comparison groups together
figure_d65.aim1 <- ggarrange(fl_d65.aim1,bl_d65.aim1,bf_d65.aim1, ncol = 3, nrow = 1)
figure_d65.aim1
```

###Twilight
```{r,fig.cap="Figure caption: Contrast comparison between visual systems with different photoreceptor combinations. A dot in each visual system shows a representative contrast of a flower pattern (beetle pattern in the middle panel), which is the average of its contrast to all leaves (all beetle patterns on the right panel). Colours of the dots reflcet the visible colour of the flower (beetle patterns in the middle panel) with the lines of the same colour connecting the results between different visual systems. Black dots show the mean of the representative contrast in a visual system. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1. Two contrasts > 10 JND are from flowers that have very low UV reflectance."}
#make flower vs leaf plot
##add the mean
mean.fl_twilight.aim1<-allvis.fl_twilight.aim1 %>% mutate(patch3 = paste(allvis.fl_twilight.aim1$vissys,allvis.fl_twilight.aim1$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.fl=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.fl_twilight.aim1)[names(mean.fl_twilight.aim1) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.fl_twilight.aim1<-mean.fl_twilight.aim1[order(mean.fl_twilight.aim1$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.fl_twilight.aim1$match.name<-flower.colour.aim1$species # this column is just for checking if match correctly
mean.fl_twilight.aim1$colour<-flower.colour.aim1$colour


fl_twilight.aim1<-ggplot(mean.fl_twilight.aim1, aes(x=vissys, y=mean.dS.fl,group=flowerID))+
  geom_point(col=mean.fl_twilight.aim1$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.fl_twilight.aim1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,2)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.fl", "VS2.fl", "VS3.fl","VS4.fl"),
                   labels=c("USM", "UML", "USL","USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.fl_twilight.aim1, aes(x= "VS1.fl", y= mean(VS1.fl_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_twilight.aim1, aes(x= "VS2.fl", y= mean(VS2.fl_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_twilight.aim1, aes(x= "VS3.fl", y= mean(VS3.fl_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_twilight.aim1, aes(x= "VS4.fl", y= mean(VS4.fl_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Flower vs. Leaf")+
  annotate("text", x = c("VS1.fl", "VS2.fl", "VS3.fl","VS4.fl"), y = 3, label =c("a","b","c","d")) #add stitistical info


#make beetle vs leaf plot
##add the mean
mean.bl_twilight.aim1<-allvis.bl_twilight.aim1 %>% mutate(patch3 = paste(allvis.bl_twilight.aim1$vissys,allvis.bl_twilight.aim1$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.bl=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.bl_twilight.aim1)[names(mean.bl_twilight.aim1) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bl_twilight.aim1<-mean.bl_twilight.aim1[order(mean.bl_twilight.aim1$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bl_twilight.aim1$match.name<-beetle.colour.aim1$species # this column is just for checking if match correctly
mean.bl_twilight.aim1$colour<-beetle.colour.aim1$colour


bl_twilight.aim1<-ggplot(mean.bl_twilight.aim1, aes(x=vissys, y=mean.dS.bl,group=beetleID))+
  geom_point(col=mean.bl_twilight.aim1$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.bl_twilight.aim1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,2)+
  theme(panel.background = element_blank(), 
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.bl", "VS2.bl", "VS3.bl","VS4.bl"),
                   labels=c("USM", "UML", "USL","USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bl_twilight.aim1, aes(x= "VS1.bl", y= mean(VS1.bl_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_twilight.aim1, aes(x= "VS2.bl", y= mean(VS2.bl_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_twilight.aim1, aes(x= "VS3.bl", y= mean(VS3.bl_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_twilight.aim1, aes(x= "VS4.bl", y= mean(VS4.bl_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Beetle vs. Leaf")+
  annotate("text", x = c("VS1.bl", "VS2.bl", "VS3.bl","VS4.bl"), y = 3, label =c("a","b","b","c")) #add stitistical info



#make beetle vs flower plot
##add the mean
mean.bf_twilight.aim1<-allvis.bf_twilight.aim1 %>% mutate(patch3 = paste(allvis.bf_twilight.aim1$vissys,allvis.bf_twilight.aim1$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.bf_twilight.aim1)[names(mean.bf_twilight.aim1) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf_twilight.aim1<-mean.bf_twilight.aim1[order(mean.bf_twilight.aim1$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf_twilight.aim1$match.name<-flower.colour.aim1$species # this column is just for checking if match correctly
mean.bf_twilight.aim1$colour<-flower.colour.aim1$colour

bf_twilight.aim1<-ggplot(mean.bf_twilight.aim1, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf_twilight.aim1$colour, size=3, alpha=0.7) + 
  geom_line(col=mean.bf_twilight.aim1$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,2)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA),#make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle=90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.bf", "VS2.bf", "VS3.bf","VS4.bf"),
                   labels=c("USM", "UML", "USL","USML"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf_twilight.aim1, aes(x= "VS1.bf", y= mean(VS1.bf_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_twilight.aim1, aes(x= "VS2.bf", y= mean(VS2.bf_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_twilight.aim1, aes(x= "VS3.bf", y= mean(VS3.bf_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_twilight.aim1, aes(x= "VS4.bf", y= mean(VS4.bf_twilight.aim1$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("VS1.bf", "VS2.bf", "VS3.bf","VS4.bf"), y = 3, label =c("a","b","c","d")) #add stitistical info



#plot the contrasts from the 3 comparison groups together
figure_twilight.aim1 <- ggarrange(fl_twilight.aim1,bl_twilight.aim1,bf_twilight.aim1, ncol = 3, nrow = 1)
figure_twilight.aim1
```


##Aim 2 {.tabset .tabset-fade .tabset-pills}
###Daylight
```{r,fig.cap="Figure caption: Contrast comparison between visual systems with the LWS photoreceptor peaking at different wavelengths. A dot in each visual system shows a representative contrast of a flower pattern (beetle pattern in the middle panel), which is the average of its contrast to all leaves (all beetle patterns on the right panel). Colours of the dots reflect the visible colour of the flower (beetle patterns in the middle panel) with the lines of the same colour connecting the results between different visual systems. Black dots show the mean of the representative contrast in a visual system. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1. Two contrasts > 10 JND are from flowers that have very low UV reflectance."}
#creat flower name list for Aim 2
flower.colour.aim2 <- name.list %>% filter(str_detect(species, "flower")) %>% #select flower names
  cbind(color.code %>% filter(str_detect(type, "flower")) %>% arrange(name)) %>% #select flower color codes and order it alphebatically
  dplyr::select(-type) %>% #remove the redundant column
  mutate(count = 5) %>% uncount(count) #repeat each row for 5 times for 5 visual systems

#creat beetle name list for Aim 2
beetle.colour.aim2 <- name.list %>% filter(str_detect(species, "beetle")) %>% #select flower names
  cbind(color.code %>% filter(str_detect(type, "beetle")) %>% arrange(name)) %>% #select flower color codes and order it alphebatically
  dplyr::select(-type) %>% #remove the redundant column
  mutate(count = 5) %>% uncount(count) #repeat each row for 5 times for 5 visual systems


#make flower vs leaf plot
##add the mean
mean.fl_d65.aim2<-allvis.fl_d65.aim2 %>% mutate(patch3 = paste(allvis.fl_d65.aim2$vissys,allvis.fl_d65.aim2$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.fl=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.fl_d65.aim2)[names(mean.fl_d65.aim2) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.fl_d65.aim2<-mean.fl_d65.aim2[order(mean.fl_d65.aim2$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.fl_d65.aim2$match.name<-flower.colour.aim2$species # this column is just for checking if match correctly
mean.fl_d65.aim2$colour<-flower.colour.aim2$colour

fl_d65.aim2<-ggplot(mean.fl_d65.aim2, aes(x=vissys, y=mean.dS.fl,group=flowerID))+
  geom_point(col=mean.fl_d65.aim2$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.fl_d65.aim2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.fl", "VS2.fl", "VS3.fl","VS4.fl","VS5.fl"),
                   labels=c("VS 580", "VS 600","VS 620","VS 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.fl_d65.aim2, aes(x= "VS1.fl", y= mean(VS1.fl_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_d65.aim2, aes(x= "VS2.fl", y= mean(VS2.fl_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_d65.aim2, aes(x= "VS3.fl", y= mean(VS3.fl_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_d65.aim2, aes(x= "VS4.fl", y= mean(VS4.fl_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_d65.aim2, aes(x= "VS5.fl", y= mean(VS5.fl_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Flower vs. Leaf")+
  annotate("text", x = c("VS1.fl", "VS2.fl", "VS3.fl","VS4.fl","VS5.fl"), y = 15, label =c("a","b","c","d","d")) #add stitistical info


#make beetle vs leaf plot
##add the mean
mean.bl_d65.aim2<-allvis.bl_d65.aim2 %>% mutate(patch3 = paste(allvis.bl_d65.aim2$vissys,allvis.bl_d65.aim2$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.bl=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.bl_d65.aim2)[names(mean.bl_d65.aim2) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bl_d65.aim2<-mean.bl_d65.aim2[order(mean.bl_d65.aim2$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bl_d65.aim2$match.name<-beetle.colour.aim2$species # this column is just for checking if match correctly
mean.bl_d65.aim2$colour<-beetle.colour.aim2$colour


bl_d65.aim2<-ggplot(mean.bl_d65.aim2, aes(x=vissys, y=mean.dS.bl,group=beetleID))+
  geom_point(col=mean.bl_d65.aim2$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.bl_d65.aim2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.background = element_blank(),
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.bl", "VS2.bl", "VS3.bl","VS4.bl","VS5.bl"),
                   labels=c("VS 580", "VS 600","VS 620","VS 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bl_d65.aim2, aes(x= "VS1.bl", y= mean(VS1.bl_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_d65.aim2, aes(x= "VS2.bl", y= mean(VS2.bl_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_d65.aim2, aes(x= "VS3.bl", y= mean(VS3.bl_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_d65.aim2, aes(x= "VS4.bl", y= mean(VS4.bl_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_d65.aim2, aes(x= "VS5.bl", y= mean(VS5.bl_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Beetle vs. Leaf")+
  annotate("text", x = c("VS1.bl", "VS2.bl", "VS3.bl","VS4.bl","VS5.bl"), y = 15, label =c("a","b","c","d","e")) #add stitistical info


#make beetle vs flower plot
##add the mean
mean.bf_d65.aim2<-allvis.bf_d65.aim2 %>% mutate(patch3 = paste(allvis.bf_d65.aim2$vissys,allvis.bf_d65.aim2$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore


##plot the mean dS
names(mean.bf_d65.aim2)[names(mean.bf_d65.aim2) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf_d65.aim2<-mean.bf_d65.aim2[order(mean.bf_d65.aim2$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf_d65.aim2$match.name<-flower.colour.aim2$species # this column is just for checking if match correctly
mean.bf_d65.aim2$colour<-flower.colour.aim2$colour

bf_d65.aim2<-ggplot(mean.bf_d65.aim2, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf_d65.aim2$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.bf_d65.aim2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.bf", "VS2.bf", "VS3.bf","VS4.bf","VS5.bf"),
                   labels=c("VS 580", "VS 600","VS 620","VS 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf_d65.aim2, aes(x= "VS1.bf", y= mean(VS1.bf_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_d65.aim2, aes(x= "VS2.bf", y= mean(VS2.bf_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_d65.aim2, aes(x= "VS3.bf", y= mean(VS3.bf_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_d65.aim2, aes(x= "VS4.bf", y= mean(VS4.bf_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_d65.aim2, aes(x= "VS5.bf", y= mean(VS5.bf_d65.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("VS1.bf", "VS2.bf", "VS3.bf","VS4.bf","VS5.bf"), y = 15, label =c("a","b","c","d","e")) #add stitistical info

figure_d65.aim2 <- ggarrange(fl_d65.aim2,bl_d65.aim2,bf_d65.aim2, ncol = 3, nrow = 1)
figure_d65.aim2
```

###Twilight
```{r,fig.cap="Figure caption: Contrast comparison between visual systems with the LWS photoreceptor peaking at different wavelengths. A dot in each visual system shows a representative contrast of a flower pattern (beetle pattern in the middle panel), which is the average of its contrast to all leaves (all beetle patterns on the right panel). Colours of the dots reflect the visible colour of the flower (beetle patterns in the middle panel) with the lines of the same colour connecting the results between different visual systems. Black dots show the mean of the representative contrast in a visual system. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1. Two contrasts > 10 JND are from flowers that have very low UV reflectance."}
#make flower vs leaf plot
##add the mean
mean.fl_twilight.aim2<-allvis.fl_twilight.aim2 %>% mutate(patch3 = paste(allvis.fl_twilight.aim2$vissys,allvis.fl_twilight.aim2$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.fl=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.fl_twilight.aim2)[names(mean.fl_twilight.aim2) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.fl_twilight.aim2<-mean.fl_twilight.aim2[order(mean.fl_twilight.aim2$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.fl_twilight.aim2$match.name<-flower.colour.aim2$species # this column is just for checking if match correctly
mean.fl_twilight.aim2$colour<-flower.colour.aim2$colour

fl_twilight.aim2<-ggplot(mean.fl_twilight.aim2, aes(x=vissys, y=mean.dS.fl,group=flowerID))+
  geom_point(col=mean.fl_twilight.aim2$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.fl_twilight.aim2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,2)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.fl", "VS2.fl", "VS3.fl","VS4.fl","VS5.fl"),
                   labels=c("VS 580", "VS 600","VS 620","VS 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.fl_twilight.aim2, aes(x= "VS1.fl", y= mean(VS1.fl_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_twilight.aim2, aes(x= "VS2.fl", y= mean(VS2.fl_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_twilight.aim2, aes(x= "VS3.fl", y= mean(VS3.fl_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_twilight.aim2, aes(x= "VS4.fl", y= mean(VS4.fl_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.fl_twilight.aim2, aes(x= "VS5.fl", y= mean(VS5.fl_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Flower vs. Leaf")+
  annotate("text", x = c("VS1.fl", "VS2.fl", "VS3.fl","VS4.fl","VS5.fl"), y = 3, label =c("a","b","c","d","e")) #add stitistical info


#make beetle vs leaf plot
##add the mean
mean.bl_twilight.aim2<-allvis.bl_twilight.aim2 %>% mutate(patch3 = paste(allvis.bl_twilight.aim2$vissys,allvis.bl_twilight.aim2$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.bl=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.bl_twilight.aim2)[names(mean.bl_twilight.aim2) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bl_twilight.aim2<-mean.bl_twilight.aim2[order(mean.bl_twilight.aim2$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bl_twilight.aim2$match.name<-beetle.colour.aim2$species # this column is just for checking if match correctly
mean.bl_twilight.aim2$colour<-beetle.colour.aim2$colour


bl_twilight.aim2<-ggplot(mean.bl_twilight.aim2, aes(x=vissys, y=mean.dS.bl,group=beetleID))+
  geom_point(col=mean.bl_twilight.aim2$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.bl_twilight.aim2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,2)+
  theme(panel.background = element_blank(),
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.bl", "VS2.bl", "VS3.bl","VS4.bl","VS5.bl"),
                   labels=c("VS 580", "VS 600","VS 620","VS 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bl_twilight.aim2, aes(x= "VS1.bl", y= mean(VS1.bl_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_twilight.aim2, aes(x= "VS2.bl", y= mean(VS2.bl_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_twilight.aim2, aes(x= "VS3.bl", y= mean(VS3.bl_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_twilight.aim2, aes(x= "VS4.bl", y= mean(VS4.bl_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bl_twilight.aim2, aes(x= "VS5.bl", y= mean(VS5.bl_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Beetle vs. Leaf")+
  annotate("text", x = c("VS1.bl", "VS2.bl", "VS3.bl","VS4.bl","VS5.bl"), y = 3, label =c("a","b","c","d","d")) #add stitistical info


#make beetle vs flower plot
##add the mean
mean.bf_twilight.aim2<-allvis.bf_twilight.aim2 %>% mutate(patch3 = paste(allvis.bf_twilight.aim2$vissys,allvis.bf_twilight.aim2$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore


##plot the mean dS
names(mean.bf_twilight.aim2)[names(mean.bf_twilight.aim2) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf_twilight.aim2<-mean.bf_twilight.aim2[order(mean.bf_twilight.aim2$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf_twilight.aim2$match.name<-flower.colour.aim2$species # this column is just for checking if match correctly
mean.bf_twilight.aim2$colour<-flower.colour.aim2$colour

bf_twilight.aim2<-ggplot(mean.bf_twilight.aim2, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf_twilight.aim2$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.bf_twilight.aim2$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,2)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("VS1.bf", "VS2.bf", "VS3.bf","VS4.bf","VS5.bf"),
                   labels=c("VS 580", "VS 600","VS 620","VS 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf_twilight.aim2, aes(x= "VS1.bf", y= mean(VS1.bf_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_twilight.aim2, aes(x= "VS2.bf", y= mean(VS2.bf_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_twilight.aim2, aes(x= "VS3.bf", y= mean(VS3.bf_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_twilight.aim2, aes(x= "VS4.bf", y= mean(VS4.bf_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  geom_point(data = mean.bf_twilight.aim2, aes(x= "VS5.bf", y= mean(VS5.bf_twilight.aim2$dS)), 
             col="black", size=3)+ #add the mean point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("VS1.bf", "VS2.bf", "VS3.bf","VS4.bf","VS5.bf"), y = 3, label =c("a","b","c","d","e")) #add stitistical info

figure_twilight.aim2 <- ggarrange(fl_twilight.aim2,bl_twilight.aim2,bf_twilight.aim2, ncol = 3, nrow = 1)
figure_twilight.aim2
```

#Summary

* Visual models using hypothetical insect visual systems indicate that having both SWS and LWS receptors enhances the contrast of beetles with flowers and flowers with leaves, and a LWS receptor enhances the contrast of beetles against leaves.
</br>
</br>
* The USL visual system (UVS, SWS and LWS) consistently provides the highest contrast compared to the other three visual systems, whereas the USM visual system (UVS, SWS and MWS) consistently provides the lowest or equal lowest contrast.
</br>
</br>
* The optimal peak sensitivity of the LWS photoreceptor depends on what is being viewed. When comparing beetle colours with both leaves and flowers, contrast increases with increasing LWS max; whereas when comparing flowers against leaves, contrast is maximized with a LWS photoreceptor peak sensitivity of 640 nm.
</br>
</br>
* The contrasts of the models using civil twilight were substantially lower (often < 1 JND) than those using daylight. The contrasts in twilight showed different patterns from those using daylight in Aim 1 models, but were qualitatively similar in Aim 2 models.