---
title: "Opsin-shifted LWS photoreceptors: Visual models using opsin-shifted LWS receptors instead of filter-shifted LWS receptors in Main models"
output:
  pdf_document: default
  html_document:
    theme: flatly
    toc: true
    toc_depth: 2
subtitle: Supplementary Information
Date: January 08 2021
---

# The aim
  
* We tested how the LWS photoreceptors generated (opsin-shifted vs. filter-shifted) using different methods affect the contrasts. 

* In the following sections, we ran the same models as in the [Main models](main_models.html) but using the opsin-shifted LWS receptors for comparison.

* The model parameters and the statistical methods remain the same as described in the [Main models](main_models.html).
</br>
</br>

```{r, warning=FALSE, message=FALSE, results='hide'}
#Load R libraries 
library(pavo)
library(dplyr)
library(stringr)
library(tidyr) #for gather() function
library(ggplot2)
library(lme4)
library(car)
library(multcomp)
library(boot) #for mean() function
library(pander) #for creating tidy tables
library(ggpubr) #for ggarrange() function
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE) # Suppress warnings in the HTML output
knitr::opts_chunk$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
```


</br>
</br>

# Data description
* We used the same spectral data and illumination as the [Main models](main_models.html).

</br>

## Sensitivity curves
* ALL photoreceptor sensitivities (UVS, SWS, MWS, LWS) were generated from the Govardovskii template without apply filters.

* Note: UVS, SWS, MWS photoreceptors were the same as those in the main models

```{r import data,message=FALSE}
#import sensitivity curves
specsensbuprest.aim1 <- read.csv("data/peak sensitivity_opsin shift_aim1.csv",header = TRUE) %>%
  as.rspec()
specsensbuprest.aim2 <- read.csv("data/peak sensitivity_opsin shift_aim2.csv",header = TRUE) %>%
  as.rspec()


# import irradiance
irradiance.d65 <- read.csv("data/d65.csv", header = TRUE) %>% 
  as.rspec(lim = c(300,800)) %>%  #set import range
  procspec(opt = c("min", "max")) #standardize the illumination spectrum
irradiance.twilight <- read.csv("data/civil twilight.csv", header = TRUE) %>% 
  as.rspec(lim = c(300,800)) %>% 
  rename( twilight = Irradiance) %>% 
  irrad2flux() #convert the irradiance (μ Watt.cm^{-2}) to photon flux (μ mol.s^{-1}.m^{-2}) to derive correct quantum catch.

#import background - average leaf
aveleaf <- read.csv("data/aveleaf.csv",header=TRUE) %>% 
  as.rspec()

#import and combine beetle, flower, leaf together
raw.dataset <- read.csv("data/refelectance spectra.csv",header=TRUE) %>% 
  as.rspec()
dataset <- aggspec(raw.dataset, by = 3, FUN = mean) %>%  #average three measurements to a representative one
  procspec(opt = "smooth", span = 0.1, fixneg = "zero") #smooth the spectra and lift <0 to 0
```

```{r, fig.cap="Figure caption: Sensitivity curves of the photoreceptors with different peak wavelengths."}
wl <- specsensbuprest.aim2[,1]
peaks <- gather(specsensbuprest.aim2[,2:9], peak, value) %>% 
  cbind(wl)

#order the peaks in the legend
wl <- specsensbuprest.aim2[,1]
peaks<-gather(specsensbuprest.aim2[,2:9], peak, value) %>% cbind(wl)

peak.order <- c("UVS.355.A1.", "SWS.445.A1.", "MWS.530.A1.", "LWS.580.A1.", "LWS.600.A1.", "LWS.620.A1.", "LWS.640.A1.", "LWS.660.A1.") #to order the peaks in the legend

ggplot(peaks,
       aes(x = wl, y = value, col = peak))+
  geom_line()+
  guides(color = guide_legend(title = "peak sensitivity"))+
  scale_color_manual(
    values = c("darkorchid4", "dodgerblue3", "olivedrab4", "orange1", "orange3","darkorange3", "orangered1", "red2"),
    labels = c("355 nm", "445 nm","530 nm", "580 nm", "600 nm", "620 nm", "640 nm", "660 nm"),
    breaks = peak.order)+
  xlab("Wavelength (nm)")+ 
  ylab("Relative spectral sensitivity")+
  theme_classic()
```

</br>
</br>

# Run the visual models
* We ran the visual models with the same parameter settings and steps as in the [Main models](main_models.html).

* We first calculated the quantum catches, then calculated the contrasts.

```{r Set up functions for quantum catch calculation, message=FALSE}
## D65
get.d65.vismodel <- function(i){
  
  vs.i <- vismodel(dataset[1:501,], 
                   visual = i, #this need to change according to the visual system
                   bkg = aveleaf$aveleaf, 
                   illum = irradiance.d65[1:501,2], 
                   qcatch = 'fi', 
                   relative = FALSE,
                   vonkries = TRUE)
  return(vs.i)
}



## Twilight
get.twilight.vismodel <- function(i){
  
  vs.i <- vismodel(dataset[1:501,], 
                   visual = i, 
                   bkg = aveleaf$aveleaf, 
                   illum = irradiance.twilight[1:501,2], 
                   qcatch = 'fi', 
                   relative = FALSE, 
                   vonkries = TRUE)
  return(vs.i)
}
```

```{r Quantum catch calculation, message=FALSE}
# set up sensitivity list for Aim 1 and Aim 2
sens.list <- list(USM <- specsensbuprest.aim1[, 1:4],
                  UML <- specsensbuprest.aim1[, c(1,2,4,5)],
                  USL <- specsensbuprest.aim1[, c(1,2,3,5)],
                  USML <- specsensbuprest.aim1[, 1:5],
                  VS580 <- specsensbuprest.aim2[, 1:5],
                  VS600 <- specsensbuprest.aim2[, c(1,2,3,4,6)],
                  VS620 <- specsensbuprest.aim2[, c(1,2,3,4,7)],
                  VS640 <- specsensbuprest.aim2[, c(1,2,3,4,8)],
                  VS660 <- specsensbuprest.aim2[, c(1,2,3,4,9)])

# Quantum catch - D65 - Aim 1 & Aim 2
## set up list for holding output
d65.vismodel.output <- list(USM = NA, UML = NA, USL = NA, USML = NA,
                            VS580 = NA, VS600 = NA, VS620 = NA, VS640 = NA, VS660 = NA)
twilight.vismodel.output <- d65.vismodel.output # replicate a same empty list for twilight

## Run the loop
for (i in 1:length(sens.list)){
  
  vs.result.d65 <- get.d65.vismodel(sens.list[[i]]) # for D65
  d65.vismodel.output[[i]] <- vs.result.d65
  
  vs.result.twilight <- get.twilight.vismodel(sens.list[[i]]) # for twilight
  twilight.vismodel.output[[i]] <- vs.result.twilight

}

## D65 Aim 1 & Aim 2 vismodel output
vsUSM <- d65.vismodel.output$USM
vsUML <- d65.vismodel.output$UML
vsUSL <- d65.vismodel.output$USL
vsUSML <- d65.vismodel.output$USML
buprest580 <- d65.vismodel.output$VS580
buprest600 <- d65.vismodel.output$VS600
buprest620 <- d65.vismodel.output$VS620
buprest640 <- d65.vismodel.output$VS640
buprest660 <- d65.vismodel.output$VS660

## Twilight Aim 1 & Aim 2 vismodel output
vsUSM_twilight <- twilight.vismodel.output$USM
vsUML_twilight <- twilight.vismodel.output$UML
vsUSL_twilight <- twilight.vismodel.output$USL
vsUSML_twilight <- twilight.vismodel.output$USML
buprest580_twilight <- twilight.vismodel.output$VS580
buprest600_twilight <- twilight.vismodel.output$VS600
buprest620_twilight <- twilight.vismodel.output$VS620
buprest640_twilight <- twilight.vismodel.output$VS640
buprest660_twilight <- twilight.vismodel.output$VS660
```

```{r Contrast calculation, message=FALSE}
# set up common list before running loop for calculating contrast
## receptor density
aim1.recep.density.list <- list(USM <- c(1.6027, 1.4059, 1.7714),
                                UML <- c(1.4416, 1.5933, 1.7451),
                                USL <- c(1.5481, 1.3580, 1.8740),
                                USML <- c(1.14, 1, 1.26, 1.38))

## Weber fraction
aim1.web.list <- c(0.1059, 0.1067, 0.1030, 0.12)
aim1.web.ref <- c(3, 3, 3, 4)

# Contrast calculation- D65 - aim 1
## create model data list
aim1.d65.vismodel.list <- list(vsUSM, vsUML, vsUSL, vsUSML)
## combine list before running the loop
aim1.d65.comb.list <- list(vis.list = aim1.d65.vismodel.list,
                           recp.dens.list = aim1.recep.density.list,
                           web.list = aim1.web.list,
                           web.ref = aim1.web.ref)

# list for holding output
aim1.d65.contrast.output <- list(USM = NA, UML = NA, USL = NA, USML = NA)

for (i in 1:length(aim1.d65.comb.list)) {
 
  coldist.result <- coldist(modeldata = aim1.d65.comb.list$vis.list[[i]], # change input model data
                            noise = "neural",
                            achro = FALSE, 
                            n = aim1.d65.comb.list$recp.dens.list[[i]] , # change receptor density
                            weber = aim1.d65.comb.list$web.list[[i]], # change weber's fraction
                            weber.ref = aim1.d65.comb.list$web.ref[[i]] )
  
  aim1.d65.contrast.output[[i]] <- coldist.result
}

CvsUSM <- aim1.d65.contrast.output$USM
CvsUML <- aim1.d65.contrast.output$UML
CvsUSL <- aim1.d65.contrast.output$USL
CvsUSML <- aim1.d65.contrast.output$USML


#Contrast calculation- D65 - Aim 2
get.aim2.d65.coldist <- function(i){
  
  con <- coldist(modeldata = i, # put output of vismodel()
                   noise = "neural", 
                   achro = FALSE, 
                   n = c(1.14, 1, 1.26, 1.38),
                   weber = 0.12,
                   weber.ref = 4)
  
  return(con)
}

aim2.d65.contrast.output <- list(VS580 = NA, VS600 = NA, VS620 = NA, VS640 = NA, VS660 = NA)
aim2.d65.vismodel.list <- list(buprest580, 
                               buprest600, 
                               buprest620, 
                               buprest640, 
                               buprest660)

for (i in 1:length(aim2.d65.vismodel.list)) {
  
  contrast.result.i <- get.aim2.d65.coldist(aim2.d65.vismodel.list[[i]])
  aim2.d65.contrast.output[[i]] <- contrast.result.i
}

Cbuprest580 <- aim2.d65.contrast.output$VS580
Cbuprest600 <- aim2.d65.contrast.output$VS600
Cbuprest620 <- aim2.d65.contrast.output$VS620
Cbuprest640 <- aim2.d65.contrast.output$VS640
Cbuprest660 <- aim2.d65.contrast.output$VS660


#Contrast calculation- twilight - aim 1
aim1.twilight.vismodel.list <- list(vsUSM_twilight, 
                                    vsUML_twilight, 
                                    vsUSL_twilight,
                                    vsUSML_twilight)
# Here have to create one comb.list is becasue vis.model input is different from D65
aim1.twilight.comb.list <- list(vis.list = aim1.twilight.vismodel.list,
                                recp.dens.list = aim1.recep.density.list,
                                web.list = aim1.web.list,
                                web.ref = aim1.web.ref)

# list for holding output
aim1.twilight.contrast.output <- list(USM = NA, UML = NA, USL = NA, USML = NA)

for (i in 1:length(aim1.twilight.comb.list)) {
 
  coldist.result <- coldist(modeldata = aim1.twilight.comb.list$vis.list[[i]], # change input model data
                            noise = "quantum", 
                            achro = FALSE, 
                            n = aim1.twilight.comb.list$recp.dens.list[[i]] , # change receptor density ratio 
                            weber = aim1.twilight.comb.list$web.list[[i]], # change weber's fraction
                            weber.ref = aim1.twilight.comb.list$web.ref[[i]])
  
  aim1.twilight.contrast.output[[i]] <- coldist.result
}

CvsUSM_twilight <- aim1.twilight.contrast.output$USM
CvsUML_twilight <- aim1.twilight.contrast.output$UML
CvsUSL_twilight <- aim1.twilight.contrast.output$USL
CvsUSML_twilight <- aim1.twilight.contrast.output$USML



#Contrast calculation- twilight - Aim 2
get.aim2.twilight.coldist <- function(i){
  
  con <- coldist(modeldata = i,  
                   noise="quantum", 
                   achro=FALSE, 
                   n = c(1.14,1,1.26,1.38), 
                   weber = 0.12, 
                   weber.ref = 4)
  
  return(con)
}

aim2.twilight.contrast.output <- list(VS580 = NA, VS600 = NA, VS620 = NA, VS640 = NA, VS660 = NA)
aim2.twilight.vismodel.list <- list(buprest580_twilight, 
                                    buprest600_twilight, 
                                    buprest620_twilight, 
                                    buprest640_twilight,
                                    buprest660_twilight)

for (i in 1:length(aim2.twilight.vismodel.list)) {
  
  contrast.result.i <- get.aim2.twilight.coldist(aim2.twilight.vismodel.list[[i]])
  aim2.twilight.contrast.output[[i]] <- contrast.result.i
}

Cbuprest580_twilight <- aim2.twilight.contrast.output$VS580
Cbuprest600_twilight <- aim2.twilight.contrast.output$VS600
Cbuprest620_twilight <- aim2.twilight.contrast.output$VS620
Cbuprest640_twilight <- aim2.twilight.contrast.output$VS640
Cbuprest660_twilight <- aim2.twilight.contrast.output$VS660
```

```{r Combine all contrast value in each comparison group}
# Get a column for visual system names 
## Create list required in the loops
aim1.fl.vissys <- list("UVSWMW...fl",
                       "UV..MWLW.fl", 
                       "UVSW..LW.fl",
                       "UVSWMWLW.fl")
aim1.bl.vissys <- list("UVSWMW...bl",
                       "UV..MWLW.bl", 
                       "UVSW..LW.bl",
                       "UVSWMWLW.bl")
aim1.bf.vissys <- list("UVSWMW...bf",
                       "UV..MWLW.bf",
                       "UVSW..LW.bf",
                       "UVSWMWLW.bf")
aim2.fl.vissys <- list("VS580.fl", "VS600.fl", "VS620.fl", "VS640.fl", "VS660.fl") 
aim2.bl.vissys <- list("VS580.bl", "VS600.bl", "VS620.bl", "VS640.bl", "VS660.bl")
aim2.bf.vissys <- list("VS580.bf", "VS600.bf", "VS620.bf", "VS640.bf", "VS660.bf") 

## Daylight - aim 1
aim1.vissys_d65 <- list(CvsUSM, CvsUML, CvsUSL, CvsUSML)

### flower vs leaf

allvis.fl_d65.aim1 <- data_frame()
for (i in 1:length(aim1.vissys_d65)) {
  
  temp.i <- aim1.vissys_d65[[i]] %>% 
    filter(str_detect(patch1,"flower")) %>% 
    filter(str_detect(patch2,"leaves")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim1.fl.vissys[[i]],1)
  
  allvis.fl_d65.aim1 <- temp.i %>% rbind(allvis.fl_d65.aim1)  
}

### beetle vs leaf
allvis.bl_d65.aim1 <- data_frame()
for (i in 1:length(aim1.vissys_d65)) {
  
  temp.i <- aim1.vissys_d65[[i]] %>% 
    filter(str_detect(patch2,"beetle")) %>% 
    # Note: for beelte vs. leaf, have to filter from patch 2 then pactch 1
    filter(str_detect(patch1,"leaves")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim1.bl.vissys[[i]],1)
  
  allvis.bl_d65.aim1 <- temp.i %>% rbind(allvis.bl_d65.aim1)  
}

### beetle vs flower
allvis.bf_d65.aim1 <- data_frame()
for (i in 1:length(aim1.vissys_d65)) {
  
  temp.i <- aim1.vissys_d65[[i]] %>% 
    filter(str_detect(patch1,"flower")) %>% 
    filter(str_detect(patch2,"beetle")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim1.bf.vissys[[i]],1)
  
  allvis.bf_d65.aim1 <- temp.i %>% rbind(allvis.bf_d65.aim1)  
}




## Twilight - aim 1
aim1.vissys_twilight <- list(CvsUSM_twilight, CvsUML_twilight, CvsUSL_twilight, CvsUSML_twilight)

### flower vs leaf
allvis.fl_twilight.aim1 <- data_frame()
for (i in 1:length(aim1.vissys_twilight)) {
  
  temp.i <- aim1.vissys_twilight[[i]] %>% 
    filter(str_detect(patch1,"flower")) %>% 
    filter(str_detect(patch2,"leaves")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim1.fl.vissys[[i]],1)
  
  allvis.fl_twilight.aim1 <- temp.i %>% rbind(allvis.fl_twilight.aim1)  
}

### beetle vs leaf
allvis.bl_twilight.aim1 <- data_frame()
for (i in 1:length(aim1.vissys_twilight)) {
  
  temp.i <- aim1.vissys_twilight[[i]] %>% 
    filter(str_detect(patch2,"beetle")) %>% 
    filter(str_detect(patch1,"leaves")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim1.bl.vissys[[i]],1)
  
  allvis.bl_twilight.aim1 <- temp.i %>% rbind(allvis.bl_twilight.aim1)  
}

### beetle vs flower
allvis.bf_twilight.aim1 <- data_frame()
for (i in 1:length(aim1.vissys_twilight)) {
  
  temp.i <- aim1.vissys_twilight[[i]] %>% 
    filter(str_detect(patch1,"flower")) %>% 
    filter(str_detect(patch2,"beetle")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim1.bf.vissys[[i]],1)
  
  allvis.bf_twilight.aim1 <- temp.i %>% rbind(allvis.bf_twilight.aim1)  
}


## Daylight - aim 2
aim2.vissys_d65 <- list(Cbuprest580, Cbuprest600, Cbuprest620, Cbuprest640, Cbuprest660)

### flower vs leaf
allvis.fl_d65.aim2 <- data_frame()
for (i in 1:length(aim2.vissys_d65)) {
  
  temp.i <- aim2.vissys_d65[[i]] %>% 
    filter(str_detect(patch1,"flower")) %>% 
    filter(str_detect(patch2,"leaves")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim2.fl.vissys[[i]],1)
  
  allvis.fl_d65.aim2 <- temp.i %>% rbind(allvis.fl_d65.aim2)  
}

### beetle vs leaf
allvis.bl_d65.aim2 <- data_frame()
for (i in 1:length(aim2.vissys_d65)) {
  
  temp.i <- aim2.vissys_d65[[i]] %>% 
    filter(str_detect(patch2,"beetle")) %>% 
    filter(str_detect(patch1,"leaves")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim2.bl.vissys[[i]],1)
  
  allvis.bl_d65.aim2 <- temp.i %>% rbind(allvis.bl_d65.aim2)  
}

### beetle vs flower
allvis.bf_d65.aim2 <- data_frame()
for (i in 1:length(aim2.vissys_d65)) {
  
  temp.i <- aim2.vissys_d65[[i]] %>% 
    filter(str_detect(patch1,"flower")) %>% 
    filter(str_detect(patch2,"beetle")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim2.bf.vissys[[i]],1)
  
  allvis.bf_d65.aim2 <- temp.i %>% rbind(allvis.bf_d65.aim2)  
}


##Twilight - aim 2
aim2.vissys_twilight <- list(Cbuprest580_twilight, Cbuprest600_twilight, Cbuprest620_twilight, Cbuprest640_twilight, Cbuprest660_twilight)

### flower vs leaf
allvis.fl_twilight.aim2 <- data_frame()
for (i in 1:length(aim2.vissys_twilight)) {
  
  temp.i <- aim2.vissys_twilight[[i]] %>% 
    filter(str_detect(patch1,"flower")) %>% 
    filter(str_detect(patch2,"leaves")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim2.fl.vissys[[i]],1)
  
  allvis.fl_twilight.aim2 <- temp.i %>% rbind(allvis.fl_twilight.aim2)  
}

### beetle vs leaf
allvis.bl_twilight.aim2 <- data_frame()
for (i in 1:length(aim2.vissys_twilight)) {
  
  temp.i <- aim2.vissys_twilight[[i]] %>% 
    filter(str_detect(patch2,"beetle")) %>% 
    filter(str_detect(patch1,"leaves")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim2.bl.vissys[[i]],1)
  
  allvis.bl_twilight.aim2 <- temp.i %>% rbind(allvis.bl_twilight.aim2)  
}

### beetle vs flower
allvis.bf_twilight.aim2 <- data_frame()
for (i in 1:length(aim2.vissys_twilight)) {
  
  temp.i <- aim2.vissys_twilight[[i]] %>% 
    filter(str_detect(patch1,"flower")) %>% 
    filter(str_detect(patch2,"beetle")) %>% 
    dplyr::select(1:3)
  
  temp.i$vissys <- strrep(aim2.bf.vissys[[i]],1)
  
  allvis.bf_twilight.aim2 <- temp.i %>% rbind(allvis.bf_twilight.aim2)  
}
```

</br>

## Contrast tables{.tabset .tabset-fade .tabset-pills}

</br>

### Aim 1 {.tabset .tabset-fade .tabset-pills}
The table shows the mean contrast in each comparison group

#### Daylight
```{r}
# Combine comparison groups together in a table
## create a input list for the loop
allvis.aim1_d65.list <- list(allvis.fl_d65.aim1, allvis.bl_d65.aim1, allvis.bf_d65.aim1)

## create a data frame to hold the loop output
contrast.list_d65.aim1 <- data_frame(system = c("USM", "UML", "USL", "USML"),
                                     flower.vs.leaf = NA, 
                                     beetle.vs.leaf = NA, 
                                     beetle.vs.flower = NA)
## loop
for (i in 1:length(allvis.aim1_d65.list)) {
  
   meantable.i <- aggregate(allvis.aim1_d65.list[[i]][,"dS"], 
                            by = list(allvis.aim1_d65.list[[i]]$vissys), 
                            mean) 
   mean.i <- meantable.i[, 2] 
   contrast.list_d65.aim1[,i+1] <- mean.i # here same at column i+1 because the 1st column is the visual system names
}

## print out the table 
contrast.list_d65.aim1 %>% pander() 
```
#### Twilight
```{r}
allvis.aim1_twilight.list <- list(allvis.fl_twilight.aim1, allvis.bl_twilight.aim1, allvis.bf_twilight.aim1)

## create a data frame to hold the loop output
contrast.list_twilight.aim1 <- data_frame(system = c("USM", "UML", "USL", "USML"),
                                          flower.vs.leaf = NA, 
                                          beetle.vs.leaf = NA, 
                                          beetle.vs.flower = NA)
## loop
for (i in 1:length(allvis.aim1_twilight.list)) {
  
   meantable.i <- aggregate(allvis.aim1_twilight.list[[i]][,"dS"], 
                            by = list(allvis.aim1_twilight.list[[i]]$vissys), 
                            mean) 
   mean.i <- meantable.i[, 2] 
   contrast.list_twilight.aim1[,i+1] <- mean.i # here same at column i+1 because the 1st column is the visual system names
}

## print out the table 
contrast.list_twilight.aim1 %>% pander() 
```
### Aim 2 {.tabset .tabset-fade .tabset-pills}
The table shows the mean contrast in each comparison group

#### Daylight
```{r}
allvis.aim2_d65.list <- list(allvis.fl_d65.aim2, allvis.bl_d65.aim2, allvis.bf_d65.aim2)

## create a data frame to hold the loop output
contrast.list_d65.aim2 <- data_frame(system = c("VS 580", "VS 600", "VS 620", "VS 640", "VS 660"),
                                     flower.vs.leaf = NA, 
                                     beetle.vs.leaf = NA, 
                                     beetle.vs.flower = NA)
## loop
for (i in 1:length(allvis.aim2_d65.list)) {
  
   meantable.i <- aggregate(allvis.aim2_d65.list[[i]][,"dS"], 
                            by = list(allvis.aim2_d65.list[[i]]$vissys), 
                            mean) 
   mean.i <- meantable.i[, 2] 
   contrast.list_d65.aim2[,i+1] <- mean.i # here same at column i+1 because the 1st column is the visual system names
}

## print out the table 
contrast.list_d65.aim2 %>% pander() 
```
#### Twilight
```{r}
allvis.aim2_twilight.list <- list(allvis.fl_twilight.aim2, allvis.bl_twilight.aim2, allvis.bf_twilight.aim2)

## create a data frame to hold the loop output
contrast.list_twilight.aim2 <- data_frame(system = c("VS 580", "VS 600", "VS 620", "VS 640", "VS 660"),
                                          flower.vs.leaf = NA,
                                          beetle.vs.leaf = NA, 
                                          beetle.vs.flower = NA)
## loop
for (i in 1:length(allvis.aim2_twilight.list)) {
  
   meantable.i <- aggregate(allvis.aim2_twilight.list[[i]][,"dS"], 
                            by = list(allvis.aim2_twilight.list[[i]]$vissys), 
                            mean) 
   mean.i <- meantable.i[, 2] 
   contrast.list_twilight.aim2[,i+1] <- mean.i # here same at column i+1 because the 1st column is the visual system names
}

## print out the table 
contrast.list_twilight.aim2 %>% pander() 
```

# Compare contrasts
* We applied the same statistical approaches to compare contrasts between visual systems as in the [Main models](main_models.html).

## Check assumptions {.tabset .tabset-fade .tabset-pills}

* Before running the GLMMs, we first check if the data follows the assumption of normality and homogeneity of variance

</br>

Click the tabs to choose the assumptions ( __Normality__ / __Homogeneity__ ) of the visual models ( __Aim 1__ / __Aim 2__ ) under different light conditions ( __Daylight__ / __Twilight__)

</br>
```{r Group data for regressions}
# list data for the following loops
input.list.regres_d65.aim1 <- list(allvis.fl_d65.aim1,
                                   allvis.bl_d65.aim1,
                                   allvis.bf_d65.aim1)
input.list.regres_twilight.aim1 <- list(allvis.fl_twilight.aim1,
                                        allvis.bl_twilight.aim1,
                                        allvis.bf_twilight.aim1)
input.list.regres_d65.aim2 <- list(allvis.fl_d65.aim2,
                                   allvis.bl_d65.aim2,
                                   allvis.bf_d65.aim2)
input.list.regres_twilight.aim2 <- list(allvis.fl_twilight.aim2,
                                        allvis.bl_twilight.aim2,
                                        allvis.bf_twilight.aim2)
```

```{r Create regressions for assumption check}
##D65 - aim 1
res.list_d65.aim1 <- list(NA)

for (i in 1:length(input.list.regres_d65.aim1)) {
  res.i <- lm(
    input.list.regres_d65.aim1[[i]]$dS ~ input.list.regres_d65.aim1[[i]][,4])
  res.list_d65.aim1[[i]] <- res.i
}


##D65 - Aim 2
res.list_d65.aim2 <- list(NA)

for (i in 1:length(input.list.regres_d65.aim2)) {
  res.i <- lm(
    input.list.regres_d65.aim2[[i]]$dS ~ input.list.regres_d65.aim2[[i]][,4])
  res.list_d65.aim2[[i]] <- res.i
}

##Twilight - aim 1
res.list_twilight.aim1 <- list(NA)

for (i in 1:length(input.list.regres_twilight.aim1)) {
  res.i <- lm(
    input.list.regres_twilight.aim1[[i]]$dS ~ input.list.regres_twilight.aim1[[i]][,4])
  res.list_twilight.aim1[[i]] <- res.i
}

##Twilight - Aim 2
res.list_twilight.aim2 <- list(NA)

for (i in 1:length(input.list.regres_twilight.aim2)) {
  res.i <- lm(
    input.list.regres_twilight.aim2[[i]]$dS ~ input.list.regres_twilight.aim2[[i]][,4])
  res.list_twilight.aim2[[i]] <- res.i
}
```

### Normality {.tabset .tabset-fade .tabset-pills}

```{r Group data for the normality test}
group.list <- list("Flower vs Leaf", "Beetle vs Leaf", "Beetle vs Flower")
input.list.norm_d65.aim1 <- list(res.list_d65.aim1[[1]], 
                                 res.list_d65.aim1[[2]],
                                 res.list_d65.aim1[[3]])
input.list.norm_twilight.aim1 <- list(res.list_twilight.aim1[[1]], 
                                      res.list_twilight.aim1[[2]],
                                      res.list_twilight.aim1[[3]])
input.list.norm_d65.aim2 <- list(res.list_d65.aim2[[1]], 
                                 res.list_d65.aim2[[2]],
                                 res.list_d65.aim2[[3]])
input.list.norm_twilight.aim2 <- list(res.list_twilight.aim2[[1]], 
                                      res.list_twilight.aim2[[2]],
                                      res.list_twilight.aim2[[3]])
```
#### Aim 1 {.tabset .tabset-fade .tabset-pills}

##### D65 
```{r}
par(mfrow = c(1,3), pin = c(1.5, 1.5))
for (i in 1:length(input.list.norm_d65.aim1)) {
  
  qqnorm(input.list.norm_d65.aim1[[i]]$residuals, 
         main = group.list[[i]])
}
```

##### Twilight
```{r}
par(mfrow=c(1,3), pin = c(1.5, 1.5))
for (i in 1:length(input.list.norm_twilight.aim1)) {
  
  qqnorm(input.list.norm_twilight.aim1[[i]]$residuals, 
         main = group.list[[i]])
}
```

#### Aim 2 {.tabset .tabset-fade .tabset-pills}
##### D65 
```{r}
par(mfrow=c(1,3), pin = c(1.5, 1.5))
for (i in 1:length(input.list.norm_d65.aim2)) {
  
  qqnorm(input.list.norm_d65.aim2[[i]]$residuals, 
         main = group.list[[i]])
}
```

##### Twilight
```{r}
par(mfrow=c(1,3), pin = c(1.5, 1.5))
for (i in 1:length(input.list.norm_twilight.aim2)) {
  
  qqnorm(input.list.norm_twilight.aim2[[i]]$residuals, 
         main = group.list[[i]])
}
```

### Homoscedasticity {.tabset .tabset-fade .tabset-pills}
```{r}
vislist.aim1 <- c("UML", "USL", "USM", "USML")
vislist.aim2 <- c("VS 580", "VS 600", "VS 620", "VS 640", "VS 660")
```

#### Aim 1 {.tabset .tabset-fade .tabset-pills}

##### D65
```{r}
par (mfrow = c(1,3), oma = c(2,2,0,0)) #oma=c() to create space for common labels

for (i in 1:length(input.list.regres_d65.aim1)) {
boxplot(input.list.regres_d65.aim1[[i]]$dS ~ input.list.regres_d65.aim1[[i]][,4], 
        # the forth column is the compairson group name
        las = 2,
        main = group.list[[i]],
        names = vislist.aim1)
}

mtext("Visual system",side = 1, line = 0, outer = TRUE, cex = 1.3) 
#side assigns the position of the text e.g. bottom
mtext("Contrast (JND)",side = 2, line = 0, outer = TRUE, cex = 1.3, las = 0) 
#las assigns the orientation of the text
```

##### Twilight
```{r}
par (mfrow = c(1,3), oma = c(2,2,0,0))

for (i in 1:length(input.list.regres_twilight.aim1)) {
boxplot(input.list.regres_twilight.aim1[[i]]$dS ~ input.list.regres_twilight.aim1[[i]][,4], 
        las = 2,
        main = group.list[[i]],
        names = vislist.aim1)
}

mtext("Visual system",side = 1, line = 0, outer = TRUE, cex = 1.3) 
mtext("Contrast (JND)",side = 2, line = 0, outer = TRUE, cex = 1.3, las = 0) 
```

#### Aim 2 {.tabset .tabset-fade .tabset-pills}
##### D65
```{r}
par (mfrow = c(1,3), oma = c(2,2,0,0))

for (i in 1:length(input.list.regres_d65.aim2)) {
boxplot(input.list.regres_d65.aim2[[i]]$dS ~ input.list.regres_d65.aim2[[i]][,4], 
        las = 2,
        main = group.list[[i]],
        names = vislist.aim2)
}

mtext("Visual system",side = 1, line = 0, outer = TRUE, cex = 1.3) 
mtext("Contrast (JND)",side = 2, line = 0, outer = TRUE, cex = 1.3, las = 0) 
```

##### Twilight 
```{r}
par (mfrow = c(1,3), oma = c(2,2,0,0))

for (i in 1:length(input.list.regres_twilight.aim2)) {
boxplot(input.list.regres_twilight.aim2[[i]]$dS ~ input.list.regres_twilight.aim2[[i]][,4], 
        las = 2,
        main = group.list[[i]],
        names = vislist.aim2)
}

mtext("Visual system",side = 1, line = 0, outer = TRUE, cex = 1.3) 
mtext("Contrast (JND)",side = 2, line = 0, outer = TRUE, cex = 1.3, las = 0) 
```


</br>
</br>

## GLMM results

</br>

```{r Set up functions for GLMM}
get.lmer <- function(datlist, compnnumber){
  
  lmer(dS ~ vissys + (1|patch2) + (1|patch1), 
       data = datlist[[compnnumber]], REML = F)
  #REML=F, in order to fit the model using the likelihood ratio test. Otherwise, the lmer default will fit the model using the REML (REstricted Maximum Likelihood) criterion.
}

get.posthocsum <- function(modelx){
  
  summary(glht(modelx, 
               linfct = mcp(vissys = "Tukey")), 
          test = adjusted("bonferroni"))
}
```

```{r Run GLMM models}
#GLMM - D65 - aim 1
##Flower vs Leaf
m.flower.vs.leaf_d65.aim1 <- get.lmer(input.list.regres_d65.aim1, 1)
sum.flower.vs.leaf_d65.aim1 <- get.posthocsum(m.flower.vs.leaf_d65.aim1)

##Beetle vs Leaf
m.beetle.vs.leaf_d65.aim1 <- get.lmer(input.list.regres_d65.aim1, 2)
sum.beetle.vs.leaf_d65.aim1 <- get.posthocsum(m.beetle.vs.leaf_d65.aim1)

##Beetle vs Flower
m.beetle.vs.flower_d65.aim1 <- get.lmer(input.list.regres_d65.aim1, 3)
sum.beetle.vs.flower_d65.aim1 <- get.posthocsum(m.beetle.vs.flower_d65.aim1)

#GLMM - D65 - Aim 2
##Flower vs Leaf
m.flower.vs.leaf_d65.aim2 <- get.lmer(input.list.regres_d65.aim2, 1)
sum.flower.vs.leaf_d65.aim2 <- get.posthocsum(m.flower.vs.leaf_d65.aim2)

##Beetle vs Leaf
m.beetle.vs.leaf_d65.aim2 <- get.lmer(input.list.regres_d65.aim2, 2)
sum.beetle.vs.leaf_d65.aim2 <- get.posthocsum(m.beetle.vs.leaf_d65.aim2)

##Beetle vs Flower
m.beetle.vs.flower_d65.aim2 <- get.lmer(input.list.regres_d65.aim2, 3)
sum.beetle.vs.flower_d65.aim2 <- get.posthocsum(m.beetle.vs.flower_d65.aim2)


#GLMM - Twilight - Aim 1
##Flower vs Leaf
m.flower.vs.leaf_twilight.aim1 <- get.lmer(input.list.regres_twilight.aim1, 1)
sum.flower.vs.leaf_twilight.aim1 <- get.posthocsum(m.flower.vs.leaf_twilight.aim1)

##Beetle vs Leaf
m.beetle.vs.leaf_twilight.aim1 <- get.lmer(input.list.regres_twilight.aim1, 2)
sum.beetle.vs.leaf_twilight.aim1 <- get.posthocsum(m.beetle.vs.leaf_twilight.aim1)

##Beetle vs Flower
m.beetle.vs.flower_twilight.aim1 <- get.lmer(input.list.regres_twilight.aim1, 3)
sum.beetle.vs.flower_twilight.aim1 <- get.posthocsum(m.beetle.vs.flower_twilight.aim1)

#GLMM - Twilight - Aim 2
##Flower vs Leaf
m.flower.vs.leaf_twilight.aim2 <- get.lmer(input.list.regres_twilight.aim2, 1)
sum.flower.vs.leaf_twilight.aim2 <- get.posthocsum(m.flower.vs.leaf_twilight.aim2)

##Beetle vs Leaf
m.beetle.vs.leaf_twilight.aim2 <- get.lmer(input.list.regres_twilight.aim2, 2)
sum.beetle.vs.leaf_twilight.aim2 <- get.posthocsum(m.beetle.vs.leaf_twilight.aim2)

##Beetle vs Flower
m.beetle.vs.flower_twilight.aim2 <- get.lmer(input.list.regres_twilight.aim2, 3)
sum.beetle.vs.flower_twilight.aim2 <- get.posthocsum(m.beetle.vs.flower_twilight.aim2)
```

```{r Set up lists and function for heap maps}
# Set up lists
vislist.heatmap.aim1 <- list(c("USL", "USM","USML","USM","USML","USML"),
                             c("UML", "UML","UML","USL","USL","USM"))
vislist.heatmap.aim2 <- list(c("VS 600", "VS 620","VS 640","VS 660","VS 620","VS 640","VS 660","VS 640","VS 660","VS 660"),
                             c("VS 580","VS 580","VS 580","VS 580","VS 600","VS 600","VS 600","VS 620","VS 620","VS 640"))

# Set up the function
get.heatmap.datframe <- function(i,z){
  
  heatmapdat.i <- data.frame(as.numeric(str_extract(i[[1]],"([0-9]+).*$"))) %>%
    cbind(as.numeric(str_extract(i[[2]],"([0-9]+).*$"))) %>% 
    cbind(as.numeric(str_extract(i[[3]],"([0-9]+).*$"))) %>%
    dplyr::rename(flower.vs.leaf = 1, beetle.vs.leaf = 2, beetle.vs.flower = 3) %>% 
    cbind(z[[1]]) %>% 
    cbind(z[[2]]) 
  
  colnames(heatmapdat.i)[4:5] <- c("VislistA", "VislistB")
  
  return(heatmapdat.i)
}
```

```{r Create p-value heat map}
# D65 - Aim 1
## reshape data for heat map
pdata_d65.aim1 <- list(sum.flower.vs.leaf_d65.aim1[["test"]][["pvalues"]],
                       sum.beetle.vs.leaf_d65.aim1[["test"]][["pvalues"]],
                       sum.beetle.vs.flower_d65.aim1[["test"]][["pvalues"]])

heat_d65.aim1 <- get.heatmap.datframe(pdata_d65.aim1, vislist.heatmap.aim1)


# D65 - Aim 2
## reshape data for heat map
pdata_d65.aim2 <- list(sum.flower.vs.leaf_d65.aim2[["test"]][["pvalues"]],
                       sum.beetle.vs.leaf_d65.aim2[["test"]][["pvalues"]],
                       sum.beetle.vs.flower_d65.aim2[["test"]][["pvalues"]])

heat_d65.aim2 <- get.heatmap.datframe(pdata_d65.aim2, vislist.heatmap.aim2)

#Twilight - Aim 1
## reshape data for heatmap
pdata_twilight.aim1 <- list(sum.flower.vs.leaf_twilight.aim1[["test"]][["pvalues"]],
                            sum.beetle.vs.leaf_twilight.aim1[["test"]][["pvalues"]],
                            sum.beetle.vs.flower_twilight.aim1[["test"]][["pvalues"]])

heat_twilight.aim1 <- get.heatmap.datframe(pdata_twilight.aim1, vislist.heatmap.aim1)


# Twilight - Aim 2
##reshape data for heat map
pdata_twilight.aim2 <- list(sum.flower.vs.leaf_twilight.aim2[["test"]][["pvalues"]],
                       sum.beetle.vs.leaf_twilight.aim2[["test"]][["pvalues"]],
                       sum.beetle.vs.flower_twilight.aim2[["test"]][["pvalues"]])

heat_twilight.aim2 <- get.heatmap.datframe(pdata_twilight.aim2, vislist.heatmap.aim2)


# Assign asterisk signs
pdatalist <- list(heat_d65.aim1, heat_d65.aim2, heat_twilight.aim1, heat_twilight.aim2)

for (i in 1:length(pdatalist)) {
  
  pdatalist[[i]]$sig.flower.vs.leaf[pdatalist[[i]]$flower.vs.leaf > 0.05] <- ""
  pdatalist[[i]]$sig.flower.vs.leaf[pdatalist[[i]]$flower.vs.leaf < 0.05] <- "*"
  pdatalist[[i]]$sig.flower.vs.leaf[pdatalist[[i]]$flower.vs.leaf < 0.01] <- "**"
  pdatalist[[i]]$sig.flower.vs.leaf[pdatalist[[i]]$flower.vs.leaf < 0.0001] <- "***"
  pdatalist[[i]]$sig.beetle.vs.leaf[pdatalist[[i]]$beetle.vs.leaf > 0.05] <- ""
  pdatalist[[i]]$sig.beetle.vs.leaf[pdatalist[[i]]$beetle.vs.leaf < 0.05] <- "*"
  pdatalist[[i]]$sig.beetle.vs.leaf[pdatalist[[i]]$beetle.vs.leaf < 0.01] <- "**"
  pdatalist[[i]]$sig.beetle.vs.leaf[pdatalist[[i]]$beetle.vs.leaf < 0.0001] <- "***"
  pdatalist[[i]]$sig.beetle.vs.flower[pdatalist[[i]]$beetle.vs.flower > 0.05] <- ""
  pdatalist[[i]]$sig.beetle.vs.flower[pdatalist[[i]]$beetle.vs.flower < 0.05] <- "*"
  pdatalist[[i]]$sig.beetle.vs.flower[pdatalist[[i]]$beetle.vs.flower < 0.01] <- "**"
  pdatalist[[i]]$sig.beetle.vs.flower[pdatalist[[i]]$beetle.vs.flower < 0.0001] <- "***"
  
}

# Because we did the assignment on a data list, now we need to link the loop output back to the data respectively
heat_d65.aim1 <- pdatalist[[1]] 
heat_d65.aim2 <- pdatalist[[2]]
heat_twilight.aim1 <- pdatalist[[3]]
heat_twilight.aim2 <- pdatalist[[4]]
```

### Results of Aim 1: comparing visual systems with different photoreceptor combinations {.tabset .tabset-fade .tabset-pills}

</br>

Click the tabs to see the results for each comparison group ( __Flower vs. Leaf__ / __Beetle vs. Leaf__ / __Beetle vs. Flower__) and under different light conditions ( __Daylight__ / __Twilight__)
```{r Function for p-value heat maps}
# a = data
# b = 1/2/3; 1 for flower.vs.leaf, 2 for beetle.vs.leaf, 3 for beetle.vs.flower
get.pheatmap <- function(a, b){ggplot(data = a, 
                                        aes(x = VislistA, 
                                            y = VislistB, 
                                            fill = a[,b])) + 
    geom_tile(colour = "white", size = 4)+
    geom_text(aes(VislistA, 
                  VislistB, 
                  label = paste(format(round(a[,b], 2), nsmall = 2), 
                                a[, b+5])))+
    scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit = c(0,1))+ #delete if want to reverse the colour
    theme_bw()+
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          panel.grid = element_blank(), 
          panel.border = element_blank(), 
          axis.ticks = element_blank() )+
    labs(fill = "p vaalue")
  
}
```

</br>

#### __Flower v.s Leaf__ {.tabset .tabset-fade .tabset-pills}
##### Daylight{.tabset .tabset-fade .tabset-pills}

```{r}
Anova(m.flower.vs.leaf_d65.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values 
```{r}
get.pheatmap(heat_d65.aim1, 1)
```

###### Original model output
```{r}
sum.flower.vs.leaf_d65.aim1
```

##### Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.leaf_twilight.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values
```{r}
get.pheatmap(heat_twilight.aim1, 1)
```

###### Original model output
```{r}
sum.flower.vs.leaf_twilight.aim1
```

#### __Beetle vs. Leaf__ {.tabset .tabset-fade .tabset-pills}
##### Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.leaf_d65.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values 
```{r}
get.pheatmap(heat_d65.aim1, 2)
```

###### Original model output
```{r}
sum.beetle.vs.leaf_d65.aim1
```

##### Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.leaf_twilight.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values
```{r}
get.pheatmap(heat_twilight.aim1, 2)
```

###### Original model output
```{r}
sum.beetle.vs.leaf_twilight.aim1
```

#### __Beetle vs. Flower__ {.tabset .tabset-fade .tabset-pills}
##### Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.flower_d65.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values 
```{r}
get.pheatmap(heat_d65.aim1, 3)
```

###### Original model output
```{r}
sum.beetle.vs.flower_d65.aim1
```

##### Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.flower_twilight.aim1) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values
```{r}
get.pheatmap(heat_twilight.aim1, 3)
```

###### Original model output
```{r}
sum.beetle.vs.flower_twilight.aim1
```


</br>
</br>


### Results of Aim 2: comparing visual systems with different LWS peak sensitivities {.tabset .tabset-fade .tabset-pills}

</br>

Click the tabs to see the results for each comparison group ( __Flower vs. Leaf__ / __Beetle vs. Leaf__ / __Beetle vs. Flower__) and under different light conditions ( __Daylight__ / __Twilight__)

</br>

#### __Flower v.s Leaf__ {.tabset .tabset-fade .tabset-pills}
##### Daylight {.tabset .tabset-fade .tabset-pills}

```{r}
Anova(m.flower.vs.leaf_d65.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values 
```{r}
get.pheatmap(heat_d65.aim2, 1)
```

###### Original model output
```{r}
sum.flower.vs.leaf_d65.aim2
```

##### Twilight {.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.leaf_twilight.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values
```{r}
get.pheatmap(heat_twilight.aim2, 1)
```

###### Original model output
```{r}
sum.flower.vs.leaf_twilight.aim2
```

#### __Beetle vs. Leaf__ {.tabset .tabset-fade .tabset-pills}
##### Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.leaf_d65.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values 
```{r}
get.pheatmap(heat_d65.aim2, 2)
```

###### Original model output
```{r}
sum.beetle.vs.leaf_d65.aim2
```

##### Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.leaf_twilight.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values
```{r}
get.pheatmap(heat_twilight.aim2, 2)
```

###### Original model output
```{r}
sum.beetle.vs.leaf_twilight.aim2
```

#### __Beetle vs. Flower__ {.tabset .tabset-fade .tabset-pills}
##### Daylight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.flower_d65.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values 
```{r}
get.pheatmap(heat_d65.aim2, 3)
```

###### Original model output
```{r}
sum.beetle.vs.flower_d65.aim2
```

##### Twilight{.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.beetle.vs.flower_twilight.aim2) %>% pander()
```

</br>
</br>

Click the tabs to see posthoc results ( __p-value summary plot__ / __original model output__ )

###### Pair-wise p-values
```{r}
get.pheatmap(heat_twilight.aim2, 3)
```

###### Original model output
```{r}
sum.beetle.vs.flower_twilight.aim2
```


</br>
</br>

# Plot the contrasts {.tabset .tabset-fade .tabset-pills}
* Colours approximate human perception of either flower (left and right) or beetle (centre) colouration.
* Lines of the same colors connect the same sample

```{r Import color code and setup functions}
#import the sample color code 
color.code <- read.csv("data/color code list.csv", header=TRUE) 

# Set up a function to calculate means for the plot
get.plotmeans <- function(a, b, c){
  if (a == "aim1"){
    if(b == "bl"){
      plotmean.i <- c %>% 
        group_by(patch2, vissys) %>%
        summarize(mean.dS.sub = mean(dS)) %>% 
        ungroup() %>% 
        rename(beetleID = patch2) %>% 
        merge(beetle.colour.aim1[,c("species", "colour")], by.x = c("beetleID"), by.y = c("species")) %>% 
        distinct()
      return(plotmean.i)
    } else {
      plotmean.i <- c %>% 
        group_by(patch1, vissys) %>%
        summarize(mean.dS.sub = mean(dS)) %>% 
        ungroup() %>% 
        rename(flowerID = patch1) %>% 
        merge(flower.colour.aim1[,c("species", "colour")], by.x = c("flowerID"), by.y = c("species")) %>% 
        distinct()
      return(plotmean.i)
    }
  } else if (a == "aim2"){
    if (b == "bl"){
      plotmean.i <- c %>% 
        group_by(patch2, vissys) %>%
        summarize(mean.dS.sub = mean(dS)) %>% 
        ungroup() %>% 
        rename(beetleID = patch2) %>% 
        merge(beetle.colour.aim2[,c("species", "colour")], by.x = c("beetleID"), by.y = c("species")) %>% 
        distinct()
      return(plotmean.i)
    } else {
      plotmean.i <- c %>% 
        group_by(patch1, vissys) %>%
        summarize(mean.dS.sub = mean(dS)) %>% 
        ungroup() %>% 
        rename(flowerID = patch1) %>% 
        merge(flower.colour.aim2[,c("species", "colour")], by.x = c("flowerID"), by.y = c("species")) %>% 
        distinct()
      return(plotmean.i)
    }
  }
}

# What should be put in the function get.plotmeans()
# a = "aim1" or "aim2"
# b = comparison type: "fl", "bl", "bf"
# c = input data, e.g. allvis.fl_d65.aim1
```

```{r Create colour code lists for the plot}
# transform the data for plotting purpose
dataset.transpose <- gather(dataset[,2:131], 
                            key = "species", 
                            value = "reflectance", 
                            na.rm = FALSE,
                          convert = FALSE, 
                          factor_key = FALSE)

# create a list of species name used in the spec data in oder to merge() with mean data set later
name.list <- unique(dataset.transpose$species) %>% 
  sort() %>% #order it alphabetically 
  data.frame() %>% 
  dplyr::rename(species = ".") #make it a data frame and name the column "species"

# create flower and beetle name list 
colourgrouplist <- c( "flower", "beetle")
tempcolordat <- vector("list", 4)

## for aim 1
for(i in seq_along(colourgrouplist)){
  
  ouput.i <- name.list %>% 
    filter(str_detect(species, colourgrouplist[i])) %>% 
    cbind(color.code %>% 
            filter(str_detect(type, colourgrouplist[i])) %>% 
            arrange(name)) %>% 
    dplyr::select(-type) %>% 
    mutate(count = 4) %>% 
    uncount(count) 
  
  tempcolordat[[i]] <- ouput.i
  
}
flower.colour.aim1 <- tempcolordat[[1]]
beetle.colour.aim1 <- tempcolordat[[2]]

## for Aim 2
for(i in seq_along(colourgrouplist)){
  
  ouput.i <- name.list %>% 
    filter(str_detect(species, colourgrouplist[i])) %>% 
    cbind(color.code %>% 
            filter(str_detect(type, colourgrouplist[i])) %>% 
            arrange(name)) %>% 
    dplyr::select(-type) %>% 
    mutate(count = 5) %>% 
    uncount(count) 
  
  tempcolordat[[i+2]] <- ouput.i # here same in i+2 because 1-2 is for aim1
  
}
flower.colour.aim2 <- tempcolordat[[3]]
beetle.colour.aim2 <- tempcolordat[[4]]
```

```{r Calculate means for each visual system on the plot}
allvis.list <- list(allvis.fl_d65.aim1, allvis.bl_d65.aim1, allvis.bf_d65.aim1,
                 allvis.fl_d65.aim2, allvis.bl_d65.aim2, allvis.bf_d65.aim2,
                 allvis.fl_twilight.aim1, allvis.bl_twilight.aim1, allvis.bf_twilight.aim1,
                 allvis.fl_twilight.aim2, allvis.bl_twilight.aim2, allvis.bf_twilight.aim2)

tempcolordat <- vector("list", length(allvis.list))

for(i in seq_along(allvis.list)){
  
  temp.meandS.i <- allvis.list[[i]] %>% 
    group_by(vissys) %>%
    summarize(mean.dS = mean(dS))
  
  tempcolordat[[i]] <- temp.meandS.i
  
}
```

```{r Set up list and functions for plots}
title.list <- list("Flower vs. Leaf", "Beetle vs. Leaf", "Beetle vs. Flower")
ylim.list <- c(21, 2) # 21 for aim1, 2 for aim2
vislable.list <- list(c("USM", "UML", "USL","USML"), # aim1
                      c("VS 580", "VS 600","VS 620","VS 640","VS 660")) # aim2

vis.comp.list <- list(fl.aim1 <- c("UVSWMW...fl", "UV..MWLW.fl", "UVSW..LW.fl", "UVSWMWLW.fl"),
                      bl.aim1 <- c("UVSWMW...bl", "UV..MWLW.bl", "UVSW..LW.bl", "UVSWMWLW.bl"),
                      bf.aim1 <- c("UVSWMW...bf", "UV..MWLW.bf", "UVSW..LW.bf", "UVSWMWLW.bf"),
                      fl.aim2 <- c("VS580.fl", "VS600.fl", "VS620.fl", "VS640.fl", "VS660.fl"),
                      bl.aim2 <- c("VS580.bl", "VS600.bl", "VS620.bl", "VS640.bl", "VS660.bl"),
                      bf.aim2 <- c("VS580.bf", "VS600.bf", "VS620.bf", "VS640.bf", "VS660.bf"))

stats.list <- list(fl_d65.aim1 <- c("a","b","a","a"),
                   bl_d65.aim1 <- c("a","b","b","b"),
                   bf_d65.aim1 <- c("a","b","a","a"),
                   fl_d65.aim2 <- c("a","b","cd","c","d"),
                   bl_d65.aim2 <- c("a","b","c","d","e"),
                   bf_d65.aim2 <- c("a","a","b","c","d"),
                   fl_twilight.aim1 <- c("a","a","b","c"),
                   bl_twilight.aim1 <- c("a","b","b","c"),
                   bf_twilight.aim1 <- c("a","b","c","d"),
                   fl_twilight.aim2 <- c("a","b","c","c","b"),
                   bl_twilight.aim2 <- c("a","b","c","d","e"),
                   bf_twilight.aim2 <- c("a","b","c","d","e"))

backgorund.list <- c("grey80", NA) # choose NA for beetle.vs.leaf

get.contrastplot <- function(dat, title, vislable, upperylim, visomplist, compgroupnstats, background){
  ggplot(dat, aes(x = vissys, 
                y = mean.dS.sub,
                group = factor(dat[,1])))+
    geom_point(col = dat$colour,
               size = 1, alpha = 0.7) + 
    geom_line(col = dat$colour, 
              size = 0.5, alpha = 0.7)+
    xlab("Visual system") +     
    ylab("Chromatic contrast (JND)") +
    ylim(0, ylim.list[upperylim])+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = backgorund.list[background], size = NA), 
          axis.title.x = element_text(size = 12),  
          axis.text.x  = element_text(size = 8, colour = "black", angle = 90),
          axis.title.y = element_text(size = 12, vjust = 1),
          axis.text.y = element_text(size = 8, colour = "black"),
          axis.line.x = element_line(colour = 'black', size = 0.5, linetype = 'solid'),
          axis.line.y = element_line(colour = 'black', size = 0.5, linetype = 'solid'),
          legend.justification = c(1,0), 
          legend.position = c(1,0.45),
          legend.key = element_blank(),
          legend.title = element_text(size = 10),
          legend.text = element_text(size = 9))+
    scale_x_discrete(limits = vis.comp.list[[visomplist]],
                     labels = vislable.list[vislable])+
    geom_point(data = dat, 
               aes(x = vis.comp.list[[visomplist]][1], 
                   y = tempcolordat[[compgroupnstats]]$mean.dS[1]),
               col = "black", size = 3)+
    geom_point(data = dat, 
               aes(x = vis.comp.list[[visomplist]][2], 
                   y = tempcolordat[[compgroupnstats]]$mean.dS[2]), 
               col = "black", size = 3)+
    geom_point(data = dat, 
               aes(x = vis.comp.list[[visomplist]][3], 
                   y = tempcolordat[[compgroupnstats]]$mean.dS[3]), 
               col = "black", size = 3)+
    geom_point(data = dat, 
               aes(x = vis.comp.list[[visomplist]][4], 
                   y = tempcolordat[[compgroupnstats]]$mean.dS[4]), 
               col = "black", size = 3)+
    geom_point(data = dat, 
               aes(x = vis.comp.list[[visomplist]][5], 
                   y = tempcolordat[[compgroupnstats]]$mean.dS[5]), 
               col = "black", size = 3)+
    ggtitle(title.list[[title]])+
    annotate("text", x = vis.comp.list[[visomplist]], y = ylim.list[upperylim], 
             label = stats.list[[compgroupnstats]])
    
}

```
</br>

## Aim 1 {.tabset .tabset-fade .tabset-pills}
### Daylight
```{r,fig.cap="Figure caption: Comparison of chromatic contrast for visual systems with different photoreceptor combinations. Black dots show the means of the representative contrasts in visual systems. Each coloured dot represents the average contrast of each flower pattern to all leaves (left panel), each beetle colour to all leaves (middle panel) or each flower colour to all beetle colours (right panel). Colours of the dots correspond to the human-visible colour of the flower (left and right panels) or beetle (middle panel) with the lines of the same colour connecting the results between different visual systems. This is for graphical representation only; statistical tests are based on all pairwise combinations of spectra and not averages. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1. Three contrasts > 13 JND are from flowers that have high UV - blue chroma compared to beetles and leaves."}

# create a data set for means
mean.fl_d65.aim1 <- get.plotmeans("aim1", "fl", allvis.fl_d65.aim1)
mean.bl_d65.aim1 <- get.plotmeans("aim1", "bl", allvis.bl_d65.aim1)
mean.bf_d65.aim1 <- get.plotmeans("aim1", "bf", allvis.bf_d65.aim1)

# plot individual panel
fl_d65.aim1 <- get.contrastplot(mean.fl_d65.aim1, 1, 1, 1, 1, 1, 1) # flower vs leaf
bl_d65.aim1 <- get.contrastplot(mean.bl_d65.aim1, 2, 1, 1, 2, 2, 2) # beetle vs leaf
bf_d65.aim1 <- get.contrastplot(mean.bf_d65.aim1, 3, 1, 1, 3, 3, 1) # beetle vs flower

# bind the 3 panels
figure_d65.aim1 <- ggarrange(fl_d65.aim1,
                             bl_d65.aim1,
                             bf_d65.aim1, 
                             ncol = 3, nrow = 1)
figure_d65.aim1
```

### Twilight
```{r,fig.cap="Figure caption: Comparison of chromatic contrast for visual systems with different photoreceptor combinations under civil twilight illumination. Black dots show the means of the representative contrasts in visual systems. Each coloured dot represents the average contrast of each flower pattern to all leaves (left panel), each beetle colour to all leaves (middle panel) or each flower colour to all beetle colours (right panel). Colours of the dots correspond to the human-visible colour of the flower (left and right panels) or beetle (middle panel) with the lines of the same colour connecting the results between different visual systems. This is for graphical representation only; statistical tests are based on all pairwise combinations of spectra and not averages. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1."}
# create a data set for means
mean.fl_twilight.aim1 <- get.plotmeans("aim1", "fl", allvis.fl_twilight.aim1)
mean.bl_twilight.aim1 <- get.plotmeans("aim1", "bl", allvis.bl_twilight.aim1)
mean.bf_twilight.aim1 <- get.plotmeans("aim1", "bf", allvis.bf_twilight.aim1)

# plot individual panel
fl_twilight.aim1 <- get.contrastplot(mean.fl_twilight.aim1, 1, 1, 2, 1, 7, 1)
bl_twilight.aim1 <- get.contrastplot(mean.bl_twilight.aim1, 2, 1, 2, 2, 8, 2)
bf_twilight.aim1 <- get.contrastplot(mean.bf_twilight.aim1, 3, 1, 2, 3, 9, 1)

# bind the 3 panels
figure_twilight.aim1 <- ggarrange(fl_twilight.aim1,
                                  bl_twilight.aim1,
                                  bf_twilight.aim1, 
                                  ncol = 3, nrow = 1)
figure_twilight.aim1
```


## Aim 2 {.tabset .tabset-fade .tabset-pills}
### Daylight
```{r,fig.cap="Figure caption: Comparison of chromatic contrast between visual systems with the LWS photoreceptor peaking at different wavelengths. Black dots show the means of the representative contrasts in visual systems. Each coloured dot represents the average contrast of each flower pattern to all leaves (left panel), each beetle colour to all leaves (middle panel) or each flower colour to all beetle colours (right panel). Colours of the dots correspond to the human-visible colour of the flower (left and right panels) or beetle (middle panel) with the lines of the same colour connecting the results between different visual systems. This is for graphical representation only; statistical tests are based on all pairwise combinations of spectra and not averages. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1. Three contrasts > 13 JND are from flowers that have high UV - blue chroma compared to beetles and leaves."}

# create a data set for means
mean.fl_d65.aim2 <- get.plotmeans("aim2", "fl", allvis.fl_d65.aim2)
mean.bl_d65.aim2 <- get.plotmeans("aim2", "bl", allvis.bl_d65.aim2)
mean.bf_d65.aim2 <- get.plotmeans("aim2", "bf", allvis.bf_d65.aim2)

# plot individual panel
fl_d65.aim2 <- get.contrastplot(mean.fl_d65.aim2, 1, 2, 1, 4, 4, 1)
bl_d65.aim2 <- get.contrastplot(mean.bl_d65.aim2, 2, 2, 1, 5, 5, 2)
bf_d65.aim2 <- get.contrastplot(mean.bf_d65.aim2, 3, 2, 1, 6, 6, 1)

# bind the 3 panels
figure_d65.aim2 <- ggarrange(fl_d65.aim2,
                             bl_d65.aim2,
                             bf_d65.aim2, 
                             ncol = 3, nrow = 1)
figure_d65.aim2
```

### Twilight
```{r,fig.cap="Figure caption: Comparison of chromatic contrast between visual systems with the LWS photoreceptor peaking at different wavelengths under civil twilight illumination. Black dots show the means of the representative contrasts in visual systems. Each coloured dot represents the average contrast of each flower pattern to all leaves (left panel), each beetle colour to all leaves (middle panel) or each flower colour to all beetle colours (right panel). Colours of the dots correspond to the human-visible colour of the flower (left and right panels) or beetle (middle panel) with the lines of the same colour connecting the results between different visual systems. This is for graphical representation only; statistical tests are based on all pairwise combinations of spectra and not averages. Letters on the top of each panel show the significant difference in contrast between visual systems. Dotted horizontal line indicates JND=1."}
# create a data set for means
mean.fl_twilight.aim2 <- get.plotmeans("aim2", "fl", allvis.fl_twilight.aim2)
mean.bl_twilight.aim2 <- get.plotmeans("aim2", "bl", allvis.bl_twilight.aim2)
mean.bf_twilight.aim2 <- get.plotmeans("aim2", "bf", allvis.bf_twilight.aim2)

# plot individual panel
fl_twilight.aim2 <- get.contrastplot(mean.fl_twilight.aim2, 1, 2, 2, 4, 10, 1)
bl_twilight.aim2 <- get.contrastplot(mean.bl_twilight.aim2, 2, 2, 2, 5, 11, 2)
bf_twilight.aim2 <- get.contrastplot(mean.bf_twilight.aim2, 3, 2, 2, 6, 12, 1)

# bind the 3 panels
figure_twilight.aim2 <- ggarrange(fl_twilight.aim2,
                                  bl_twilight.aim2,
                                  bf_twilight.aim2, 
                                  ncol = 3, nrow = 1)
figure_twilight.aim2
```

# Summary

* Models with opsin-shifted LWS receptors showed qualitatively similar results for the comparison of beetles against leaves, with a LWS receptor improving contrast. However, only the presence of a SWS receptor improved contrasts of beetles against flowers and flowers against leaves. 
* When increasing peak sensitivities from 580 nm to 660 nm,the results were similar to that of filter-shifted models --  the contrasts increased from VS 580 to at least VS 640 but the differences in contrast between visual systems were smaller.