---
title: "Sensitivity analysis"
author: <br>Lu-Yi Wang^1^, Devi Stuart-Fox^1^, Geoff Walker^1^, Nicholas W. Roberts^2^
  and Amanda M. Franklin^1^ <br></br> ^1^School of Biosciences, The University of Melbourne,
  Australia <br></br> ^2^School of Biological Sciences, University of Bristol, UK
  <br></br>
output:
  pdf_document: default
  html_document:
    theme: flatly
    toc: true
    toc_depth: 2
subtitle: Supplementary Information
Date: July 28 2020
---
#The aim

To test whether the modelling results were sensitive to the photoreceptor ratios used, we repeated these analyses using published ratios that represent the known variation in insects. Specifically, we compared the tetrachomat visual sistem with peak sensitivities at 380, 460, 520 and 580 nm.
</br>
</br>
We applied the same modelling method described in the main text but using ratios of different insects, including the jewel beetle, *Agrilus planipennis* (same as the ratio used in the main text; 1.14: 1: 1.26: 1.38; UVS: SWS: MWS: LWS), and two butterflies, *Papilio Xuthus* (1: 1: 4.08: 2.92) and *Heliconius* sp. type III (0.09: 0.13: 0.2: 1).
</br>
</br>
The model parameters and the statistical methods remain the same as described in the main text.

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pavo)
library(dplyr)
library(stringr)
library(tidyr) #for gather() function
library(ggplot2)
library(lme4)
library(car)
library(multcomp)
library(boot) #for mean() function
library(pander) #for creating tidy tables
library(ggpubr) #for ggarrange() function
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE) # Suppress warnings in the HTML output
knitr::opts_chunk$set(cache=TRUE, warning = F) # set up cacheing to save time when re-building the html document
```

```{r ,echo=FALSE,message=FALSE, warning=FALSE}
#import sensitivity curves
specsensbuprest.model2 <- read.csv("data/peak sensitivity_filter shift_aim2.csv",header=TRUE) %>% as.rspec()
#import irradiance
irradiance.d65 <- read.csv("data/d65.csv",header=TRUE) %>% 
  as.rspec(lim=c(300,800)) %>%  #set import range
  procspec(opt = c("min", "max")) #standardize the illumination spectrum

#import backgound - average leaf
aveleaf <- read.csv("data/aveleaf.csv",header=TRUE) %>% as.rspec()

#import and combind beetle, flower, leaf together
raw.dataset<-read.csv("data/pooled_spec_2019.csv",header=TRUE) %>% as.rspec()
dataset<- aggspec(raw.dataset, by = 3, FUN = mean) %>%  #average three measurements to a representative one
  procspec(opt = "smooth", span = 0.1, fixneg = "zero") #smooth the spectra and lift <0 to 0
```

```{r,echo=FALSE,message=FALSE, warning=FALSE}
#import spectral data
#assign categoryies to each spectrum
category.list <- c("flower","leaf","beetle")
category <- rep(category.list , c(47*501,46*501,37*501))
wavelength<-rep(dataset[,1])

#transform the data for ploting purpose
dataset.transpose<-gather(dataset[,2:131], key = "species", value = "reflectance", na.rm = FALSE,
       convert = FALSE, factor_key = FALSE)
dataset.plot.indivisually<-cbind(dataset.transpose, wavelength,category)

#split data by categories for future use
flower.spec<-dataset.plot.indivisually[1:23547,]
leaf.spec<-dataset.plot.indivisually[23548:46593,]
beetle.spec<-dataset.plot.indivisually[46594:65130,]

#merge the spectra before plot here
dataset.plot.indivisually$category2<-factor(dataset.plot.indivisually$category, levels=c("leaf","flower","beetle"))

#plot the spectra of the targets used in this model
# ggplot(dataset.plot.indivisually,aes(x=wavelength,y=reflectance, colour=category2, group=species))+
#   geom_point(size=.05)+
#   geom_line(size=.05)+
#   scale_color_manual( values = c( "forestgreen", "palevioletred1","cornflowerblue"))+
#   facet_grid(category2 ~ .)+
#   xlab("Wavelength (nm)")+ylab("Reflectance (%)")+
#   scale_fill_discrete(name="sample type")+
#   theme(legend.position = "none")+
#   theme_classic()
```

```{r, fig.cap="Figure caption: Vis 580 was used for the sensitivity analysis" ,echo=FALSE,message=FALSE, warning=FALSE}
#plot the visual sensitivity curves
wl<-specsensbuprest.model2[,1]
peaks<-gather(specsensbuprest.model2[,2:9], peak, value) %>% cbind(wl)

peak.order <- c("UVS.380.A1.", "SWS.460.A1.", "MWS.520.A1.", "LWS.570.A1..filter580.","LWS.570.A1..filter600.","LWS.570.A1..filter620.","LWS.570.A1..filter640.","LWS.570.A1..filter660.") #to order the peaks in the legend
ggplot(peaks,aes(x=wl, y=value, col=peak))+
  geom_line()+
  guides(color=guide_legend(title="peak sensitivity"))+
  scale_color_manual(
    values = c("darkorchid4", "dodgerblue3", "olivedrab4", "orange1", "orange3","darkorange3", "orangered1", "red2"),
    labels=c("380 nm", "460 nm","520 nm", "580 nm", "600 nm", "620 nm", "640 nm", "660 nm"),
    breaks=peak.order)+
  xlab("Wavelength (nm)")+
  ylab("Relative spectral sensitivity")+
  theme_classic()

```

</br>
</br>

#Data description

We used the same spectral data collected from beetles and plants as described in the [Main models](main_models.html) section.

</br>
</br>

#Run the visual models
We created 3 different visual systems using different receptor ratios from 3 insect species (UVS, SWS, MWS, LWS):

+ _Agrilus planipennis_: 1.14, 1, 1.26, 1.38
+ _Papilio xuthus_: 1, 1, 4.08, 2.92
+ _Heliconius_ sp. type III : 1, 1.44, 2.22, 11.11 
    
</br>
</br>

##First: Quantum catch calculation
* We used the `vismodel` function in the package pavo to calculate quantum catch.
* For each visual system, quantum catch was calculated based on Fechner's law (the signal of the receptor channel is proportional to the logarithm of the quantum catch).
* The average of all leaf spectra was used as the background adapting light.
* The von Kries chromatic adaptation was applied.
```{r,message=FALSE}
#Quantum catch - D65 - Visual model 2
#shared between 3 species
buprest580=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, 1:5], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest600=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,6)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest620=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,7)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest640=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,8)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
buprest660=vismodel(dataset[1:501,], visual = specsensbuprest.model2[, c(1,2,3,4,9)], bkg=aveleaf$aveleaf, illum = irradiance.d65[1:501,2], qcatch = 'fi', relative=FALSE, vonkries=TRUE)
```

##Second: Contrast calculation
* To calculate chromatic contrast we used the `coldist` function in pavo.
* We used a neural noise-limited model where the noise is proportional to the Weber fraction and is independent of the intensity of the signal received.
* The Weber fraction was 0.1.

```{r,message=FALSE}
#Contrast calculation- D65 - Visual model 2
#for Agrilus planipennis
Cbuprest580 = coldist(buprest580, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest600 = coldist(buprest600, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest620 = coldist(buprest620, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest640 = coldist(buprest640, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)
Cbuprest660 = coldist(buprest660, noise="neural", achro=FALSE, n = c(1.14,1,1.26,1.38), weber = 0.1, weber.ref = 4)

#for Papilio xuthus
Cpapilio580 = coldist(buprest580, noise="neural", achro=FALSE, n = c(1, 1, 4.08, 2.92), weber = 0.1, weber.ref = 4)
Cpapilio600 = coldist(buprest600, noise="neural", achro=FALSE, n = c(1, 1, 4.08, 2.92), weber = 0.1, weber.ref = 4)
Cpapilio620 = coldist(buprest620, noise="neural", achro=FALSE, n = c(1, 1, 4.08, 2.92), weber = 0.1, weber.ref = 4)
Cpapilio640 = coldist(buprest640, noise="neural", achro=FALSE, n = c(1, 1, 4.08, 2.92), weber = 0.1, weber.ref = 4)
Cpapilio660 = coldist(buprest660, noise="neural", achro=FALSE, n = c(1, 1, 4.08, 2.92), weber = 0.1, weber.ref = 4)

#for Heliconius sp
Cheliconius580 = coldist(buprest580, noise="neural", achro=FALSE, n = c(1, 1.44, 2.22, 11.11), weber = 0.1, weber.ref = 4)
Cheliconius600 = coldist(buprest600, noise="neural", achro=FALSE, n = c(1, 1.44, 2.22, 11.11), weber = 0.1, weber.ref = 4)
Cheliconius620 = coldist(buprest620, noise="neural", achro=FALSE, n = c(1, 1.44, 2.22, 11.11), weber = 0.1, weber.ref = 4)
Cheliconius640 = coldist(buprest640, noise="neural", achro=FALSE, n = c(1, 1.44, 2.22, 11.11), weber = 0.1, weber.ref = 4)
Cheliconius660 = coldist(buprest660, noise="neural", achro=FALSE, n = c(1, 1.44, 2.22, 11.11), weber = 0.1, weber.ref = 4)
```

#Compare contrasts {.tabset .tabset-fade .tabset-pills}

```{r} 
#creat different comparison groups for furthur GLMM analysis
#Organize data before GLMM

#for Agrilus planipennis
##flower vs leaf
Cbuprest580.leaf.vs.flower=
  Cbuprest580 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest600.leaf.vs.flower=
  Cbuprest600 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest620.leaf.vs.flower=
  Cbuprest620 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest640.leaf.vs.flower=
  Cbuprest640 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cbuprest660.leaf.vs.flower=
  Cbuprest660 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

Cbuprest.leaf.vs.flower=
  Cbuprest580.leaf.vs.flower %>% rbind(Cbuprest600.leaf.vs.flower) %>%
  rbind(Cbuprest620.leaf.vs.flower)%>% rbind(Cbuprest640.leaf.vs.flower) %>% rbind(Cbuprest660.leaf.vs.flower) 

bup580.leaf.vs.flower<-Cbuprest580.leaf.vs.flower[,3]
bup600.leaf.vs.flower<-Cbuprest600.leaf.vs.flower[,3]
bup620.leaf.vs.flower<-Cbuprest620.leaf.vs.flower[,3]
bup640.leaf.vs.flower<-Cbuprest640.leaf.vs.flower[,3]
bup660.leaf.vs.flower<-Cbuprest660.leaf.vs.flower[,3]

com.bupcontrast.leaf.vs.flower<-cbind(Cbuprest.leaf.vs.flower[,1:2],bup580.leaf.vs.flower,bup600.leaf.vs.flower,bup620.leaf.vs.flower,bup640.leaf.vs.flower,bup660.leaf.vs.flower)
compare.leaf.vs.flower.bup <- com.bupcontrast.leaf.vs.flower %>%
  gather(key = "peak_wl.leaf.vs.flower", value = "dS", 3:7)

##beetle vs leaf
Cbuprest580.leaf.vs.beetle=
  Cbuprest580 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest600.leaf.vs.beetle=
  Cbuprest600 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest620.leaf.vs.beetle=
  Cbuprest620 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest640.leaf.vs.beetle=
  Cbuprest640 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest660.leaf.vs.beetle=
  Cbuprest660 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

Cbuprest.leaf.vs.beetle=
  Cbuprest580.leaf.vs.beetle  %>% rbind(Cbuprest600.leaf.vs.beetle)%>%
  rbind(Cbuprest620.leaf.vs.beetle)%>% rbind(Cbuprest640.leaf.vs.beetle) %>% rbind(Cbuprest660.leaf.vs.beetle) 

bup580.leaf.vs.beetle<-Cbuprest580.leaf.vs.beetle[,3]
bup600.leaf.vs.beetle<-Cbuprest600.leaf.vs.beetle[,3]
bup620.leaf.vs.beetle<-Cbuprest620.leaf.vs.beetle[,3]
bup640.leaf.vs.beetle<-Cbuprest640.leaf.vs.beetle[,3]
bup660.leaf.vs.beetle<-Cbuprest660.leaf.vs.beetle[,3]

com.bupcontrast.leaf.vs.beetle<-cbind(Cbuprest.leaf.vs.beetle[,1:2],bup580.leaf.vs.beetle,bup600.leaf.vs.beetle,bup620.leaf.vs.beetle,bup640.leaf.vs.beetle,bup660.leaf.vs.beetle)
compare.leaf.vs.beetle.bup <- com.bupcontrast.leaf.vs.beetle %>%
  gather(key = "peak_wl.leaf.vs.beetle", value = "dS", 3:7)

##beetle vs flower
Cbuprest580.flower.vs.beetle=
  Cbuprest580 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest600.flower.vs.beetle=
  Cbuprest600 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest620.flower.vs.beetle=
  Cbuprest620 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest640.flower.vs.beetle=
  Cbuprest640 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cbuprest660.flower.vs.beetle=
  Cbuprest660 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

Cbuprest.flower.vs.beetle=
  Cbuprest580.flower.vs.beetle %>% rbind(Cbuprest600.flower.vs.beetle) %>% 
  rbind(Cbuprest620.flower.vs.beetle)%>% rbind(Cbuprest640.flower.vs.beetle) %>% 
  rbind(Cbuprest660.flower.vs.beetle)

bup580.flower.vs.beetle<-Cbuprest580.flower.vs.beetle[,3]
bup600.flower.vs.beetle<-Cbuprest600.flower.vs.beetle[,3]
bup620.flower.vs.beetle<-Cbuprest620.flower.vs.beetle[,3]
bup640.flower.vs.beetle<-Cbuprest640.flower.vs.beetle[,3]
bup660.flower.vs.beetle<-Cbuprest660.flower.vs.beetle[,3]

com.bupcontrast.flower.vs.beetle<-cbind(Cbuprest.flower.vs.beetle[,1:2],bup580.flower.vs.beetle,bup600.flower.vs.beetle,bup620.flower.vs.beetle,bup640.flower.vs.beetle,bup660.flower.vs.beetle)
compare.flower.vs.beetle.bup <- com.bupcontrast.flower.vs.beetle %>%
  gather(key = "peak_wl.flower.vs.beetle", value = "dS", 3:7)




#for Papilio xuthus
##flower vs leaf
Cpapilio580.leaf.vs.flower=
  Cpapilio580 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cpapilio600.leaf.vs.flower=
  Cpapilio600 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cpapilio620.leaf.vs.flower=
  Cpapilio620 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cpapilio640.leaf.vs.flower=
  Cpapilio640 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cpapilio660.leaf.vs.flower=
  Cpapilio660 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

Cpapilio.leaf.vs.flower=
  Cpapilio580.leaf.vs.flower %>% rbind(Cpapilio600.leaf.vs.flower) %>%
  rbind(Cpapilio620.leaf.vs.flower)%>% rbind(Cpapilio640.leaf.vs.flower) %>% rbind(Cpapilio660.leaf.vs.flower) 

pap580.leaf.vs.flower<-Cpapilio580.leaf.vs.flower[,3]
pap600.leaf.vs.flower<-Cpapilio600.leaf.vs.flower[,3]
pap620.leaf.vs.flower<-Cpapilio620.leaf.vs.flower[,3]
pap640.leaf.vs.flower<-Cpapilio640.leaf.vs.flower[,3]
pap660.leaf.vs.flower<-Cpapilio660.leaf.vs.flower[,3]

com.papcontrast.leaf.vs.flower<-cbind(Cpapilio.leaf.vs.flower[,1:2],pap580.leaf.vs.flower,pap600.leaf.vs.flower,pap620.leaf.vs.flower,pap640.leaf.vs.flower,pap660.leaf.vs.flower)
compare.leaf.vs.flower.pap <- com.papcontrast.leaf.vs.flower %>%
  gather(key = "peak_wl.leaf.vs.flower", value = "dS", 3:7)

##beetle vs leaf
Cpapilio580.leaf.vs.beetle=
  Cpapilio580 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cpapilio600.leaf.vs.beetle=
  Cpapilio600 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cpapilio620.leaf.vs.beetle=
  Cpapilio620 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cpapilio640.leaf.vs.beetle=
  Cpapilio640 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cpapilio660.leaf.vs.beetle=
  Cpapilio660 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

Cpapilio.leaf.vs.beetle=
  Cpapilio580.leaf.vs.beetle  %>% rbind(Cpapilio600.leaf.vs.beetle)%>%
  rbind(Cpapilio620.leaf.vs.beetle)%>% rbind(Cpapilio640.leaf.vs.beetle) %>% rbind(Cpapilio660.leaf.vs.beetle) 

pap580.leaf.vs.beetle<-Cpapilio580.leaf.vs.beetle[,3]
pap600.leaf.vs.beetle<-Cpapilio600.leaf.vs.beetle[,3]
pap620.leaf.vs.beetle<-Cpapilio620.leaf.vs.beetle[,3]
pap640.leaf.vs.beetle<-Cpapilio640.leaf.vs.beetle[,3]
pap660.leaf.vs.beetle<-Cpapilio660.leaf.vs.beetle[,3]

com.papcontrast.leaf.vs.beetle<-cbind(Cpapilio.leaf.vs.beetle[,1:2],pap580.leaf.vs.beetle,pap600.leaf.vs.beetle,pap620.leaf.vs.beetle,pap640.leaf.vs.beetle,pap660.leaf.vs.beetle)
compare.leaf.vs.beetle.pap <- com.papcontrast.leaf.vs.beetle %>%
  gather(key = "peak_wl.leaf.vs.beetle", value = "dS", 3:7)

##beetle vs flower
Cpapilio580.flower.vs.beetle=
  Cpapilio580 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cpapilio600.flower.vs.beetle=
  Cpapilio600 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cpapilio620.flower.vs.beetle=
  Cpapilio620 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cpapilio640.flower.vs.beetle=
  Cpapilio640 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cpapilio660.flower.vs.beetle=
  Cpapilio660 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

Cpapilio.flower.vs.beetle=
  Cpapilio580.flower.vs.beetle %>% rbind(Cpapilio600.flower.vs.beetle) %>% 
  rbind(Cpapilio620.flower.vs.beetle)%>% rbind(Cpapilio640.flower.vs.beetle) %>% 
  rbind(Cpapilio660.flower.vs.beetle)

pap580.flower.vs.beetle<-Cpapilio580.flower.vs.beetle[,3]
pap600.flower.vs.beetle<-Cpapilio600.flower.vs.beetle[,3]
pap620.flower.vs.beetle<-Cpapilio620.flower.vs.beetle[,3]
pap640.flower.vs.beetle<-Cpapilio640.flower.vs.beetle[,3]
pap660.flower.vs.beetle<-Cpapilio660.flower.vs.beetle[,3]

com.papcontrast.flower.vs.beetle<-cbind(Cpapilio.flower.vs.beetle[,1:2],pap580.flower.vs.beetle,pap600.flower.vs.beetle,pap620.flower.vs.beetle,pap640.flower.vs.beetle,pap660.flower.vs.beetle)
compare.flower.vs.beetle.pap <- com.papcontrast.flower.vs.beetle %>%
  gather(key = "peak_wl.flower.vs.beetle", value = "dS", 3:7)



#for Heliconius sp
##flower vs leaf
Cheliconius580.leaf.vs.flower=
  Cheliconius580 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cheliconius600.leaf.vs.flower=
  Cheliconius600 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cheliconius620.leaf.vs.flower=
  Cheliconius620 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cheliconius640.leaf.vs.flower=
  Cheliconius640 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))
Cheliconius660.leaf.vs.flower=
  Cheliconius660 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "leaves"))

Cheliconius.leaf.vs.flower=
  Cheliconius580.leaf.vs.flower %>% rbind(Cheliconius600.leaf.vs.flower) %>%
  rbind(Cheliconius620.leaf.vs.flower)%>% rbind(Cheliconius640.leaf.vs.flower) %>% rbind(Cheliconius660.leaf.vs.flower) 

heli580.leaf.vs.flower<-Cheliconius580.leaf.vs.flower[,3]
heli600.leaf.vs.flower<-Cheliconius600.leaf.vs.flower[,3]
heli620.leaf.vs.flower<-Cheliconius620.leaf.vs.flower[,3]
heli640.leaf.vs.flower<-Cheliconius640.leaf.vs.flower[,3]
heli660.leaf.vs.flower<-Cheliconius660.leaf.vs.flower[,3]

com.helicontrast.leaf.vs.flower<-cbind(Cheliconius.leaf.vs.flower[,1:2],heli580.leaf.vs.flower,heli600.leaf.vs.flower,heli620.leaf.vs.flower,heli640.leaf.vs.flower,heli660.leaf.vs.flower)
compare.leaf.vs.flower.heli <- com.helicontrast.leaf.vs.flower %>%
  gather(key = "peak_wl.leaf.vs.flower", value = "dS", 3:7)

##beetle vs leaf
Cheliconius580.leaf.vs.beetle=
  Cheliconius580 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cheliconius600.leaf.vs.beetle=
  Cheliconius600 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cheliconius620.leaf.vs.beetle=
  Cheliconius620 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cheliconius640.leaf.vs.beetle=
  Cheliconius640 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))
Cheliconius660.leaf.vs.beetle=
  Cheliconius660 %>%filter(str_detect(patch1, "leaves")) %>% filter(str_detect(patch2, "beetle"))

Cheliconius.leaf.vs.beetle=
  Cheliconius580.leaf.vs.beetle  %>% rbind(Cheliconius600.leaf.vs.beetle)%>%
  rbind(Cheliconius620.leaf.vs.beetle)%>% rbind(Cheliconius640.leaf.vs.beetle) %>% rbind(Cheliconius660.leaf.vs.beetle) 

heli580.leaf.vs.beetle<-Cheliconius580.leaf.vs.beetle[,3]
heli600.leaf.vs.beetle<-Cheliconius600.leaf.vs.beetle[,3]
heli620.leaf.vs.beetle<-Cheliconius620.leaf.vs.beetle[,3]
heli640.leaf.vs.beetle<-Cheliconius640.leaf.vs.beetle[,3]
heli660.leaf.vs.beetle<-Cheliconius660.leaf.vs.beetle[,3]

com.helicontrast.leaf.vs.beetle<-cbind(Cheliconius.leaf.vs.beetle[,1:2],heli580.leaf.vs.beetle,heli600.leaf.vs.beetle,heli620.leaf.vs.beetle,heli640.leaf.vs.beetle,heli660.leaf.vs.beetle)
compare.leaf.vs.beetle.heli <- com.helicontrast.leaf.vs.beetle %>%
  gather(key = "peak_wl.leaf.vs.beetle", value = "dS", 3:7)

##beetle vs flower
Cheliconius580.flower.vs.beetle=
  Cheliconius580 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cheliconius600.flower.vs.beetle=
  Cheliconius600 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cheliconius620.flower.vs.beetle=
  Cheliconius620 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cheliconius640.flower.vs.beetle=
  Cheliconius640 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))
Cheliconius660.flower.vs.beetle=
  Cheliconius660 %>%filter(str_detect(patch1, "flower")) %>% filter(str_detect(patch2, "beetle"))

Cheliconius.flower.vs.beetle=
  Cheliconius580.flower.vs.beetle %>% rbind(Cheliconius600.flower.vs.beetle) %>% 
  rbind(Cheliconius620.flower.vs.beetle)%>% rbind(Cheliconius640.flower.vs.beetle) %>% 
  rbind(Cheliconius660.flower.vs.beetle)

heli580.flower.vs.beetle<-Cheliconius580.flower.vs.beetle[,3]
heli600.flower.vs.beetle<-Cheliconius600.flower.vs.beetle[,3]
heli620.flower.vs.beetle<-Cheliconius620.flower.vs.beetle[,3]
heli640.flower.vs.beetle<-Cheliconius640.flower.vs.beetle[,3]
heli660.flower.vs.beetle<-Cheliconius660.flower.vs.beetle[,3]

com.helicontrast.flower.vs.beetle<-cbind(Cheliconius.flower.vs.beetle[,1:2],heli580.flower.vs.beetle,heli600.flower.vs.beetle,heli620.flower.vs.beetle,heli640.flower.vs.beetle,heli660.flower.vs.beetle)
compare.flower.vs.beetle.heli <- com.helicontrast.flower.vs.beetle%>%
  gather(key = "peak_wl.flower.vs.beetle", value = "dS", 3:7)
```
</br>
</br>

* To compare contrasts between visual systems, We conducted Wald chi-square tests on generalised linear mixed models (GLMM) followed by posthoc tests.

* In the models, we assigned
    + Independent variable: __contrast__
    + Dependent variable: 
        + Fixed factor: __visual system__
        + Random factor: __sample ID__ of both targets in the comparison
</br>
</br>

Click the tabs to see the results for each comparison group ( __Leaf vs. Flower__ / __Leaf vs. Beetle__ / __Beetle vs. Flower__) 

```{r}
#for Agrilus planipennis
##Leaf vs Flower
m.leaf.vs.flower.bup <- lmer(dS~peak_wl.leaf.vs.flower + (1|patch2) + (1|patch1), data = compare.leaf.vs.flower.bup,REML=F)
sum.leaf.vs.flower.bup <- summary(glht(m.leaf.vs.flower.bup, linfct = mcp(peak_wl.leaf.vs.flower = "Tukey")), test = adjusted("bonferroni"))
##Leaf vs Beetle
m.leaf.vs.beetle.bup <- lmer(dS~peak_wl.leaf.vs.beetle + (1|patch2) + (1|patch1), data = compare.leaf.vs.beetle.bup,REML=F)
sum.leaf.vs.beetle.bup <- summary(glht(m.leaf.vs.beetle.bup, linfct = mcp(peak_wl.leaf.vs.beetle = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Flower
m.flower.vs.beetle.bup <- lmer(dS~peak_wl.flower.vs.beetle + (1|patch2) + (1|patch1), data = compare.flower.vs.beetle.bup,REML=F)
sum.flower.vs.beetle.bup <- summary(glht(m.flower.vs.beetle.bup, linfct = mcp(peak_wl.flower.vs.beetle = "Tukey")), test = adjusted("bonferroni"))

###reshape data for heatmap
p1.bup<-sum.leaf.vs.flower.bup[["test"]][["pvalues"]]
p2.bup<-sum.leaf.vs.beetle.bup[["test"]][["pvalues"]]
p3.bup<-sum.flower.vs.beetle.bup[["test"]][["pvalues"]]

VislistA.bup<-c("Vis 600","Vis 620","Vis 640","Vis 660","Vis 620","Vis 640","Vis 660","Vis 640","Vis 660","Vis 660")
VislistB.bup<-c("Vis 580","Vis 580","Vis 580","Vis 580","Vis 600","Vis 600","Vis 600","Vis 620","Vis 620","Vis 640")

heat.bup<-data.frame(names(p1.bup),as.numeric(str_extract(p1.bup,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2.bup,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3.bup,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, leaf.vs.flower = 2, leaf.vs.beetle = 3, flower.vs.beetle = 4) %>% 
  cbind(VislistA.bup) %>% 
  cbind(VislistB.bup) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat.bup$sig.leaf.vs.flower[heat.bup$leaf.vs.flower > 0.05] <- ""
heat.bup$sig.leaf.vs.flower[heat.bup$leaf.vs.flower < 0.05] <- "*"
heat.bup$sig.leaf.vs.flower[heat.bup$leaf.vs.flower < 0.01] <- "**"
heat.bup$sig.leaf.vs.flower[heat.bup$leaf.vs.flower < 0.0001] <- "***"
heat.bup$sig.leaf.vs.beetle[heat.bup$leaf.vs.beetle > 0.05] <- ""
heat.bup$sig.leaf.vs.beetle[heat.bup$leaf.vs.beetle < 0.05] <- "*"
heat.bup$sig.leaf.vs.beetle[heat.bup$leaf.vs.beetle < 0.01] <- "**"
heat.bup$sig.leaf.vs.beetle[heat.bup$leaf.vs.beetle < 0.0001] <- "***"
heat.bup$sig.flower.vs.beetle[heat.bup$flower.vs.beetle > 0.05] <- ""
heat.bup$sig.flower.vs.beetle[heat.bup$flower.vs.beetle < 0.05] <- "*"
heat.bup$sig.flower.vs.beetle[heat.bup$flower.vs.beetle < 0.01] <- "**"
heat.bup$sig.flower.vs.beetle[heat.bup$flower.vs.beetle < 0.0001] <- "***"



#for Papilio xuthus
##Leaf vs Flower
m.leaf.vs.flower.pap <- lmer(dS~peak_wl.leaf.vs.flower + (1|patch2) + (1|patch1), data = compare.leaf.vs.flower.pap,REML=F)
sum.leaf.vs.flower.pap <- summary(glht(m.leaf.vs.flower.pap, linfct = mcp(peak_wl.leaf.vs.flower = "Tukey")), test = adjusted("bonferroni"))
##Leaf vs Beetle
m.leaf.vs.beetle.pap <- lmer(dS~peak_wl.leaf.vs.beetle + (1|patch2) + (1|patch1), data = compare.leaf.vs.beetle.pap,REML=F)
sum.leaf.vs.beetle.pap <- summary(glht(m.leaf.vs.beetle.pap, linfct = mcp(peak_wl.leaf.vs.beetle = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Flower
m.flower.vs.beetle.pap <- lmer(dS~peak_wl.flower.vs.beetle + (1|patch2) + (1|patch1), data = compare.flower.vs.beetle.pap,REML=F)
sum.flower.vs.beetle.pap <- summary(glht(m.flower.vs.beetle.pap, linfct = mcp(peak_wl.flower.vs.beetle = "Tukey")), test = adjusted("bonferroni"))

###reshape data for heatmap
p1.pap<-sum.leaf.vs.flower.pap[["test"]][["pvalues"]]
p2.pap<-sum.leaf.vs.beetle.pap[["test"]][["pvalues"]]
p3.pap<-sum.flower.vs.beetle.pap[["test"]][["pvalues"]]

VislistA.pap<-c("Vis 600","Vis 620","Vis 640","Vis 660","Vis 620","Vis 640","Vis 660","Vis 640","Vis 660","Vis 660")
VislistB.pap<-c("Vis 580","Vis 580","Vis 580","Vis 580","Vis 600","Vis 600","Vis 600","Vis 620","Vis 620","Vis 640")

heat.pap<-data.frame(names(p1.pap),as.numeric(str_extract(p1.pap,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2.pap,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3.pap,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, leaf.vs.flower = 2, leaf.vs.beetle = 3, flower.vs.beetle = 4) %>% 
  cbind(VislistA.pap) %>% 
  cbind(VislistB.pap) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat.pap$sig.leaf.vs.flower[heat.pap$leaf.vs.flower > 0.05] <- ""
heat.pap$sig.leaf.vs.flower[heat.pap$leaf.vs.flower < 0.05] <- "*"
heat.pap$sig.leaf.vs.flower[heat.pap$leaf.vs.flower < 0.01] <- "**"
heat.pap$sig.leaf.vs.flower[heat.pap$leaf.vs.flower < 0.0001] <- "***"
heat.pap$sig.leaf.vs.beetle[heat.pap$leaf.vs.beetle > 0.05] <- ""
heat.pap$sig.leaf.vs.beetle[heat.pap$leaf.vs.beetle < 0.05] <- "*"
heat.pap$sig.leaf.vs.beetle[heat.pap$leaf.vs.beetle < 0.01] <- "**"
heat.pap$sig.leaf.vs.beetle[heat.pap$leaf.vs.beetle < 0.0001] <- "***"
heat.pap$sig.flower.vs.beetle[heat.pap$flower.vs.beetle > 0.05] <- ""
heat.pap$sig.flower.vs.beetle[heat.pap$flower.vs.beetle < 0.05] <- "*"
heat.pap$sig.flower.vs.beetle[heat.pap$flower.vs.beetle < 0.01] <- "**"
heat.pap$sig.flower.vs.beetle[heat.pap$flower.vs.beetle < 0.0001] <- "***"



#for Heliconius sp
##Leaf vs Flower
m.leaf.vs.flower.heli <- lmer(dS~peak_wl.leaf.vs.flower + (1|patch2) + (1|patch1), data = compare.leaf.vs.flower.heli,REML=F)
sum.leaf.vs.flower.heli <- summary(glht(m.leaf.vs.flower.heli, linfct = mcp(peak_wl.leaf.vs.flower = "Tukey")), test = adjusted("bonferroni"))
##Leaf vs Beetle
m.leaf.vs.beetle.heli <- lmer(dS~peak_wl.leaf.vs.beetle + (1|patch2) + (1|patch1), data = compare.leaf.vs.beetle.heli,REML=F)
sum.leaf.vs.beetle.heli <- summary(glht(m.leaf.vs.beetle.heli, linfct = mcp(peak_wl.leaf.vs.beetle = "Tukey")), test = adjusted("bonferroni"))
##Beetle vs Flower
m.flower.vs.beetle.heli <- lmer(dS~peak_wl.flower.vs.beetle + (1|patch2) + (1|patch1), data = compare.flower.vs.beetle.heli,REML=F)
sum.flower.vs.beetle.heli <- summary(glht(m.flower.vs.beetle.heli, linfct = mcp(peak_wl.flower.vs.beetle = "Tukey")), test = adjusted("bonferroni"))

###reshape data for heatmap
p1.heli<-sum.leaf.vs.flower.heli[["test"]][["pvalues"]]
p2.heli<-sum.leaf.vs.beetle.heli[["test"]][["pvalues"]]
p3.heli<-sum.flower.vs.beetle.heli[["test"]][["pvalues"]]

VislistA.heli<-c("Vis 600","Vis 620","Vis 640","Vis 660","Vis 620","Vis 640","Vis 660","Vis 640","Vis 660","Vis 660")
VislistB.heli<-c("Vis 580","Vis 580","Vis 580","Vis 580","Vis 600","Vis 600","Vis 600","Vis 620","Vis 620","Vis 640")

heat.heli<-data.frame(names(p1.heli),as.numeric(str_extract(p1.heli,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p2.heli,"([0-9]+).*$"))) %>% 
  cbind(as.numeric(str_extract(p3.heli,"([0-9]+).*$"))) %>%
  dplyr:: rename(orignial.list = 1, leaf.vs.flower = 2, leaf.vs.beetle = 3, flower.vs.beetle = 4) %>% 
  cbind(VislistA.heli) %>% 
  cbind(VislistB.heli) %>% 
  dplyr::select(-orignial.list)

##add asterisks for significant pairs
heat.heli$sig.leaf.vs.flower[heat.heli$leaf.vs.flower > 0.05] <- ""
heat.heli$sig.leaf.vs.flower[heat.heli$leaf.vs.flower < 0.05] <- "*"
heat.heli$sig.leaf.vs.flower[heat.heli$leaf.vs.flower < 0.01] <- "**"
heat.heli$sig.leaf.vs.flower[heat.heli$leaf.vs.flower < 0.0001] <- "***"
heat.heli$sig.leaf.vs.beetle[heat.heli$leaf.vs.beetle > 0.05] <- ""
heat.heli$sig.leaf.vs.beetle[heat.heli$leaf.vs.beetle < 0.05] <- "*"
heat.heli$sig.leaf.vs.beetle[heat.heli$leaf.vs.beetle < 0.01] <- "**"
heat.heli$sig.leaf.vs.beetle[heat.heli$leaf.vs.beetle < 0.0001] <- "***"
heat.heli$sig.flower.vs.beetle[heat.heli$flower.vs.beetle > 0.05] <- ""
heat.heli$sig.flower.vs.beetle[heat.heli$flower.vs.beetle < 0.05] <- "*"
heat.heli$sig.flower.vs.beetle[heat.heli$flower.vs.beetle < 0.01] <- "**"
heat.heli$sig.flower.vs.beetle[heat.heli$flower.vs.beetle < 0.0001] <- "***"
```

## __Leaf vs Flower__ {.tabset .tabset-fade .tabset-pills}

### _Agrilus planipennis_ {.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.flower.bup) %>% pander()
```

</br>
</br>

Click the tabs to see the __p-value summary plot__ or the __original model output__

#### Pair-wise p-values 
```{r}
ggplot(data = heat.bup, aes(x=VislistA.bup, y=VislistB.bup, fill=leaf.vs.flower)) + 
  geom_tile()+
  geom_text(aes(VislistA.bup, VislistB.bup, label = paste(format(round(leaf.vs.flower, 2), nsmall = 2), sig.leaf.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_minimal()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
```

</br>
</br>

#### Original model output
```{r}
sum.leaf.vs.flower.bup
```

</br>
</br>

### _Papilio xuthus_ {.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.flower.pap) %>% pander()
```

</br>
</br>

Click the tabs to see the __p-value summary plot__ or the __original model output__

#### Pair-wise p-values 
```{r}
ggplot(data = heat.pap, aes(x=VislistA.pap, y=VislistB.pap, fill=leaf.vs.flower)) + 
  geom_tile()+
  geom_text(aes(VislistA.pap, VislistB.pap, label = paste(format(round(leaf.vs.flower, 2), nsmall = 2), sig.leaf.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_minimal()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
```

</br>
</br>

#### Original model output
```{r}
sum.leaf.vs.flower.pap
```

</br>
</br>

### _Heliconius_ sp {.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.flower.heli) %>% pander()
```

</br>
</br>

Click the tabs to see the __p-value summary plot__ or the __original model output__

#### Pair-wise p-values 
```{r}
ggplot(data = heat.heli, aes(x=VislistA.heli, y=VislistB.heli, fill=leaf.vs.flower)) + 
  geom_tile()+
  geom_text(aes(VislistA.heli, VislistB.heli, label = paste(format(round(leaf.vs.flower, 2), nsmall = 2), sig.leaf.vs.flower)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_minimal()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
```

</br>
</br>

#### Original model output
```{r}
sum.leaf.vs.flower.heli
```

</br>
</br>

## __Leaf vs Beetle__ {.tabset .tabset-fade .tabset-pills}
### _Agrilus planipennis_ {.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.beetle.bup) %>% pander()
```

</br>
</br>

Click the tabs to see the __p-value summary plot__ or the __original model output__

#### Pair-wise p-values 
```{r}
ggplot(data = heat.bup, aes(x=VislistA.bup, y=VislistB.bup, fill=leaf.vs.beetle)) + 
  geom_tile()+
  geom_text(aes(VislistA.bup, VislistB.bup, label = paste(format(round(leaf.vs.beetle, 2), nsmall = 2), sig.leaf.vs.beetle))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_minimal()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
```

</br>
</br>

#### Original model output
```{r}
sum.leaf.vs.beetle.bup
```

</br>
</br>

### _Papilio xuthus_ {.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.leaf.vs.beetle.pap) %>% pander()
```

</br>
</br>

Click the tabs to see the __p-value summary plot__ or the __original model output__

#### Pair-wise p-values 
```{r}
ggplot(data = heat.pap, aes(x=VislistA.pap, y=VislistB.pap, fill=leaf.vs.beetle)) + 
  geom_tile()+
  geom_text(aes(VislistA.pap, VislistB.pap, label = paste(format(round(leaf.vs.beetle, 2), nsmall = 2), sig.leaf.vs.beetle))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_minimal()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
```

</br>
</br>

#### Original model output
```{r}
sum.leaf.vs.beetle.pap
```

</br>
</br>

### _Heliconius_ sp {.tabset .tabset-fade .tabset-pills}

```{r}
Anova(m.leaf.vs.beetle.heli) %>% pander()
```

</br>
</br>

Click the tabs to see the __p-value summary plot__ or the __original model output__

#### Pair-wise p-values 
```{r}
ggplot(data = heat.heli, aes(x=VislistA.heli, y=VislistB.heli, fill=leaf.vs.beetle)) + 
  geom_tile()+
  geom_text(aes(VislistA.heli, VislistB.heli, label = paste(format(round(leaf.vs.beetle, 2), nsmall = 2), sig.leaf.vs.beetle))) +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour
  theme_minimal()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
```

</br>
</br>

#### Original model output
```{r}
sum.leaf.vs.beetle.heli
```

</br>
</br>

## __Beetle vs Flower__ {.tabset .tabset-fade .tabset-pills}
### _Agrilus planipennis_ {.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.beetle.bup) %>% pander()
```

</br>
</br>

Click the tabs to see the __p-value summary plot__ or the __original model output__

#### Pair-wise p-values 
```{r}
ggplot(data = heat.bup, aes(x=VislistA.bup, y=VislistB.bup, fill=flower.vs.beetle)) + 
  geom_tile()+
  geom_text(aes(VislistA.bup, VislistB.bup, label = paste(format(round(flower.vs.beetle, 2), nsmall = 2), sig.flower.vs.beetle)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour 
  theme_minimal()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
```
</br>
</br>

#### Original model output
```{r}
sum.flower.vs.beetle.bup
```
</br>
</br>

### _Papilio xuthus_ {.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.beetle.pap) %>% pander()
```

</br>
</br>

Click the tabs to see the __p-value summary plot__ or the __original model output__

#### Pair-wise p-values 
```{r}
ggplot(data = heat.pap, aes(x=VislistA.pap, y=VislistB.pap, fill=flower.vs.beetle)) + 
  geom_tile()+
  geom_text(aes(VislistA.pap, VislistB.pap, label = paste(format(round(flower.vs.beetle, 2), nsmall = 2), sig.flower.vs.beetle)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour 
  theme_minimal()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
```

</br>
</br>

#### Original model output
```{r}
sum.flower.vs.beetle.pap
```

</br>
</br>

### _Heliconius_ sp {.tabset .tabset-fade .tabset-pills}
```{r}
Anova(m.flower.vs.beetle.heli) %>% pander()
```

</br>
</br>

Click the tabs to see the __p-value summary plot__ or the __original model output__

#### Pair-wise p-values 
```{r}
ggplot(data = heat.heli, aes(x=VislistA.heli, y=VislistB.heli, fill=flower.vs.beetle)) + 
  geom_tile()+
  geom_text(aes(VislistA.heli, VislistB.heli, label = paste(format(round(flower.vs.beetle, 2), nsmall = 2), sig.flower.vs.beetle)))+
  scale_fill_continuous(high = "#132B43", low = "#56B1F7", limit=c(0,1))+ #delete if want to reverse the colour 
  theme_minimal()+
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())
```

</br>
</br>

#### Original model output
```{r}
sum.flower.vs.beetle.heli
```

</br>
</br>


#Plot the contrasts {.tabset .tabset-fade .tabset-pills}
* Colours approximate human perception of either flower (left and right) or beetle (centre) colouration.
* Lines of the same colors connect the same sample
```{r}
#combine all contrast value in each comparison group
##for Agrilus planipennis
###flower vs leaf
Vis1.lf.bup<- Cbuprest580%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis1.lf.bup$vissys<-strrep("Vis1.lf",1)
Vis2.lf.bup<-Cbuprest600%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis2.lf.bup$vissys<-strrep("Vis2.lf",1)
Vis3.lf.bup<-Cbuprest620%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis3.lf.bup$vissys<-strrep("Vis3.lf",1)
Vis4.lf.bup<-Cbuprest640%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis4.lf.bup$vissys<-strrep("Vis4.lf",1)
Vis5.lf.bup<-Cbuprest660%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis5.lf.bup$vissys<-strrep("Vis5.lf",1)

allvis.lf.bup<-Vis1.lf.bup %>% rbind(Vis2.lf.bup) %>% rbind(Vis3.lf.bup) %>%
  rbind(Vis4.lf.bup) %>%rbind(Vis5.lf.bup) 

###beetle vs leaf
Vis1.lb.bup<- Cbuprest580%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis1.lb.bup$vissys<-strrep("Vis1.lb",1)
Vis2.lb.bup<-Cbuprest600%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis2.lb.bup$vissys<-strrep("Vis2.lb",1)
Vis3.lb.bup<-Cbuprest620%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis3.lb.bup$vissys<-strrep("Vis3.lb",1)
Vis4.lb.bup<-Cbuprest640%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis4.lb.bup$vissys<-strrep("Vis4.lb",1)
Vis5.lb.bup<-Cbuprest660%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis5.lb.bup$vissys<-strrep("Vis5.lb",1)

allvis.lb.bup<-Vis1.lb.bup %>% rbind(Vis2.lb.bup) %>% rbind(Vis3.lb.bup) %>%
  rbind(Vis4.lb.bup) %>%rbind(Vis5.lb.bup)

###beetle vs flower
Vis1.bf.bup<- Cbuprest580%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis1.bf.bup$vissys<-strrep("Vis1.bf",1)
Vis2.bf.bup<-Cbuprest600%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis2.bf.bup$vissys<-strrep("Vis2.bf",1)
Vis3.bf.bup<-Cbuprest620%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis3.bf.bup$vissys<-strrep("Vis3.bf",1)
Vis4.bf.bup<-Cbuprest640%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis4.bf.bup$vissys<-strrep("Vis4.bf",1)
Vis5.bf.bup<-Cbuprest660%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis5.bf.bup$vissys<-strrep("Vis5.bf",1)

allvis.bf.bup<-Vis1.bf.bup %>% rbind(Vis2.bf.bup) %>% rbind(Vis3.bf.bup) %>%
  rbind(Vis4.bf.bup) %>%rbind(Vis5.bf.bup) 



##for Papilio xuthus
###flower vs leaf
Vis1.lf.pap<- Cpapilio580%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis1.lf.pap$vissys<-strrep("Vis1.lf",1)
Vis2.lf.pap<-Cpapilio600%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis2.lf.pap$vissys<-strrep("Vis2.lf",1)
Vis3.lf.pap<-Cpapilio620%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis3.lf.pap$vissys<-strrep("Vis3.lf",1)
Vis4.lf.pap<-Cpapilio640%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis4.lf.pap$vissys<-strrep("Vis4.lf",1)
Vis5.lf.pap<-Cpapilio660%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis5.lf.pap$vissys<-strrep("Vis5.lf",1)


allvis.lf.pap<-Vis1.lf.pap %>% rbind(Vis2.lf.pap) %>% rbind(Vis3.lf.pap) %>%
  rbind(Vis4.lf.pap) %>% rbind(Vis5.lf.pap) 

###beetle vs leaf
Vis1.lb.pap<- Cpapilio580%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis1.lb.pap$vissys<-strrep("Vis1.lb",1)
Vis2.lb.pap<-Cpapilio600%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis2.lb.pap$vissys<-strrep("Vis2.lb",1)
Vis3.lb.pap<-Cpapilio620%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis3.lb.pap$vissys<-strrep("Vis3.lb",1)
Vis4.lb.pap<-Cpapilio640%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis4.lb.pap$vissys<-strrep("Vis4.lb",1)
Vis5.lb.pap<-Cpapilio660%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis5.lb.pap$vissys<-strrep("Vis5.lb",1)


allvis.lb.pap<-Vis1.lb.pap %>% rbind(Vis2.lb.pap) %>% rbind(Vis3.lb.pap) %>%
  rbind(Vis4.lb.pap) %>% rbind(Vis5.lb.pap) 

###beetle vs flower
Vis1.bf.pap<- Cpapilio580%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis1.bf.pap$vissys<-strrep("Vis1.bf",1)
Vis2.bf.pap<-Cpapilio600%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis2.bf.pap$vissys<-strrep("Vis2.bf",1)
Vis3.bf.pap<-Cpapilio620%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis3.bf.pap$vissys<-strrep("Vis3.bf",1)
Vis4.bf.pap<-Cpapilio640%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis4.bf.pap$vissys<-strrep("Vis4.bf",1)
Vis5.bf.pap<-Cpapilio660%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis5.bf.pap$vissys<-strrep("Vis5.bf",1)

allvis.bf.pap<-Vis1.bf.pap %>% rbind(Vis2.bf.pap) %>% rbind(Vis3.bf.pap) %>%
  rbind(Vis4.bf.pap) %>% rbind(Vis5.bf.pap) 




##for Heliconius sp
###flower vs leaf
Vis1.lf.heli<- Cheliconius580%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis1.lf.heli$vissys<-strrep("Vis1.lf",1)
Vis2.lf.heli<-Cheliconius600%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis2.lf.heli$vissys<-strrep("Vis2.lf",1)
Vis3.lf.heli<-Cheliconius620%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis3.lf.heli$vissys<-strrep("Vis3.lf",1)
Vis4.lf.heli<-Cheliconius640%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis4.lf.heli$vissys<-strrep("Vis4.lf",1)
Vis5.lf.heli<-Cheliconius660%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"leaves"))
Vis5.lf.heli$vissys<-strrep("Vis5.lf",1)


allvis.lf.heli<-Vis1.lf.heli %>% rbind(Vis2.lf.heli) %>% rbind(Vis3.lf.heli) %>%
  rbind(Vis4.lf.heli) %>% rbind(Vis5.lf.heli) 

###beetle vs leaf
Vis1.lb.heli<- Cheliconius580%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis1.lb.heli$vissys<-strrep("Vis1.lb",1)
Vis2.lb.heli<-Cheliconius600%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis2.lb.heli$vissys<-strrep("Vis2.lb",1)
Vis3.lb.heli<-Cheliconius620%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis3.lb.heli$vissys<-strrep("Vis3.lb",1)
Vis4.lb.heli<-Cheliconius640%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis4.lb.heli$vissys<-strrep("Vis4.lb",1)
Vis5.lb.heli<-Cheliconius660%>% filter(str_detect(patch2,"beetle")) %>% 
  filter(str_detect(patch1,"leaves"))
Vis5.lb.heli$vissys<-strrep("Vis5.lb",1)


allvis.lb.heli<-Vis1.lb.heli %>% rbind(Vis2.lb.heli) %>% rbind(Vis3.lb.heli) %>%
  rbind(Vis4.lb.heli) %>% rbind(Vis5.lb.heli) 

###beetle vs flower
Vis1.bf.heli<- Cheliconius580%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis1.bf.heli$vissys<-strrep("Vis1.bf",1)
Vis2.bf.heli<-Cheliconius600%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis2.bf.heli$vissys<-strrep("Vis2.bf",1)
Vis3.bf.heli<-Cheliconius620%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis3.bf.heli$vissys<-strrep("Vis3.bf",1)
Vis4.bf.heli<-Cheliconius640%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis4.bf.heli$vissys<-strrep("Vis4.bf",1)
Vis5.bf.heli<-Cheliconius660%>% filter(str_detect(patch1,"flower")) %>% 
  filter(str_detect(patch2,"beetle"))
Vis5.bf.heli$vissys<-strrep("Vis5.bf",1)

allvis.bf.heli<-Vis1.bf.heli %>% rbind(Vis2.bf.heli) %>% rbind(Vis3.bf.heli) %>%
  rbind(Vis4.bf.heli) %>% rbind(Vis5.bf.heli) 
```

```{r}
#import the flower color code 
color.code<-read.csv("data/color code list.csv",header=TRUE) 

#creat a list of species name used in the spec data and 
name.list<-unique(dataset.transpose$species) %>% 
  sort() %>% #order it alphebatically as well
  data.frame() %>% dplyr::rename(species = ".")#make it a data frame and name the column "species"

#creat flower name list
flower.colour <- name.list %>% filter(str_detect(species, "flower")) %>% #select flower names
  cbind(color.code %>% filter(str_detect(type, "flower")) %>% arrange(name)) %>% #select flower color codes and order it alphebatically
  dplyr::select(-type) %>% #remove the redundant column
  mutate(count = 5) %>% uncount(count) #repeat each row for 5 times for 5 visual systems

#creat beetle name list

beetle.colour<- name.list %>% filter(str_detect(species, "beetle")) %>% #select flower names
  cbind(color.code %>% filter(str_detect(type, "beetle")) %>% arrange(name)) %>% #select flower color codes and order it alphebatically
  dplyr::select(-type) %>% #remove the redundant column
  mutate(count = 5) %>% uncount(count) #repeat each row for 5 times for 5 visual systems
```

## _Agrilus planipennis_
```{r}
#make flower vs leaf plot
##add the mean
mean.lf.bup<-allvis.lf.bup %>% mutate(patch3 = paste(allvis.lf.bup$vissys,allvis.lf.bup$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.lf=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lf.bup)[names(mean.lf.bup) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lf.bup<-mean.lf.bup[order(mean.lf.bup$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lf.bup$match.name<-flower.colour$species # this column is just for checking if match correctly
mean.lf.bup$colour<-flower.colour$colour

lf.bup<-ggplot(mean.lf.bup, aes(x=vissys, y=mean.dS.lf,group=flowerID))+
  geom_point(col=mean.lf.bup$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lf.bup$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf","Vis5.lf"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lf.bup, aes(x= "Vis1.lf", y= mean(Vis1.lf.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.bup, aes(x= "Vis2.lf", y= mean(Vis2.lf.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.bup, aes(x= "Vis3.lf", y= mean(Vis3.lf.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.bup, aes(x= "Vis4.lf", y= mean(Vis4.lf.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.bup, aes(x= "Vis5.lf", y= mean(Vis5.lf.bup$dS)), 
             col="black", size=3)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Flower")+
  annotate("text", x = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf","Vis5.lf"), y = 15, label =c("a","b","c","d","d")) #add stitistical info


#make beetle vs leaf plot
##add the mean
mean.lb.bup<-allvis.lb.bup %>% mutate(patch3 = paste(allvis.lb.bup$vissys,allvis.lb.bup$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.lb=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lb.bup)[names(mean.lb.bup) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lb.bup<-mean.lb.bup[order(mean.lb.bup$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lb.bup$match.name<-beetle.colour$species # this column is just for checking if match correctly
mean.lb.bup$colour<-beetle.colour$colour


lb.bup<-ggplot(mean.lb.bup, aes(x=vissys, y=mean.dS.lb,group=beetleID))+
  geom_point(col=mean.lb.bup$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lb.bup$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.background = element_blank(),
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb","Vis5.lb"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lb.bup, aes(x= "Vis1.lb", y= mean(Vis1.lb.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.bup, aes(x= "Vis2.lb", y= mean(Vis2.lb.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.bup, aes(x= "Vis3.lb", y= mean(Vis3.lb.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.bup, aes(x= "Vis4.lb", y= mean(Vis4.lb.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.bup, aes(x= "Vis5.lb", y= mean(Vis5.lb.bup$dS)), 
             col="black", size=3)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Beetle")+
  annotate("text", x = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb","Vis5.lb"), y = 15, label =c("a","b","c","d","e")) #add stitistical info


#make beetle vs flower plot
##add the mean
mean.bf.bup<-allvis.bf.bup %>% mutate(patch3 = paste(allvis.bf.bup$vissys,allvis.bf.bup$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore


##plot the mean dS
names(mean.bf.bup)[names(mean.bf.bup) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf.bup<-mean.bf.bup[order(mean.bf.bup$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf.bup$match.name<-flower.colour$species # this column is just for checking if match correctly
mean.bf.bup$colour<-flower.colour$colour

bf.bup<-ggplot(mean.bf.bup, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf.bup$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.bf.bup$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf","Vis5.bf"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf.bup, aes(x= "Vis1.bf", y= mean(Vis1.bf.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.bup, aes(x= "Vis2.bf", y= mean(Vis2.bf.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.bup, aes(x= "Vis3.bf", y= mean(Vis3.bf.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.bup, aes(x= "Vis4.bf", y= mean(Vis4.bf.bup$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.bup, aes(x= "Vis5.bf", y= mean(Vis5.bf.bup$dS)), 
             col="black", size=3)+ #add the median point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf","Vis5.bf"), y = 15, label =c("a","b","c","d","e")) #add stitistical info


figure.bup <- ggarrange(lf.bup,lb.bup,bf.bup, ncol = 3, nrow = 1)
figure.bup
```
</br>
</br>

## _Papilio xuthus_
```{r}
#make flower vs leaf plot
##add the mean
mean.lf.pap<-allvis.lf.pap %>% mutate(patch3 = paste(allvis.lf.pap$vissys,allvis.lf.pap$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.lf=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lf.pap)[names(mean.lf.pap) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lf.pap<-mean.lf.pap[order(mean.lf.pap$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lf.pap$match.name<-flower.colour$species # this column is just for checking if match correctly
mean.lf.pap$colour<-flower.colour$colour

lf.pap<-ggplot(mean.lf.pap, aes(x=vissys, y=mean.dS.lf,group=flowerID))+
  geom_point(col=mean.lf.pap$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lf.pap$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf","Vis5.lf"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lf.pap, aes(x= "Vis1.lf", y= mean(Vis1.lf.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.pap, aes(x= "Vis2.lf", y= mean(Vis2.lf.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.pap, aes(x= "Vis3.lf", y= mean(Vis3.lf.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.pap, aes(x= "Vis4.lf", y= mean(Vis4.lf.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.pap, aes(x= "Vis5.lf", y= mean(Vis5.lf.pap$dS)), 
             col="black", size=3)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Flower")+
  annotate("text", x = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf","Vis5.lf"), y = 15, label =c("a","b","c","d","d")) #add stitistical info


#make beetle vs leaf plot
##add the mean
mean.lb.pap<-allvis.lb.pap %>% mutate(patch3 = paste(allvis.lb.pap$vissys,allvis.lb.pap$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.lb=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lb.pap)[names(mean.lb.pap) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lb.pap<-mean.lb.pap[order(mean.lb.pap$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lb.pap$match.name<-beetle.colour$species # this column is just for checking if match correctly
mean.lb.pap$colour<-beetle.colour$colour


lb.pap<-ggplot(mean.lb.pap, aes(x=vissys, y=mean.dS.lb,group=beetleID))+
  geom_point(col=mean.lb.pap$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lb.pap$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.background = element_blank(),
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb","Vis5.lb"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lb.pap, aes(x= "Vis1.lb", y= mean(Vis1.lb.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.pap, aes(x= "Vis2.lb", y= mean(Vis2.lb.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.pap, aes(x= "Vis3.lb", y= mean(Vis3.lb.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.pap, aes(x= "Vis4.lb", y= mean(Vis4.lb.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.pap, aes(x= "Vis5.lb", y= mean(Vis5.lb.pap$dS)), 
             col="black", size=3)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Beetle")+
  annotate("text", x = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb","Vis5.lb"), y = 15, label =c("a","b","c","d","e")) #add stitistical info


#make beetle vs flower plot
##add the mean
mean.bf.pap<-allvis.bf.pap %>% mutate(patch3 = paste(allvis.bf.pap$vissys,allvis.bf.pap$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore


##plot the mean dS
names(mean.bf.pap)[names(mean.bf.pap) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf.pap<-mean.bf.pap[order(mean.bf.pap$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf.pap$match.name<-flower.colour$species # this column is just for checking if match correctly
mean.bf.pap$colour<-flower.colour$colour

bf.pap<-ggplot(mean.bf.pap, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf.pap$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.bf.pap$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf","Vis5.bf"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf.pap, aes(x= "Vis1.bf", y= mean(Vis1.bf.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.pap, aes(x= "Vis2.bf", y= mean(Vis2.bf.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.pap, aes(x= "Vis3.bf", y= mean(Vis3.bf.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.pap, aes(x= "Vis4.bf", y= mean(Vis4.bf.pap$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.pap, aes(x= "Vis5.bf", y= mean(Vis5.bf.pap$dS)), 
             col="black", size=3)+ #add the median point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf","Vis5.bf"), y = 15, label =c("a","b","c","d","e")) #add stitistical info


figure.pap <- ggarrange(lf.pap,lb.pap,bf.pap, ncol = 3, nrow = 1)
figure.pap
```
</br>
</br>

##  _Heliconius_ sp
```{r}
#make flower vs leaf plot
##add the mean
mean.lf.heli<-allvis.lf.heli %>% mutate(patch3 = paste(allvis.lf.heli$vissys,allvis.lf.heli$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.lf=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lf.heli)[names(mean.lf.heli) == "patch1"] <- "flowerID" 
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lf.heli<-mean.lf.heli[order(mean.lf.heli$flowerID),] 
#make the data frame order by flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lf.heli$match.name<-flower.colour$species # this column is just for checking if match correctly
mean.lf.heli$colour<-flower.colour$colour

lf.heli<-ggplot(mean.lf.heli, aes(x=vissys, y=mean.dS.lf,group=flowerID))+
  geom_point(col=mean.lf.heli$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lf.heli$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf","Vis5.lf"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lf.heli, aes(x= "Vis1.lf", y= mean(Vis1.lf.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.heli, aes(x= "Vis2.lf", y= mean(Vis2.lf.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.heli, aes(x= "Vis3.lf", y= mean(Vis3.lf.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.heli, aes(x= "Vis4.lf", y= mean(Vis4.lf.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lf.heli, aes(x= "Vis5.lf", y= mean(Vis5.lf.heli$dS)), 
             col="black", size=3)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Flower")+
  annotate("text", x = c("Vis1.lf", "Vis2.lf", "Vis3.lf","Vis4.lf","Vis5.lf"), y = 15, label =c("a","b","c","d","e")) #add stitistical info


#make beetle vs leaf plot
##add the mean
mean.lb.heli<-allvis.lb.heli %>% mutate(patch3 = paste(allvis.lb.heli$vissys,allvis.lb.heli$patch2,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch2(beetles) and vissys
  group_by(patch3,vissys,patch2) %>% summarize(mean.dS.lb=mean(dS)) %>% 
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore

##plot the mean
names(mean.lb.heli)[names(mean.lb.heli) == "patch2"] <- "beetleID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.lb.heli<-mean.lb.heli[order(mean.lb.heli$beetleID),]
#make the data frame order bt beetleID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.lb.heli$match.name<-beetle.colour$species # this column is just for checking if match correctly
mean.lb.heli$colour<-beetle.colour$colour


lb.heli<-ggplot(mean.lb.heli, aes(x=vissys, y=mean.dS.lb,group=beetleID))+
  geom_point(col=mean.lb.heli$colour,size=3, alpha=0.7) + 
  geom_line(col=mean.lb.heli$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.background = element_blank(),
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb","Vis5.lb"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.lb.heli, aes(x= "Vis1.lb", y= mean(Vis1.lb.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.heli, aes(x= "Vis2.lb", y= mean(Vis2.lb.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.heli, aes(x= "Vis3.lb", y= mean(Vis3.lb.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.heli, aes(x= "Vis4.lb", y= mean(Vis4.lb.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.lb.heli, aes(x= "Vis5.lb", y= mean(Vis5.lb.heli$dS)), 
             col="black", size=3)+ #add the median point
  #change the x labels
  ggtitle("Leaf vs. Beetle")+
  annotate("text", x = c("Vis1.lb", "Vis2.lb", "Vis3.lb","Vis4.lb","Vis5.lb"), y = 15, label =c("a","b","c","d","e")) #add stitistical info


#make beetle vs flower plot
##add the mean
mean.bf.heli<-allvis.bf.heli %>% mutate(patch3 = paste(allvis.bf.heli$vissys,allvis.bf.heli$patch1,sep=".")) %>% 
  #create a new column "patch3" which combines the category info of patch1(flowers) and vissys
  group_by(patch3,vissys,patch1) %>% summarize(mean.dS.bf=mean(dS)) %>% #patch1(flowers
  #create a column "mean.dS" as the mean dS for one patch1 to all corresponding patch2
  ungroup() %>% 
  dplyr::select(-patch3) #remove the patch3 column because we don't need it anymore


##plot the mean dS
names(mean.bf.heli)[names(mean.bf.heli) == "patch1"] <- "flowerID"
#rename the column "patch1" because somehow it doesn't work in the ggplot function
mean.bf.heli<-mean.bf.heli[order(mean.bf.heli$flowerID),]
#make the data frame order bt flowerID then when apply the colour code in the following step "viridis", the colour will be consistent in the same comparison accross different visual systems

##combine the colour code list to the mean.bf for ploting
mean.bf.heli$match.name<-flower.colour$species # this column is just for checking if match correctly
mean.bf.heli$colour<-flower.colour$colour

bf.heli<-ggplot(mean.bf.heli, aes(x=vissys, y=mean.dS.bf,group=flowerID))+
  geom_point(col=mean.bf.heli$colour, size=3,alpha=0.7) + 
  geom_line(col=mean.bf.heli$colour, size = 1, alpha=0.7)+
  xlab("Visual system") +     
  ylab("Chromatic contrast (JND)") +
  ylim(0,15)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "grey80",size = NA), #make the backfround empty: panel.background = element_blank()
        axis.title.x = element_text(size=12),  
        axis.text.x  = element_text(size=8, colour="black", angle =90),
        axis.title.y = element_text(size =12, vjust = 1),
        axis.text.y = element_text(size=8, colour="black"),
        axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
        axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'),
        legend.justification=c(1,0), legend.position=c(1,0.45),
        legend.key = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 9))+
  scale_x_discrete(limits = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf","Vis5.bf"),
                   labels=c("Vis 580", "Vis 600","Vis 620","Vis 640","Vis 660"))+
  geom_hline(yintercept = 1,linetype="dotted")+ ##add a JND=1 line
  geom_point(data = mean.bf.heli, aes(x= "Vis1.bf", y= mean(Vis1.bf.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.heli, aes(x= "Vis2.bf", y= mean(Vis2.bf.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.heli, aes(x= "Vis3.bf", y= mean(Vis3.bf.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.heli, aes(x= "Vis4.bf", y= mean(Vis4.bf.heli$dS)), 
             col="black", size=3)+ #add the median point
  geom_point(data = mean.bf.heli, aes(x= "Vis5.bf", y= mean(Vis5.bf.heli$dS)), 
             col="black", size=3)+ #add the median point
  #change the x labels
  ggtitle("Beetle vs. Flower")+
  annotate("text", x = c("Vis1.bf", "Vis2.bf", "Vis3.bf","Vis4.bf","Vis5.bf"), y = 15, label =c("a","b","c","d","e")) #add stitistical info


figure.heli <- ggarrange(lf.heli,lb.heli,bf.heli, ncol = 3, nrow = 1)
figure.heli
```
</br>
</br>


#Summary
The results were qualitatively the same for different photoreceptor ratios among the three comparison groups   contrast increased for LWS photoreceptors with peak sensitivity of 580 to 640 nm (20 nm increments), but there was little or no contrast improvement for LWS peak sensitivities at 660 and 680 nm.